### 2018-06-26 paper/drafts/litrev.tex
Changed the file structure

\documentclass{article}
\begin{document}

HI THIS IS THE START OF THE LIT REV
\section{Introduction}

Control systems on multirotor aerial vehicles have had many different iterations, each of which have added a significant level of control to the system. The control mechanism can be as simple as a motor-rotor control, all the way to controlling the torque, or thrust or so on. The control of a multirotor propellor has to account for multiple different factors, from the ambient wind speed, the rotoation, the pitch of the propellor, all the way to the high level control system of the ESC.

Our paper will compare our system with those of existing systems. 
Our system, a control system with a thrust sensor which provides a feed back loop for the system to check if the appropriate thrust is sought after.

\end{document}

### 2018-06-26 Matllab/leasterr.m

@@ -13,8 +13,8 @@ A = [w i];
 
 p = (A'*A)\A'*v;
 V = A * p;
-n = mvregress(A,v)
-m = mvregress(
+[ke, Ra] = mvregress(A,v)
+
 figure(1);
 plot(sdData.Times,v,sdData.Times,V)
 figure(2)

### 2018-07-12 paper/drafts/litrev.tex
Added more text to the paper.

@@
 
-HI THIS IS THE START OF THE LIT REV
 \section{Introduction}
 
-Control systems on multirotor aerial vehicles have had many different iterations, each of which have added a significant level of control to the system.
-The control mechanism can be as simple as a motor-rotor control, all the way to controlling the torque, or thrust or so on.
-The control of a multirotor propellor has to account for multiple different factors, from the ambient wind speed, the rotoation, the pitch of the propellor, all the way to the high level control system of the ESC.
+\$ Control systems on multirotor aerial vehicles have had many different iterations, each of which have added a significant level of control to the system.
+The control mechanism can be as simple as a motor-rotor control, all the way to controlling the torque, or thrust or one of many other variables.
+The control of a multirotor propellor has to account for multiple different factors, from the ambient wind speed, the rotation, the pitch of the propellor, all the way to the high level control system of the ESC.
+\\
+
+General control systems are what are called open loop control systems.
+The Flight controller sends a value that the propellor should spin at, the ESC converts that value into a form that the motor can handle and then the motor spins.
+From this system there is no feedback as to what the motor is doing[1].
+You wouldn't know if the motor was spinning, or if there was a propellor on the motor or one of many other faults.
+One way that this problem was approached is that the voltage and current draw of the motor is measured and from there a calibrated system would be able to determine how fast, how much torque and how efficiently a motor is spinning[1].
+These are classified as closed system approaches[3].
+Another method used is a torque sensor (strain guage) attached either to the frame or to the motor[21].
+This way we can see the the force the motor exerts and therefore determine hwo much external forces are acting on the drone so that the fc can respond accordingly[21].
+Another method used is a pitot tube to measure the wind speed of either the external wind or the output of the propellor[18].
+This way we can control the output based on the wind speed from the propellor which is an analog for the thrust output[18].
+Lastly what some people use is the IMU's in the drone to measure changes in the drone[7].
+There is an expected speed and direction if that changes we know that there are external forces added.
+While these are are extremely clever and efficient methods they do have their own downfalls.
+Just measuring the current and voltage would lead to lots of noise errors, and also it does not respond to sudden changes in wind as quick as we need it.
+The torque sensor is subject to lots of errors from noise but also has a low response rate and therefore quick changes would not be possible.
+The pitot tube method is similar to what we are proposing but rather than a pitot tube we are using a hot wire anemometer.
+The pitot tube is not as sensitive to changes as we need for this application.
+Lastly the IMU's, while they provide the reaction of the entire drone, they do not accurately show how each propellor is reacting.
+It requires intense computation to produce a model each time we sense a change.
 
 Our paper will compare our system with those of existing systems.
-Our system, a control system with a thrust sensor which provides a feed back loop for the system to check if the appropriate thrust is sought after.
+One last method of measurement to test against is the mahoney paper.
+This paper will be what our experiment will hopefully prove better.
+The mahoney paper uses a thrust estimation based on current, voltage and measurement of several properties of the motor and propellor.
+This data is used within an algorithm that allows the drone to estimate an appropriate response to maintain a constant thrust.
 
+Our system, a control system with a thrust sensor which provides a feed back loop for the system to check if the appropriate thrust is being provided by the propellors.
+
+\section{Theory}
+
+Since we are just focusing on on the static test, there are some assumptions we are making and some math we are skipping.
+
+We are following the math along with the Mahoney Paper.
+
+We have to start by defining the three different velocities that we are measuring.\\
+
+$v_{x} , v_{y} , v_{z}$  Is the velocity of the drone, the body frame velocity. \\
+$v^s_{x} , v^s_{y} , v^s_{z}$ is the velocity of the wind approaching the propellors, the stream velocity. \\
+$v^i_{x} , v^i_{y} , v^i_{z}$ is the induced velocity of the propellors.\\
+
+Since we are doing only the static tests, we do not have to worry about horizontal winds, so we can say $v_s = v^s_{z}$ and $v_i = v^i_{z}$
+What the wind sensor will notice is $v_{tot} = v_{i} + v_{s}$\\
+
+Following along with the mahoney paper we have
+\begin{equation}
+\lambda = \frac{v_{i} + v_{s}}{\varpi R}
+= \frac{v_{i}}{\varpi R}+\frac{v_{s}}{\varpi R}
+=\lambda_{i} + \lambda_{s}
+\end{equation}
+
+Next we go on to calculate the Thurst relationship with the voltage and current through the equations F1Td and F2Td.
+
+\begin{equation}
+T_{d} = \frac{C_{T}}{K^2_{e}}(v_{a} - i_{a}R_{a})
+\end{equation}
+
+$K_{e}$ in this case is obtained by calibrating the system and applying a linear regression while $v_{a}, i_{a}, R_{a}$ are all obtained from the power sent to the motor. $C_{T}$ can be calculated by 
+\begin{equation}
+C_{T} = c_{p} \lambda ^i \lambda 
+\end{equation}
+\begin{equation}
+c_{p} = 2 \rho A R^2 \nonumber
+\end{equation}
+\begin{equation}
+C_{T} = 2 \rho A R^2 \frac{v_{i}}{\varpi R}\frac{v_{i} + v{s}}{\varpi R}  = \frac{2 \rho A (v_{i}^2 + v_{i}v_{s})}{\varpi ^2}
+\end{equation}
+
+After calculating these variables we can start to work towards how we control the motor.
+From the mahoney paper, they individually calculate the appropriate voltage and current to send to the motor.
+From teh paper to calculate $f_{1}(T_{d})$
+\begin{equation}
+T_{d} = \frac{C_{T}(v_{a} - i_{a}R_{a})^2}{k_{e}^2}
+ = \frac{2 \rho A}{\varpi ^2 k^2_{e}}(v^2_{i} + v_{i}v_{s})(v_{a} - i_{a}R_{a})^2
+\end{equation}
+$f_{1}(T_{d})$ is used to calculate the voltage. This can be rearranged to obtain $v_{a}$
+\begin{equation}
+v_{a} = k_{e} \varpi \sqrt{\frac{T_{d}}{2 \rho A (v_{i}^2 + v_{i}v_{s})}} + i_{a}R_{a}
+\end{equation}
+similarly from the paper we can calculate F2Td where 
+\begin{equation}
+T_{d} = C_{T} \frac{k_{q}}{C_{Q}}i_{a}
+\end{equation}
+from applying a similar algebraic reorganization, we get 
+\begin{equation}
+T_{d} = 2 \rho A \frac{v_{i}^2 + v_{i}v_{s}}{\tau} k_{q}i_a
+\end{equation}
+from which we can solve for the current and we get
+\begin{equation}
+i_a = \frac{T_d \tau}{2 \rho A (v_i^2 + v_i v_s) k_q}
+\end{equation}
+Once these values are calculated, they are sent to the ESC at which point the esc controls the speed of the motor. 
+Data from the ESC is collected to help make the thrust estimation. 
+Our wind sensor data will be replacing the estimation for the real value which will allow for a more accurate and crisp response.
 \end{document}

### 2018-07-25 paper/drafts/draft2.tex
Created a new draft of the paper

\documentclass{article}
\begin{document}

\section{I}

%How do drones work, the control system
Multirotor Aerial Vehicles (MAV), specifically quadrotors, have become quite commonplace in many industries ranging from filmography to racing to even military operations. Over the past decade, there has been an incredible amount of research and advancement within this field leading to its proliferation and allowing for the technology to become more accessible. One of the major areas of research regarding MAV's is the control system that directs the motor-rotor system. The control mechanism can be as simple as a motor-rotor control, all the way to controlling the torque, or thrust or one of many other variables. The control of the motor-rotor has to account for multiple different factors, from the ambient wind speed, the rotation, the pitch of the propellor, all the way to the high level control system of the ESC. \\

In general, there are two different types of control loops; open and closed. Open control loops are what the majority of MAV control systems are. There is a flight controller, that sends a signal to the ESC that applies a particular voltage to the motor based on previously calibrated settings. In this method, the final result of the motor spinning is unknown to the flight controller. Therefore given any disturbances, there will be large variances in the response of the overall system. In response to these systems there are smarter, closed loop control. This is the type of control we will focus on. Closed loop systems provide a certain way to meaure the output of the rotor based on the input from the FC. This allows for a smarter, more robust system and greater control of the output.

%What are some of the technologies available, what are their pros and cons

%Intro into the problem

%Intro into wind sensor

%INtro into the mahoney Paper

\section{II}
%Theory of the mahoney paper

%Theory of the wind sensor

%How they will be used together

\section{III}
%Proof of the mahoney paper

%Proof of the wind sensor

\section{IV}
%Experimental setup

%Data

%Results

\section{V}
%Conclusion

%References
\end{document}

### 2018-07-25 paper/drafts/draft2.tex
More edits to the paper

@@
 This allows for a smarter, more robust system and greater control of the output.
+\\
 
 %What are some of the technologies available, what are their pros and cons
-
+The simplest closed loop system available is the measurement of the voltage and current that the ESC sends to the motor.
+The theory is that for a motor to spin at a constant speed, the voltage and current are constant too.
+If there are disturbances in the air, then there would be a change in the voltage to keep the rpm the same.
+While this is simplistic, requires minimal computational power, and is easily applied,  it is a slow measurement as well not very precise.
+To fix this there are other methods researchers have gathered.
+One of the most common methods is modelling the wind forces using either an accelerometer, IMU, or some other similar method.
+This may also be used in combination with the v/a sensing.
+While this is a more robust method and gives back body frame data, there is still the issue of latency of the device as well as a high computational load based on having to determine the position of the drone.
+Therefore a less computationally intense solution is using some sort of external sensor to measure a physical response of the propellors.
+One way some researchers have gone about this is using torque sensors to mesure the constant torque provided by the motor
 %Intro into the problem

### 2018-07-25 paper/drafts/draft2.tex
Added to the paper

@@
 The control of the motor-rotor has to account for multiple different factors, from the ambient wind speed, the rotation, the pitch of the propellor, all the way to the high level control system of the ESC.
+\\
+%Intro into the problem
+kjg
 \\
@@
 Therefore a less computationally intense solution is using some sort of external sensor to measure a physical response of the propellors.
-One way some researchers have gone about this is using torque sensors to mesure the constant torque provided by the motor
-%Intro into the problem
+One way some researchers have gone about this is using torque sensors to mesure the constant torque provided by the motor.
+While strain guages have a fast response and could be used, they are subject to lots of errors and therefore are not feasible.
+
+%INtro into the mahoney Paper
+Robert Mahoney and Bangura have developed a an estimation algorithm based on the voltage and current that can be sensed by the ESC.
+While according to their data, they see a reasonable response there is room for improvement.
+Their algorithm is computationally intense and as well requires a lot of calibration data prior to functioning.
+This includes the radius, pitch, chord length of the propellor as well as specifications of the motor.
+We intend to build upon and develop a system that could be simpler and be used on any configuration just as easily.
 
 %Intro into wind sensor
-
-%INtro into the mahoney Paper
-
+One method of sensing the thrust output of the propellors is to measure the wind output.
+Like the paper with the pitot tubes, we will have a sensor below the propellors measuring the wind.
+Unlike a pitot tube, we will use a hot wire anemometer (HWA) wind sensor (WS).
+The (WS) works on the principle of heating up a coil by running a current through it.
+As wind passes across it, the wind cools it down.
+The WS tries to maintain a constant temperature in the coil and the rate of cooling and heating lead to a measure of how much the wind speed is based on a pre-determined calibration.
 \section{II}

### 2018-07-27 paper/drafts/draft2.tex
Made some changes to the papers, started the graphs

@@
 \\
-%Intro into the problem
-kjg
-\\
 
@@
 This allows for a smarter, more robust system and greater control of the output.
+\\
+
+%Intro into the problem
+The main problem we are trying to answer is how to create an effective, efficient, and reasonable solution to having a closed loop control system.
+This would include having a type of sensor which would measure the thrust output of the propellor and relay that onto the ESC so that the ESC can control the thrust output accordingly.
+
 \\
@@
 
+Since we are just focusing on on the static test, there are some assumptions we are making and some math we are skipping.
+
+We are following the math along with the Mahoney Paper.
+
+We have to start by defining the three different velocities that we are measuring.\\
+
+$v_{x} , v_{y} , v_{z}$  Is the velocity of the drone, the body frame velocity. \\
+$v^s_{x} , v^s_{y} , v^s_{z}$ is the velocity of the wind approaching the propellors, the stream velocity. \\
+$v^i_{x} , v^i_{y} , v^i_{z}$ is the induced velocity of the propellors.\\
+
+Since we are doing only the static tests, we do not have to worry about horizontal winds, so we can say $v_s = v^s_{z}$ and $v_i = v^i_{z}$
+What the wind sensor will notice is $v_{tot} = v_{i} + v_{s}$\\
+
+Following along with the mahoney paper we have
+\begin{equation}
+\lambda = \frac{v_{i} + v_{s}}{\varpi R}
+= \frac{v_{i}}{\varpi R}+\frac{v_{s}}{\varpi R}
+=\lambda_{i} + \lambda_{s}
+\end{equation}
+
+Next we go on to calculate the Thurst relationship with the voltage and current through the equations F1Td and F2Td.
+
+\begin{equation}
+T_{d} = \frac{C_{T}}{K^2_{e}}(v_{a} - i_{a}R_{a})
+\end{equation}
+
+$K_{e}$ in this case is obtained by calibrating the system and applying a linear regression while $v_{a}, i_{a}, R_{a}$ are all obtained from the power sent to the motor. $C_{T}$ can be calculated by 
+\begin{equation}
+C_{T} = c_{p} \lambda ^i \lambda 
+\end{equation}
+\begin{equation}
+c_{p} = 2 \rho A R^2 \nonumber
+\end{equation}
+\begin{equation}
+C_{T} = 2 \rho A R^2 \frac{v_{i}}{\varpi R}\frac{v_{i} + v{s}}{\varpi R}  = \frac{2 \rho A (v_{i}^2 + v_{i}v_{s})}{\varpi ^2}
+\end{equation}
+
+After calculating these variables we can start to work towards how we control the motor.
+From the mahoney paper, they individually calculate the appropriate voltage and current to send to the motor.
+From teh paper to calculate $f_{1}(T_{d})$
+\begin{equation}
+T_{d} = \frac{C_{T}(v_{a} - i_{a}R_{a})^2}{k_{e}^2}
+ = \frac{2 \rho A}{\varpi ^2 k^2_{e}}(v^2_{i} + v_{i}v_{s})(v_{a} - i_{a}R_{a})^2
+\end{equation}
+$f_{1}(T_{d})$ is used to calculate the voltage. This can be rearranged to obtain $v_{a}$
+\begin{equation}
+v_{a} = k_{e} \varpi \sqrt{\frac{T_{d}}{2 \rho A (v_{i}^2 + v_{i}v_{s})}} + i_{a}R_{a}
+\end{equation}
+similarly from the paper we can calculate F2Td where 
+\begin{equation}
+T_{d} = C_{T} \frac{k_{q}}{C_{Q}}i_{a}
+\end{equation}
+from applying a similar algebraic reorganization, we get 
+\begin{equation}
+T_{d} = 2 \rho A \frac{v_{i}^2 + v_{i}v_{s}}{\tau} k_{q}i_a
+\end{equation}
+from which we can solve for the current and we get
+\begin{equation}
+i_a = \frac{T_d \tau}{2 \rho A (v_i^2 + v_i v_s) k_q}
+\end{equation}
+Once these values are calculated, they are sent to the ESC at which point the esc controls the speed of the motor. 
+Data from the ESC is collected to help make the thrust estimation. 
+Our wind sensor data will be replacing the estimation for the real value which will allow for a more accurate and crisp response.
+\end{document}
+
 %Theory of the wind sensor
+talk about stream velocity and induced velocity. 
+talk about how there is an x,y,z in wind
 
 %How they will be used together
-
+Based on the math above, we will 
 \section{III} 
@@
 %Experimental setup
+wind sensor hooked to the ESC so that 2khz speed rather than 50 hz
+only doing static test
+will do dynamic multirotor test later
 
+We have a wind sensor which is placed in an area of unperturbed flow from the propellor.
+The sensor outputs a voltage based on the wind and that voltage is what the control system will maintain.
+This voltage is fed to the ESC since the communication within the ESC is much faster than communication between the ESC and teh FC.
 %Data

### 2018-07-27 paper/drafts/tsvsws.m

@@ -1,0 +1,17 @@
+filename1 = "/home/adiravishankara/Documents/GIT/TC/DATA/0deg_off_on_off1.csv"
+filename2 = "/home/adiravishankara/Documents/GIT/TC/DATA/0deg_off_on_off1T.csv"
+
+data1 = csvread("/home/adiravishankara/Documents/GIT/TC/DATA/0deg_off_on_off1T.csv",0,1);
+data2 = csvread("/home/adiravishankara/Documents/GIT/TC/DATA/0deg_off_on_off1.csv",0,1);
+
+time1 = data1(:,1);
+time2 = data2(:,1);
+
+force = data1(:,10);
+wind_voltage = data2(:,2);
+
+figure(1)
+plot(time1,force)
+
+figure(2)
+plot(time2,wind_voltage)

### 2018-08-08 paper/drafts/draft3.tex
Started the draft 3

--- 2018-07-25 paper/drafts/draft2.tex
@@
-\documentclass{article}
+\documentclass[twocolumn]{article}
+\usepackage{subfig}
 \begin{document}
-
 	\section{I}
@@
 The control of the motor-rotor has to account for multiple different factors, from the ambient wind speed, the rotation, the pitch of the propellor, all the way to the high level control system of the ESC.
-\\
-%Intro into the problem
-kjg
 \\
@@
 \\
+
+	%Intro into the problem
+	The main problem we are trying to answer is how to create an effective, efficient, and reasonable solution to having a closed loop control system.
+This would include having a type of sensor which would measure the thrust output of the propellor and relay that onto the ESC so that the ESC can control the thrust output accordingly.
 
@@
 
-%INtro into the mahoney Paper
 	Robert Mahoney and Bangura have developed a an estimation algorithm based on the voltage and current that can be sensed by the ESC.
@@
 
-%Intro into wind sensor
-One method of sensing the thrust output of the propellors is to measure the wind output.
-Like the paper with the pitot tubes, we will have a sensor below the propellors measuring the wind.
-Unlike a pitot tube, we will use a hot wire anemometer (HWA) wind sensor (WS).
-The (WS) works on the principle of heating up a coil by running a current through it.
-As wind passes across it, the wind cools it down.
-The WS tries to maintain a constant temperature in the coil and the rate of cooling and heating lead to a measure of how much the wind speed is based on a pre-determined calibration.
 	\section{II}
-%Theory of the mahoney paper
+	%Talk about the theory of the wind.
+	%Theory of things like the low pass filter, the algoright, the PID controller, and whatever else we have. Maybe even the statistics
+	We have to start by defining the three different velocities that we are measuring.\\
 
-%Theory of the wind sensor
+	$v_{x} , v_{y} , v_{z}$  Is the velocity of the drone, the body frame velocity. \\
+	$v^s_{x} , v^s_{y} , v^s_{z}$ is the velocity of the wind approaching the propellors, the stream velocity. \\
+	$v^i_{x} , v^i_{y} , v^i_{z}$ is the induced velocity of the propellors.\\
 
-%How they will be used together
-
+	Since we are doing only the static tests, we do not have to worry about horizontal winds, so we can say $v_s = v^s_{z}$ and $v_i = v^i_{z}$
+	What the wind sensor will notice is $v_{tot} = v_{i} + v_{s}$\\
 	\section{III}
-%Proof of the mahoney paper
 
 	%Proof of the wind sensor
-
+	Graph showing the response of wind sensor and force torque.
+	response of rpm based on voltage
+	response to blocking. 
+	\begin{figure}[h]
+	\include{a.png}
+	\caption{poop}
+	\end{figure}
+	\begin{figure}[h]
+		\include{dist.png}
+		\caption{hello}
+	\end{figure}
 	\section{IV}
 	%Experimental setup
+	wind sensor hooked to the ESC so that 2khz speed rather than 50 hz
+	only doing static test
+	will do dynamic multirotor test later
 
+	We have a wind sensor which is placed in an area of unperturbed flow from the propellor.
+The sensor outputs a voltage based on the wind and that voltage is what the control system will maintain.
+This voltage is fed to the ESC since the communication within the ESC is much faster than communication between the ESC and teh FC.
 	%Data

### 2018-08-08 paper/drafts/section3.tex
Started the draft 3

\documentclass[twocolumn]{article}
\begin{document}

%THE THRUST STAND
In our setup we used a thrust stand obtained from RCBenchmark. This thrust stand incorporates an arduino board along with three, three-axis strain guages to measure the forces and the torque derived by the propeller. The board also collects data on the voltage, current and the signal to the ESC's which allows us to measure the power draw of the motor, and the RPM of the motor. Along with this there is a GUI which allows us to collect and visualize the data. From measuring the pulse rate of the board, we can see that the board collects data at a 1kHz speed. At this rate, it is much faster than most ESC's and FC's and therefore is an adequate way to measure how the system responds

The wind sensor we have chosen to use is the "Modern Device- Wind Sensor Rev. P". This device is a hot wire anemometer that is designed to measure wind from any direction. Hot wire anemometers work by passing a current through a wire which heats up due to the current. The heat causes the resistance of the wire to change. As wind passes the wire it cools down the wire, which changes the resistance and is measured by the anemometer. Then the anemometer passes more current through the wire to maintain a particular resistance/temperature. This system allows us to measure the wind speed that is resultant of the propeller. We started by measuring the lower and upper limits of the wind sensor. We also incorporated a way to diminish the wind output, which allows us to measure higher speeds.

%Insert a graph here. Explain how the graph shows the lower and upper limits of the wind sensor.

We also tested how quickly the wind sensor responds to changes in speed. We did this by oscillating the propeller on the thrust stand between high and low speeds. Since the thrust stand measures the force exerted by the propeller, we can sync measuring the force of the propeller on the stand and the wind output with the sensor. This way we can test for the delay in the sensor.
Next we tested how the wind sensor's orientation effects how the sensor measures wind. This is done by maintaining a a thrust

\end{document}

### 2018-08-15 paper/drafts/draft3.tex
Added new papers and more text to the paper

@@
 \begin{document}
+	\title{\begin{titlepage}
+		My paper
+	\end{titlepage}}
+
 	\section{I}
@@
 This includes the radius, pitch, chord length of the propellor as well as specifications of the motor.
-We intend to build upon and develop a system that could be simpler and be used on any configuration just as easily.
+
+	In this paper, we present a closed loop control system that builds upon the ideas of Mahoney and Bangura while reducing the computational complexity through the use of sensors.
 
@@
 	We have to start by defining the three different velocities that we are measuring.\\
+	\begin{eqnarray}
+	\label{e1}
+	v_x , v_y , v_z \\
+	\label{e2}
+	v^s_{x} , v^s_{y} , v^s_{z} \\
+	\label{e3}
+	v^i_{x} , v^i_{y} , v^i_{z}
+	\end{eqnarray}
+	Where \ref{e1} Is the velocity of the drone, the body frame velocity.
+\ref{e2} is the velocity of the wind approaching the propellers, the stream velocity, and \ref{e3} is the induced velocity of the propellers.\\
+	Since we are doing only the static tests, we do not have to worry about horizontal winds, so we can say 
+	\begin{eqnarray}
+	\nonumber
+	v_s = v^s_{z}\\
+	\nonumber
+	v_i = v^i_{z}
+	\end{eqnarray}
+	What the wind sensor will notice is 
+	\begin{equation}
+	v_{tot} = v_{i} + v_{s}
+	\label{vtot}
+	\end{equation}	
+	\section{III} 
+	%THE THRUST STAND
+	In our setup we used a thrust stand obtained from RCBenchmark.
+This thrust stand incorporates an arduino board along with three, three-axis strain guage to measure the forces and the torque derived by the propeller.
+The board also collects data on the voltage, current and the signal to the ESC's which allows us to measure the power draw of the motor, and the RPM of the motor.
+Along with this there is a GUI which allows us to collect and visualize the data.
+From measuring the pulse rate of the board, we can see that the board collects data at a 1kHz speed.
+At this rate, it is much faster than most ESC's and FC's and therefore is an adequate way to measure how the system responds to external stimuli.
+The measurement from the thrust stand will be our "ground truth".
 
-	$v_{x} , v_{y} , v_{z}$  Is the velocity of the drone, the body frame velocity. \\
-	$v^s_{x} , v^s_{y} , v^s_{z}$ is the velocity of the wind approaching the propellors, the stream velocity. \\
-	$v^i_{x} , v^i_{y} , v^i_{z}$ is the induced velocity of the propellors.\\
+	The wind sensor we have chosen to use is the "Modern Device- Wind Sensor Rev.
+P".
+This device is a hot wire anemometer that is designed to measure wind from any direction.
+Hot wire anemometers work by passing a current through a wire which heats up due to the current.
+The heat causes the resistance of the wire to change.
+As wind passes the wire it cools down the wire, which changes the resistance and is measured by the anemometer.
+Then the anemometer passes more current through the wire to maintain a particular resistance/temperature.
+This system allows us to measure the wind speed that is resultant of the propeller.
+From measuring the data rate of the sensor, we measure that the sensor communicates and measures at a rate of 4kHz.
+We started by measuring the lower and upper limits of the wind sensor.
+We also incorporated a way to diminish the wind output, which allows us to measure somewhat higher speeds.
+An orientation test was included to measure changes in the wind in different orientations; specifically normal to the wind, parallel to the wind, and away from the wind.
+The test shows us that the minimum value with $0 km/h$ is averaged at $450 mV$, while a speed of $15 km/h$ results in a voltage of $750 mV$.
 
-	Since we are doing only the static tests, we do not have to worry about horizontal winds, so we can say $v_s = v^s_{z}$ and $v_i = v^i_{z}$
-	What the wind sensor will notice is $v_{tot} = v_{i} + v_{s}$\\
-	\section{III}
+	%Insert a graph here. Explain how the graph shows the lower and upper limits of the wind sensor.
 
-	%Proof of the wind sensor
-	Graph showing the response of wind sensor and force torque.
-	response of rpm based on voltage
-	response to blocking. 
-	\begin{figure}[h]
-	\include{a.png}
-	\caption{poop}
-	\end{figure}
-	\begin{figure}[h]
-		\include{dist.png}
-		\caption{hello}
-	\end{figure}
+	We also tested how quickly the wind sensor responds to changes in speed.
+We did this by oscillating the propeller on the thrust stand between high and low speeds.
+Since the thrust stand measures the force exerted by the propeller, we can sync measuring the force of the propeller on the stand and the wind output with the sensor.
+This way we can test for the delay in the sensor.
+The delay that the wind sensor faces is approximately $4ms$ in relation to the thrust-stand.
+While this is a a significant delay, for the purposes of MAV control, this is a reasonable response rate.
+
+	%Insert graph on oscillating fan measurement
+
+	Next we tested how the wind sensor's placement effects how the sensor measures wind.
+This is done by maintaining a stable thrust on the thrust stand.
+Next we position the wind sensor in various locations moving in a grid like pattern.
+With this method we can determine areas of most wind measurement and least.
+Next we move the sensor from a distance, towards the propeller and measure the average voltage.
+The area with the highest voltage results in the highest sensing.
+
+	%Insert the three part graph here with wind placement data.
+
+	From the collected data, we see that there is approximately a semicircle around which the wind sensor can be placed, and a distance of 15 cm away from the propeller is the convergence point
+
+	%include the algorithm here.
+
 	\section{IV}
 	%Experimental setup
+	The first step we took was to determine the relationship between the rotation speed of the propeller and the voltage the wind sensor observed.
+This gave us a linear relationship which allows us to automatically set the desired voltage within the algorithm.
+	%insert graph of therelationship
+	next we run a deterministic response. ie. graph 6. Show the response of adding disturbance and remove disturbance. shows that we have a more accurate response of wind.
+	%include graph 6
+	Next we also did a reponse of the propeller with the propeller on.
 	wind sensor hooked to the ESC so that 2khz speed rather than 50 hz
@@
 	will do dynamic multirotor test later
-
-	We have a wind sensor which is placed in an area of unperturbed flow from the propellor.
+	We have a wind sensor which is placed in an area of unperturbed flow from the propeller.
 The sensor outputs a voltage based on the wind and that voltage is what the control system will maintain.
 This voltage is fed to the ESC since the communication within the ESC is much faster than communication between the ESC and teh FC.
+
 	%Data

### 2018-08-15 paper/drafts/section3.tex
Added to the paper
Added new papers and more text to the paper

@@
 In our setup we used a thrust stand obtained from RCBenchmark.
-This thrust stand incorporates an arduino board along with three, three-axis strain guages to measure the forces and the torque derived by the propeller.
+This thrust stand incorporates an arduino board along with three, three-axis strain guage to measure the forces and the torque derived by the propeller.
 The board also collects data on the voltage, current and the signal to the ESC's which allows us to measure the power draw of the motor, and the RPM of the motor.
@@
 From measuring the pulse rate of the board, we can see that the board collects data at a 1kHz speed.
-At this rate, it is much faster than most ESC's and FC's and therefore is an adequate way to measure how the system responds
+At this rate, it is much faster than most ESC's and FC's and therefore is an adequate way to measure how the system responds to external stimuli.
+The measurement from the thrust stand will be our "ground truth".
 
@@
 This system allows us to measure the wind speed that is resultant of the propeller.
+From measuring the data rate of the sensor, we measure that the sensor communicates and measures at a rate of 4kHz.
 We started by measuring the lower and upper limits of the wind sensor.
-We also incorporated a way to diminish the wind output, which allows us to measure higher speeds.
+We also incorporated a way to diminish the wind output, which allows us to measure somewhat higher speeds.
+The test shows us that the minimum value with $0 km/h$ is averaged at $450 mV$, while a speed of $15 km/h$ results in a voltage of $750 mV$.
 
@@
 This way we can test for the delay in the sensor.
-Next we tested how the wind sensor's orientation effects how the sensor measures wind. This is done by maintaining a a thrust
+The delay that the wind sensor faces is approximately $4ms$ in relation to the thrust-stand.
+While this is a
+
+%Insert graph on oscillating fan measurement
+
+Next we tested how the wind sensor's orientation and placement effects how the sensor measures wind.
+This is done by maintaining a stable thrust on the thrust stand.
+Next we position the wind sensor in various locations moving in a grid like pattern.
+With this method we can determine areas of most wind measurement and least.
+Next we move the sensor from a distance, towards the propeller and measure the average voltage.
+The area with the highest voltage results in the highest sensing.
+Lastly we tested how the wind sensor measures changes in the wind in different orientations; specifically normal to the wind, parallel to the wind, and away from the wind.
+
+%Insert the three part graph here with wind placement data.
+
+From the collected data, we see that there is approximately a semicircle around which the wind sensor can be placed, and a distance of 15 cm away from the propeller is the convergence point
 

### 2018-08-15 paper/drafts/theory.tex
Added new papers and more text to the paper

\documentclass[twocolumn]{article}
\begin{document}
	%Talk about the theory of the wind.
	%Theory of things like the low pass filter, the algoright, the PID controller, and whatever else we have. Maybe even the statistics
	In the scope of this paper we are strictly working on the static propeller tests. This allows us to fully define and measure how the motor-rotor system will respond to any external stimuli. To start characterizing the propeller output we have to define the three different velocities that we are measuring.\\

	\noindent $v_{x}$ , $ v_{y}$ , $ v_{z}$  Is the velocity of the drone, the body frame velocity. 
	$v^s_{x}$ , $v^s_{y}$ , $v^s_{z}$  is the velocity of the wind approaching the propellers, the stream velocity. 
	$v^i_{x}$ , $v^i_{y}$ , $v^i_{z}$ is the induced velocity of the propellers. Since we are doing only the static tests,horizontal wind can be considered irrelevant, therefore $v_s = v^s_{z}$ and $v_i = v^i_{z}$. What the wind sensor will notice is $v_{tot} = v_{i} + v_{s}$. In real life settings we could calculate $v_s$ based on the data from the MAV's IMU. Since this is not the case, we can instead set a particular voltage as the desired voltage, $v_d$. This desired voltage is ideally the voltage the wind sensor measures when there are no external forces. The goal of the algorithm would be to efficiently and accurately return the measured voltage from the wind sensor towards the desired voltage.

	Since the signal of the wind sensor is an analog voltage, we have to expect some noise. Therefore we use a first order low-pass filter to reduce the noise from the wind sensor.
\end{document}

### 2018-08-23 paper/drafts/draft3.tex
New data

@@
 
-	In this paper, we present a closed loop control system that builds upon the ideas of Mahoney and Bangura while reducing the computational complexity through the use of sensors.
-
+	In this paper, we present a novel control system for MAV's based around a sensor that measures wind speed and uses a observer kalman filter to handle the data and provide an optimal output to maintain a desired thrust value.
+The goal of our system is to provide a similar or better response to that of Mahoney et al.
+while also being computationally less intense.
+	\section{Paper Review}
+	Yeo et al.
+developed a pitot tube method of sensing the wind speed.
+The purpose of their sensing was for detection of other drones, but their method can be related to.
+The pitot tubes are connected to a sensor that measures changes in pressure.
+They detail a relationship between wind speed and pressure and therefore use detected pressure to measure the overall downwash windspeed of each propeller.
+Their results showed a high level of response to changes in wind with a high level of accuracy.
+The issue that was faced was that there was a very limited range under which the drone could
 	\section{II}

### 2018-08-23 DATA/data_for_paper/Final/sync_tests.m

@@ -1,0 +1,27 @@
+load("pulse1T.mat");
+pulse1T = Data;
+load("pulse2T.mat");
+pulse2T = Data;
+load("pulse3T.mat");
+pulse3T = Data;
+load("pulse4T.mat");
+pulse4T = Data;
+
+load("step1T.mat");
+step1T = Data;
+load("step2T.mat");
+step2T = Data;
+load("step3T.mat");
+step3T = Data;
+load("step4T.mat");
+step4T = Data;
+
+pulse1 = csvread("pulse1.csv",1,0);
+pulse2 = csvread("pulse2.csv",1,0);
+pulse3 = csvread("pulse3.csv",1,0);
+pulse4 = csvread("pulse4.csv",1,0);
+
+step1 = csvread("step1.csv",1,0);
+step2 = csvread("step2.csv",1,0);
+step3 = csvread("step3.csv",1,0);
+step4 = csvread("step4.csv",1,0);

### 2018-08-27 paper/drafts/draft3.tex
Couple of changes to the algorithm

@@
 The issue that was faced was that there was a very limited range under which the drone could
+
+	Mahoney et al (2017) have developed an algorithm which bases the control system around an estimation of the thrust from a propeller based on the voltage and current given to the motor by the ESC.
+Their system works to maintain a thrust given some disturbance.
+From looking over their algorithm, they have a system which runs through a for loop before detecting an appropriate response to extraneous forces.
+This system while it allows for a valid estimation of the thrust, it is a complex system that requires relatively heavy computation and therefore is not feasible.
+As well this method of thrust based control requires a significant amount of calibration for both the propellers and
 	\section{II}

### 2018-08-27 DATA/data_for_paper/final2/datacol.m
New Tests, plus addition of testing for the wind sensor range

@@ -1,0 +1,1 @@
+t_data = csvread("wind_model.csv",1,0);

### 2018-08-27 DATA/data_for_paper/final2/step_test_ert_rtw/html/define.js

@@ -1,0 +1,200 @@
+function CodeDefine() { 
+this.def = new Array();
+this.def["IsrOverrun"] = {file: "ert_main_c.html",line:8,type:"var"};
+this.def["OverrunFlag"] = {file: "ert_main_c.html",line:9,type:"var"};
+this.def["rt_OneStep"] = {file: "ert_main_c.html",line:10,type:"fcn"};
+this.def["stopRequested"] = {file: "ert_main_c.html",line:38,type:"var"};
+this.def["main"] = {file: "ert_main_c.html",line:39,type:"fcn"};
+this.def["step_test_B"] = {file: "step_test_c.html",line:26,type:"var"};
+this.def["step_test_X"] = {file: "step_test_c.html",line:29,type:"var"};
+this.def["step_test_DW"] = {file: "step_test_c.html",line:32,type:"var"};
+this.def["step_test_M_"] = {file: "step_test_c.html",line:35,type:"var"};
+this.def["step_test_M"] = {file: "step_test_c.html",line:36,type:"var"};
+this.def["rt_ertODEUpdateContinuousStates"] = {file: "step_test_c.html",line:69,type:"fcn"};
+this.def["arduino_PWMOutput_arduino_PWMOu"] = {file: "step_test_c.html",line:146,type:"fcn"};
+this.def["rt_powd_snf"] = {file: "step_test_c.html",line:174,type:"fcn"};
+this.def["SystemProp_matlabCodegenSetA_dm"] = {file: "step_test_c.html",line:220,type:"fcn"};
+this.def["matlabCodegenHandle_matlabCo_dm"] = {file: "step_test_c.html",line:229,type:"fcn"};
+this.def["SystemProp_matlabCodegenSe_dms4"] = {file: "step_test_c.html",line:241,type:"fcn"};
+this.def["step_test_SystemCore_release_d"] = {file: "step_test_c.html",line:248,type:"fcn"};
+this.def["step_LPHPFilterBase_releaseImpl"] = {file: "step_test_c.html",line:258,type:"fcn"};
+this.def["step__SystemCore_releaseWrapper"] = {file: "step_test_c.html",line:265,type:"fcn"};
+this.def["step_test_SystemCore_release_dm"] = {file: "step_test_c.html",line:275,type:"fcn"};
+this.def["step_tes_SystemCore_delete_dms4"] = {file: "step_test_c.html",line:285,type:"fcn"};
[…]

### 2018-08-27 DATA/data_for_paper/final2/step_test_ert_rtw/multiword_types.h

@@ -1,0 +1,165 @@
+/*
+ * multiword_types.h
+ *
+ * Academic License - for use in teaching, academic research, and meeting
+ * course requirements at degree granting institutions only.  Not for
+ * government, commercial, or other organizational use.
+ *
+ * Code generation for model "step_test".
+ *
+ * Model version              : 1.19
+ * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
+ * C source code generated on : Mon Aug 27 14:28:14 2018
+ *
+ * Target selection: ert.tlc
+ * Note: GRT includes extra infrastructure and instrumentation for prototyping
+ * Embedded hardware selection: ARM Compatible->ARM Cortex
+ * Code generation objectives: Unspecified
+ * Validation result: Not run
+ */
+
+#ifndef MULTIWORD_TYPES_H
+#define MULTIWORD_TYPES_H
+#include "rtwtypes.h"
+
+/*
+ * Definitions supporting external data access
+ */
+typedef int32_T chunk_T;
+typedef uint32_T uchunk_T;
+
+/*
+ * MultiWord supporting definitions
+ */
+typedef long int long_T;
+
+/*
+ * MultiWord types
+ */
+typedef struct {
+  uint32_T chunks[2];
+} int64m_T;
+
+typedef struct {
+  int64m_T re;
+  int64m_T im;
+} cint64m_T;
+
+typedef struct {
+  uint32_T chunks[2];
+} uint64m_T;
+
+typedef struct {
+  uint64m_T re;
+  uint64m_T im;
+} cuint64m_T;
+
+typedef struct {
+  uint32_T chunks[3];
+} int96m_T;
+
+typedef struct {
+  int96m_T re;
+  int96m_T im;
+} cint96m_T;
+
+typedef struct {
+  uint32_T chunks[3];
+} uint96m_T;
+
+typedef struct {
+  uint96m_T re;
+  uint96m_T im;
+} cuint96m_T;
+
+typedef struct {
+  uint32_T chunks[4];
+} int128m_T;
+
+typedef struct {
+  int128m_T re;
+  int128m_T im;
+} cint128m_T;
+
+typedef struct {
+  uint32_T chunks[4];
+} uint128m_T;
+
+typedef struct {
+  uint128m_T re;
+  uint128m_T im;
+} cuint128m_T;
+
+typedef struct {
[…]

### 2018-08-27 DATA/data_for_paper/final2/step_test_ert_rtw/rtGetInf.c

@@ -1,0 +1,144 @@
+/*
+ * rtGetInf.c
+ *
+ * Academic License - for use in teaching, academic research, and meeting
+ * course requirements at degree granting institutions only.  Not for
+ * government, commercial, or other organizational use.
+ *
+ * Code generation for model "step_test".
+ *
+ * Model version              : 1.19
+ * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
+ * C source code generated on : Mon Aug 27 14:28:14 2018
+ *
+ * Target selection: ert.tlc
+ * Note: GRT includes extra infrastructure and instrumentation for prototyping
+ * Embedded hardware selection: ARM Compatible->ARM Cortex
+ * Code generation objectives: Unspecified
+ * Validation result: Not run
+ */
+
+/*
+ * Abstract:
+ *      Function to initialize non-finite, Inf
+ */
+#include "rtGetInf.h"
+#define NumBitsPerChar                 8U
+
+/*
+ * Initialize rtInf needed by the generated code.
+ * Inf is initialized as non-signaling. Assumes IEEE.
+ */
+real_T rtGetInf(void)
+{
+  size_t bitsPerReal = sizeof(real_T) * (NumBitsPerChar);
+  real_T inf = 0.0;
+  if (bitsPerReal == 32U) {
+    inf = rtGetInfF();
+  } else {
+    uint16_T one = 1U;
+    enum {
+      LittleEndian,
+      BigEndian
+    } machByteOrder = (*((uint8_T *) &one) == 1U) ? LittleEndian : BigEndian;
+    switch (machByteOrder) {
+     case LittleEndian:
+      {
+        union {
+          LittleEndianIEEEDouble bitVal;
+          real_T fltVal;
+        } tmpVal;
+
+        tmpVal.bitVal.words.wordH = 0x7FF00000U;
+        tmpVal.bitVal.words.wordL = 0x00000000U;
+        inf = tmpVal.fltVal;
+        break;
+      }
+
+     case BigEndian:
+      {
+        union {
+          BigEndianIEEEDouble bitVal;
+          real_T fltVal;
+        } tmpVal;
+
+        tmpVal.bitVal.words.wordH = 0x7FF00000U;
+        tmpVal.bitVal.words.wordL = 0x00000000U;
+        inf = tmpVal.fltVal;
+        break;
[…]

### 2018-08-27 DATA/data_for_paper/final2/step_test_ert_rtw/rt_nonfinite.h

@@ -1,0 +1,58 @@
+/*
+ * rt_nonfinite.h
+ *
+ * Academic License - for use in teaching, academic research, and meeting
+ * course requirements at degree granting institutions only.  Not for
+ * government, commercial, or other organizational use.
+ *
+ * Code generation for model "step_test".
+ *
+ * Model version              : 1.19
+ * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
+ * C source code generated on : Mon Aug 27 14:28:14 2018
+ *
+ * Target selection: ert.tlc
+ * Note: GRT includes extra infrastructure and instrumentation for prototyping
+ * Embedded hardware selection: ARM Compatible->ARM Cortex
+ * Code generation objectives: Unspecified
+ * Validation result: Not run
+ */
+
+#ifndef RTW_HEADER_rt_nonfinite_h_
+#define RTW_HEADER_rt_nonfinite_h_
+#include <stddef.h>
+#include "rtwtypes.h"
+
+extern real_T rtInf;
+extern real_T rtMinusInf;
+extern real_T rtNaN;
+extern real32_T rtInfF;
+extern real32_T rtMinusInfF;
+extern real32_T rtNaNF;
+extern void rt_InitInfAndNaN(size_t realSize);
+extern boolean_T rtIsInf(real_T value);
+extern boolean_T rtIsInfF(real32_T value);
+extern boolean_T rtIsNaN(real_T value);
+extern boolean_T rtIsNaNF(real32_T value);
+typedef struct {
+  struct {
+    uint32_T wordH;
+    uint32_T wordL;
+  } words;
+} BigEndianIEEEDouble;
+
+typedef struct {
+  struct {
+    uint32_T wordL;
+    uint32_T wordH;
+  } words;
+} LittleEndianIEEEDouble;
+
+typedef struct {
+  union {
+    real32_T wordLreal;
+    uint32_T wordLuint;
+  } wordL;
+} IEEESingle;
+
+#endif                                 /* RTW_HEADER_rt_nonfinite_h_ */

### 2018-08-27 DATA/data_for_paper/final2/step_test_ert_rtw/rtwtypes.h

@@ -1,0 +1,42 @@
+/*
+ * rtwtypes.h
+ *
+ * Academic License - for use in teaching, academic research, and meeting
+ * course requirements at degree granting institutions only.  Not for
+ * government, commercial, or other organizational use.
+ *
+ * Code generation for model "step_test".
+ *
+ * Model version              : 1.19
+ * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
+ * C source code generated on : Mon Aug 27 14:28:14 2018
+ *
+ * Target selection: ert.tlc
+ * Note: GRT includes extra infrastructure and instrumentation for prototyping
+ * Embedded hardware selection: ARM Compatible->ARM Cortex
+ * Code generation objectives: Unspecified
+ * Validation result: Not run
+ */
+
+#ifndef RTWTYPES_H
+#define RTWTYPES_H
+#include "tmwtypes.h"
+#include "simstruc_types.h"
+#ifndef POINTER_T
+# define POINTER_T
+
+typedef void * pointer_T;
+
+#endif
+
+/* Logical type definitions */
+#if (!defined(__cplusplus))
+#  ifndef false
+#   define false                       (0U)
+#  endif
+
+#  ifndef true
+#   define true                        (1U)
+#  endif
+#endif
+#endif                                 /* RTWTYPES_H */

### 2018-08-27 DATA/data_for_paper/final2/step_test_ert_rtw/step_test_data.c

@@ -1,0 +1,210 @@
+/*
+ * step_test_data.c
+ *
+ * Academic License - for use in teaching, academic research, and meeting
+ * course requirements at degree granting institutions only.  Not for
+ * government, commercial, or other organizational use.
+ *
+ * Code generation for model "step_test".
+ *
+ * Model version              : 1.19
+ * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
+ * C source code generated on : Mon Aug 27 14:28:14 2018
+ *
+ * Target selection: ert.tlc
+ * Note: GRT includes extra infrastructure and instrumentation for prototyping
+ * Embedded hardware selection: ARM Compatible->ARM Cortex
+ * Code generation objectives: Unspecified
+ * Validation result: Not run
+ */
+
+#include "step_test.h"
+#include "step_test_private.h"
+
+/* Block parameters (default storage) */
+P_step_test_T step_test_P = {
+  /* Mask Parameter: DiscretePIDController_I
+   * Referenced by: '<S15>/Integral Gain'
+   */
+  0.01,
+
+  /* Mask Parameter: DiscretePIDController_P
+   * Referenced by: '<S15>/Proportional Gain'
+   */
+  0.05,
+
+  /* Mask Parameter: CompareToConstant_const
+   * Referenced by: '<S10>/Constant'
+   */
+  3.0,
+
+  /* Mask Parameter: DetectChange_vinit
+   * Referenced by: '<S14>/Delay Input1'
+   */
+  0.0,
+
+  /* Expression: 0.01
+   * Referenced by: '<S4>/Analog Input1'
+   */
+  0.01,
+
+  /* Expression: 0.01
+   * Referenced by: '<S4>/Analog Input'
+   */
+  0.01,
+
+  /* Expression: 650
+   * Referenced by: '<Root>/Wind_des'
+   */
+  650.0,
+
+  /* Expression: 1
+   * Referenced by: '<S1>/Run Sim'
+   */
+  1.0,
+
+  /* Expression: 0
+   * Referenced by: '<Root>/Automatic Control'
+   */
+  0.0,
+
+  /* Expression: 1
+   * Referenced by: '<Root>/Enable'
+   */
+  1.0,
+
[…]

### 2018-08-27 DATA/data_for_paper/final2/step_test_ert_rtw/step_test_private.h

@@ -1,0 +1,57 @@
+/*
+ * step_test_private.h
+ *
+ * Academic License - for use in teaching, academic research, and meeting
+ * course requirements at degree granting institutions only.  Not for
+ * government, commercial, or other organizational use.
+ *
+ * Code generation for model "step_test".
+ *
+ * Model version              : 1.19
+ * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
+ * C source code generated on : Mon Aug 27 14:28:14 2018
+ *
+ * Target selection: ert.tlc
+ * Note: GRT includes extra infrastructure and instrumentation for prototyping
+ * Embedded hardware selection: ARM Compatible->ARM Cortex
+ * Code generation objectives: Unspecified
+ * Validation result: Not run
+ */
+
+#ifndef RTW_HEADER_step_test_private_h_
+#define RTW_HEADER_step_test_private_h_
+#include "rtwtypes.h"
+#include "multiword_types.h"
+
+/* Private macros used by the generated code to access rtModel */
+#ifndef rtmIsMajorTimeStep
+# define rtmIsMajorTimeStep(rtm)       (((rtm)->Timing.simTimeStep) == MAJOR_TIME_STEP)
+#endif
+
+#ifndef rtmIsMinorTimeStep
+# define rtmIsMinorTimeStep(rtm)       (((rtm)->Timing.simTimeStep) == MINOR_TIME_STEP)
+#endif
+
+#ifndef rtmSetTFinal
+# define rtmSetTFinal(rtm, val)        ((rtm)->Timing.tFinal = (val))
+#endif
+
+#ifndef rtmSetTPtr
+# define rtmSetTPtr(rtm, val)          ((rtm)->Timing.t = (val))
+#endif
+
+/* Used by FromWorkspace Block: '<S3>/FromWs' */
+#ifndef rtInterpolate
+# define rtInterpolate(v1,v2,f1,f2)    (((v1)==(v2))?((double)(v1)): (((f1)*((double)(v1)))+((f2)*((double)(v2)))))
+#endif
+
+#ifndef rtRound
+# define rtRound(v)                    ( ((v) >= 0) ? floor((v) + 0.5) : ceil((v) - 0.5) )
+#endif
+
+extern real_T rt_powd_snf(real_T u0, real_T u1);
+
+/* private model entry point functions */
+extern void step_test_derivatives(void);
+
+#endif                                 /* RTW_HEADER_step_test_private_h_ */

### 2018-08-27 DATA/data_for_paper/final2/step_test_ert_rtw/step_test_types.h

@@ -1,0 +1,188 @@
+/*
+ * step_test_types.h
+ *
+ * Academic License - for use in teaching, academic research, and meeting
+ * course requirements at degree granting institutions only.  Not for
+ * government, commercial, or other organizational use.
+ *
+ * Code generation for model "step_test".
+ *
+ * Model version              : 1.19
+ * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
+ * C source code generated on : Mon Aug 27 14:28:14 2018
+ *
+ * Target selection: ert.tlc
+ * Note: GRT includes extra infrastructure and instrumentation for prototyping
+ * Embedded hardware selection: ARM Compatible->ARM Cortex
+ * Code generation objectives: Unspecified
+ * Validation result: Not run
+ */
+
+#ifndef RTW_HEADER_step_test_types_h_
+#define RTW_HEADER_step_test_types_h_
+#include "rtwtypes.h"
+#include "multiword_types.h"
+#ifndef typedef_dsp_private_SlidingWindowAver_T
+#define typedef_dsp_private_SlidingWindowAver_T
+
+typedef struct {
+  int32_T isInitialized;
+  boolean_T isSetupComplete;
+  real_T pCumSum;
+  real_T pCumSumRev[4];
+  real_T pCumRevIndex;
+} dsp_private_SlidingWindowAver_T;
+
+#endif                                 /*typedef_dsp_private_SlidingWindowAver_T*/
+
+/* Custom Type definition for MATLABSystem: '<S4>/Analog Input' */
+#include "MW_SVD.h"
+#ifndef struct_mde12672362a75a5cad908219ba2cf40ac
+#define struct_mde12672362a75a5cad908219ba2cf40ac
+
+struct mde12672362a75a5cad908219ba2cf40ac
+{
+  int32_T S0_isInitialized;
+  real_T W0_states[83];
+  real_T P0_InitialStates;
+  real_T P1_Coefficients[84];
+};
+
+#endif                                 /*struct_mde12672362a75a5cad908219ba2cf40ac*/
+
+#ifndef typedef_dsp_FIRFilter_0_step_test_T
+#define typedef_dsp_FIRFilter_0_step_test_T
+
[…]

### 2018-09-05 paper/drafts/draft3.tex
Collected the final data for the paper, in final2/new_

@@
 The control mechanism can be as simple as a motor-rotor control, all the way to controlling the torque, or thrust or one of many other variables.
-The control of the motor-rotor has to account for multiple different factors, from the ambient wind speed, the rotation, the pitch of the propellor, all the way to the high level control system of the ESC.
+The control of the motor-rotor has to account for multiple different factors, from the ambient wind speed, the rotation, the pitch of the propeller, all the way to the high level control system of the ESC.
 \\
@@
 This is the type of control we will focus on.
-Closed loop systems provide a certain way to meaure the output of the rotor based on the input from the FC.
+Closed loop systems provide a certain way to measure the output of the rotor based on the input from the FC.
 This allows for a smarter, more robust system and greater control of the output.
@@
 While this is a more robust method and gives back body frame data, there is still the issue of latency of the device as well as a high computational load based on having to determine the position of the drone.
-Therefore a less computationally intense solution is using some sort of external sensor to measure a physical response of the propellors.
-One way some researchers have gone about this is using torque sensors to mesure the constant torque provided by the motor.
+Therefore a less computationally intense solution is using some sort of external sensor to measure a physical response of the propellers.
+One way some researchers have gone about this is using torque sensors to measure the constant torque provided by the motor.
 While strain guages have a fast response and could be used, they are subject to lots of errors and therefore are not feasible.
@@
 As well this method of thrust based control requires a significant amount of calibration for both the propellers and
+
+	Real-Time Wind Speed Estimation and Compensation for Improved Flight
+
+	Streit developed a control system to compensate for wind disturbances using a pitot-tube sensor coupled with the GPS sensor along with an accompanying estimation algorithm.
+While this seems similar to the Yeo et al paper, there are some major differences.
+Streit has only one pitot sensor onboard the UAV which is uni-directional and therefore only applies to forward motion.
+As well the pitot-tube is made of brass and therefore not feasible for all smaller UAV's as it will be too heavy.
+
+	Onboard Flow Sensing for Downwash Detection and Avoidance with a Small Quadrotor Helicopter
+
+	Yeo et al have developed a system similar to our proposed idea by fabricating pitot tubes to sit below each propeller and measure the rotor downwash and compare them to the estimated expected wind speed.
+Their system is ultimately used to localize external noise from other UAV's and therefore an exceedingly accurate measurement is not as important.
+While the sensor can accurately measure wind speed accurately during vertical motion, there is significant divergence from the ground speed measurement during lateral movement.
+As well there is a very limited range of speeds that are available for measurement from the probe.
 	\section{II}

### 2018-09-05 DATA/data_for_paper/final2/datacol.m

@@ -1,1 +1,6 @@
-model_test6T = csvread("model_test6.csv",1,0);
+ramp_test = csvread("new_/ramp_test2.csv",1,0);
+
+[r,c] = find(ramp_test(:,10) == 0);
+
+ramp_test(r,:) = [];
+

### 2018-09-05 DATA/data_for_paper/final2/datacol.m
Disturbance Check

@@ -1,4 +1,4 @@
-ramp_test = csvread("new_/ramp_test2.csv",1,0);
+ramp_test = csvread("new_/ramp_test3.csv",1,0);
 
 [r,c] = find(ramp_test(:,10) == 0);
 

### 2018-09-12 paper/drafts/draft_final.tex
ran some new tests in final3/paper_data

\documentclass[twocolumn]{article}
\usepackage{subfig}
\usepackage{graphicx}
\begin{document}
	\title{\begin{titlepage}
			My paper
	\end{titlepage}}
	\section{1}
	\subsection{1.1}
	\subsection{1.2}
	\subsection{1.3}
	\subsection{1.4}

	\section{2}
	\subsection{2.1}
	\subsection{2.2}
	\subsection{2.3}
	\subsection{2.4}

	\section{3}
	\subsection{Thrust stand}
	%THE THRUST STAND
	In our setup we used a thrust stand obtained from RCBenchmark, specifically the RCBenchmark Thrust stand and Dynamometer Series 1580 \cite{rcb} as our testbed. The measurements from the thrust stand will be our "ground truth". This thrust stand incorporates a micro-controller board along with three, three-axis strain guage to measure the forces and the torque derived by the propeller. The board also collects data on the voltage, current and the signal to the ESC's which allows us to measure the power draw of the motor, and the RPM of the motor. Along with this there is an associated GUI which allows us to control the board and collect and visualize the data. The testbed collects data at a very high rate of close to 1kHz but then averages the data to eliminate outliers, so the data rate is 40Hz. This is more than adequate for the purposes of modeling the thrust response of the propeller to various stimuli. 
	\subsection{Wind Sensor Intro}
	The wind sensor we have chosen to use is the "Modern Device- Wind Sensor Rev. P" \cite{wind_sensor}. This device is a hot wire anemometer that is designed to measure wind from any direction. Hot wire anemometers work by passing a constant current through a thin wire which heats up due to the current. As the wind flows past the wire, the wire will be cooled down rapidly, resulting in a change in the measured voltage, which is the value that we observe \cite{hot_wire}. This system allows us to measure the wind speed that is resultant of the propeller. 
	\subsection{Wind Sensor Proof}
	To understand the limitations of the wind sensor, we performed a series of tests to characterize the sensor. The first of which was to determine under which orientation the sensor observed the highest range of wind speeds. As seen in \ref{orient_test}, the orientation of placing the wind sensor normal to the direction of wind flow allowed for the highest range of measurement. Next we performed a test to determine the feasible range of measurement. This was done by exposing the wind sensor to a step-signal test and a pulse signal test ranging from the minimal PWM value to approximately $50\%$ of the motor's max value, the results of which are in \ref{min_max}. The PWM values in this case are based around the Simulink-Arduino Library PWM module.  This resulted in a working range from $PWM = 44$ to $PWM = 60$. While there is possibility for the wind sensor to measure higher wind speeds, there is a significant amount of noise even with the addition of a low-pass filter, hence we decided to limit the max speed of our experiment.

	Another factor that we deem is important to characterize is the speed of response to change of wind speed. We measured this by running the propeller at various different speeds, while tracking the thrust output on the testbed as our base measurement of response time and then comparing the response time to see the lag in response time. By doing this we found that there was a negligible lag time of less than $10 ms$, which is our resolution for each measurement.

	Lastly we measured the location of the wind sensor in relation to the propellers. To do so we measured a semi-circle area behind the propeller to deem the location of highest wind sensitivity. Resulting in a map as seen in figure \ref{area}.

	By characterizing the wind sensor, we can ensure that it is in the optimal configuration for us to collect data.

	\section{Results}

	\subsection{Experimental Setup- How we set up the kalman/Algorithm}
	\begin{figure}[b]
		\includegraphics[width=\textwidth]{block_diagram}
		\caption{Block Diagram}
		\label{block_diagram}
	\end{figure}

	We developed a control architecture as pictured in fig \ref{block_diagram} where there are two sources of measurement for the thrust value. The first, main value, is from the wind sensor which is measured through an Arduino. The voltage value that the arduino measures is then converted to a thrust value through the power function
	\begin{equation}
	Thrust = 4.701 * 10^{15} * V_w^{6.146} + 0.0731
	\label{wind_power}
	\end{equation}

	The second measurement of thrust is a polynomial function that converts the recorded PWM value that is used to control the propeller to thrust. \newline
	\begin{eqnarray}
	Thrust = 1.957*10^{-5}*PWM^4 \\
	- 7.476*10^{-4}*PWM^3 \nonumber\\ 
	+ 1.272*10^{-2}*PWM^2 \nonumber\\
	+ .01092*PWM - .01842 \nonumber
	\label{pwm_poly}
	\end{eqnarray}

	These values are then passed through a Kalman Filter weighted for the wind sensor. This method allows for the system to accurately determine the thrust value output while reducing noise due to the nature of the wind. Next this value is passed to a PID controller which checks the current thrust value to the desired thrust value and outputs a thrust value. Lastly a polynomial function converts the thrust value back to PWM.
	\begin{eqnarray}
	PWM = -.1746*Thrust^4 + 1.008*Thrust^3\\ 
	- 3.409*Thrust*2 + 12.29*Thrust + 1.8430 \nonumber
	\label{pwm_poly}
	\end{eqnarray}
	\subsection{The tests}
	Once the characteristics of the wind sensor were determined we ran tests to ensure the viability of our algorithm and if it would respond to external stimuli the way we expected.
	\subsection{4.3}
	\subsection{4.4}

	\section{5}

	\subsection{5.1}
	\subsection{5.2}
	\subsection{5.3}
	\subsection{5.4}

	\begin{thebibliography}{99}
		\bibitem{Mahoney1} Mahoney 2012
		\bibitem{rcb} https://www.rcbenchmark.com/dynamometer-series-1580/
		\bibitem{wind_sensor} https://moderndevice.com/product/wind-sensor-rev-p/
		\bibitem{hot_wire} Extended Applications of the Hot‐Wire Anemometer, Stanley Corrsin,Review of Scientific Instruments 1947 18:7, 469-471

	\end{thebibliography}

\end{document}

### 2018-09-12 DATA/data_for_paper/final2/Final_test_ert_rtw/Final_test.c

@@ -7,9 +7,9 @@
  *
  * Code generation for model "Final_test".
  *
- * Model version              : 1.42
+ * Model version              : 1.49
  * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
- * C source code generated on : Fri Sep  7 12:34:04 2018
+ * C source code generated on : Wed Sep 12 11:44:58 2018
  *
  * Target selection: ert.tlc
  * Note: GRT includes extra infrastructure and instrumentation for prototyping
@@ -38,17 +38,22 @@ RT_MODEL_Final_test_T *const Final_test_M = &Final_test_M_;
 /* Forward declaration for local functions */
 static codertarget_arduinobase_int_f_T *arduino_PWMOutput_arduino_PWMOu
   (codertarget_arduinobase_int_f_T *obj);
+static void SystemProp_matlabCodegenSetAn_f(dsp_simulink_MovingAverage_f_T *obj,
+  boolean_T value);
+static void Final_test_SystemCore_release_f(dsp_simulink_MovingAverage_f_T *obj);
+static void Final_test_SystemCore_delete_f(dsp_simulink_MovingAverage_f_T *obj);
+static void matlabCodegenHandle_matlabCod_f(dsp_simulink_MovingAverage_f_T *obj);
 static void SystemProp_matlabCodegenSetAnyP(dsp_simulink_MovingAverage_Fi_T *obj,
   boolean_T value);
 static void Final_test_SystemCore_release(dsp_simulink_MovingAverage_Fi_T *obj);
 static void Final_test_SystemCore_delete(dsp_simulink_MovingAverage_Fi_T *obj);
 static void matlabCodegenHandle_matlabCodeg(dsp_simulink_MovingAverage_Fi_T *obj);
-static void SystemProp_matlabCodegenSetA_fd(codertarget_arduinobase_in_fd_T *obj,
+static void SystemProp_matlabCodegenSet_fdg(codertarget_arduinobase_in_fd_T *obj,
   boolean_T value);
-static void matlabCodegenHandle_matlabCo_fd(codertarget_arduinobase_in_fd_T *obj);
-static void SystemProp_matlabCodegenSetAn_f(codertarget_arduinobase_int_f_T *obj,
[…]

### 2018-09-12 DATA/data_for_paper/final2/Final_test_ert_rtw/Final_test.h

@@ -7,9 +7,9 @@
  *
  * Code generation for model "Final_test".
  *
- * Model version              : 1.42
+ * Model version              : 1.49
  * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
- * C source code generated on : Fri Sep  7 12:34:04 2018
+ * C source code generated on : Wed Sep 12 11:44:58 2018
  *
  * Target selection: ert.tlc
  * Note: GRT includes extra infrastructure and instrumentation for prototyping
@@ -21,8 +21,8 @@
 #ifndef RTW_HEADER_Final_test_h_
 #define RTW_HEADER_Final_test_h_
 #include <math.h>
-#include <float.h>
 #include <string.h>
+#include <float.h>
 #include <stddef.h>
 #ifndef Final_test_COMMON_INCLUDES_
 # define Final_test_COMMON_INCLUDES_
@@ -176,50 +176,60 @@
 
 /* Block signals (default storage) */
 typedef struct {
+  real_T csumrev[9];
   real_T P_bar[4];
   real_T a[4];
   real_T xh_bar[2];
   real_T K[2];
-  real_T TransferFcn1;                 /* '<S4>/Transfer Fcn1' */
-  real_T e;                            /* '<S9>/Sum' */
-  real_T Product;                      /* '<S9>/Product' */
-  real_T Sum2;                         /* '<S9>/Sum2' */
-  real_T Product_m;                    /* '<S3>/Product' */
-  real_T ManualSwitch2;                /* '<Root>/Manual Switch2' */
-  real_T Add;                          /* '<S3>/Add' */
-  real_T Merge;                        /* '<S3>/Merge' */
+  real_T Constant2;                    /* '<Root>/Constant2' */
+  real_T e;                            /* '<S7>/Sum' */
+  real_T TransferFcn1;                 /* '<S3>/Transfer Fcn1' */
+  real_T Sum;                          /* '<S20>/Sum' */
+  real_T Saturation;                   /* '<S7>/Saturation' */
+  real_T Product;                      /* '<S5>/Product' */
+  real_T Sum2;                         /* '<S5>/Sum2' */
+  real_T Product_m;                    /* '<S2>/Product' */
+  real_T ManualPWM;                    /* '<Root>/Manual PWM' */
+  real_T Add;                          /* '<S2>/Add' */
+  real_T Merge;                        /* '<S2>/Merge' */
+  real_T Integrator1;                  /* '<S8>/Integrator1' */
[…]

### 2018-09-12 DATA/data_for_paper/final2/Final_test_ert_rtw/Final_test_data.c

@@ -7,9 +7,9 @@
  *
  * Code generation for model "Final_test".
  *
- * Model version              : 1.42
+ * Model version              : 1.49
  * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
- * C source code generated on : Fri Sep  7 12:34:04 2018
+ * C source code generated on : Wed Sep 12 11:44:58 2018
  *
  * Target selection: ert.tlc
  * Note: GRT includes extra infrastructure and instrumentation for prototyping
@@ -24,22 +24,37 @@
 /* Block parameters (default storage) */
 P_Final_test_T Final_test_P = {
   /* Mask Parameter: DiscretePIDController_I
-   * Referenced by: '<S56>/Integral Gain'
+   * Referenced by: '<S15>/Integral Gain'
    */
   0.01,
 
+  /* Mask Parameter: PIDController3_I
+   * Referenced by: '<S20>/Integral Gain'
+   */
+  5.23638207345188,
+
+  /* Mask Parameter: PIDController3_P
+   * Referenced by: '<S20>/Proportional Gain'
+   */
+  10.1984567978833,
+
   /* Mask Parameter: DiscretePIDController_P
-   * Referenced by: '<S56>/Proportional Gain'
+   * Referenced by: '<S15>/Proportional Gain'
    */
   0.05,
 
   /* Mask Parameter: CompareToConstant_const
-   * Referenced by: '<S52>/Constant'
+   * Referenced by: '<S11>/Constant'
    */
   3.0,
 
   /* Mask Parameter: DetectChange_vinit
-   * Referenced by: '<S55>/Delay Input1'
+   * Referenced by: '<S16>/Delay Input1'
+   */
+  0.0,
+
+  /* Mask Parameter: DetectChange_vinit_c
+   * Referenced by: '<S14>/Delay Input1'
    */
   0.0,
 
@@ -49,27 +64,32 @@ P_Final_test_T Final_test_P = {
   0.8,
 
   /* Expression: 0.01
-   * Referenced by: '<S4>/Analog Input'
+   * Referenced by: '<S3>/Analog Input'
    */
   0.01,
 
-  /* Computed Parameter: TransferFcn1_A
-   * Referenced by: '<S4>/Transfer Fcn1'
+  /* Expression: 0
[…]

### 2018-09-12 DATA/data_for_paper/final2/Final_test_ert_rtw/Final_test_dt.h

@@ -7,9 +7,9 @@
  *
  * Code generation for model "Final_test".
  *
- * Model version              : 1.42
+ * Model version              : 1.49
  * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
- * C source code generated on : Fri Sep  7 12:34:04 2018
+ * C source code generated on : Wed Sep 12 11:44:58 2018
  *
  * Target selection: ert.tlc
  * Note: GRT includes extra infrastructure and instrumentation for prototyping
@@ -38,6 +38,8 @@ static uint_T rtDataTypeSizes[] = {
   2*sizeof(uint32_T),
   sizeof(dsp_simulink_MovingAverage_Fi_T),
   sizeof(dsp_private_SlidingWindowAver_T),
+  sizeof(dsp_simulink_MovingAverage_f_T),
+  sizeof(dsp_private_SlidingWindowAv_f_T),
   sizeof(codertarget_arduinobase_int_f_T),
   sizeof(codertarget_arduinobase_in_fd_T)
 };
@@ -60,45 +62,51 @@ static const char_T * rtDataTypeNames[] = {
   "timer_uint32_pair_T",
   "dsp_simulink_MovingAverage_Fi_T",
   "dsp_private_SlidingWindowAver_T",
+  "dsp_simulink_MovingAverage_f_T",
+  "dsp_private_SlidingWindowAv_f_T",
   "codertarget_arduinobase_int_f_T",
   "codertarget_arduinobase_in_fd_T"
 };
 
 /* data type transitions for block I/O structure */
 static DataTypeTransition rtBTransitions[] = {
-  { (char_T *)(&Final_test_B.TransferFcn1), 0, 0, 24 }
+  { (char_T *)(&Final_test_B.Constant2), 0, 0, 28 }
   ,
+
+  { (char_T *)(&Final_test_DW.gobj_0), 17, 0, 2 },
 
   { (char_T *)(&Final_test_DW.obj), 14, 0, 1 },
 
-  { (char_T *)(&Final_test_DW.gobj_0), 15, 0, 2 },
-
-  { (char_T *)(&Final_test_DW.obj_g), 17, 0, 1 },
-
   { (char_T *)(&Final_test_DW.obj_n), 16, 0, 1 },
 
-  { (char_T *)(&Final_test_DW.DelayInput1_DSTATE), 0, 0, 8 },
[…]

### 2018-09-12 DATA/data_for_paper/final2/Final_test_ert_rtw/Final_test_private.h

@@ -7,9 +7,9 @@
  *
  * Code generation for model "Final_test".
  *
- * Model version              : 1.42
+ * Model version              : 1.49
  * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
- * C source code generated on : Fri Sep  7 12:34:04 2018
+ * C source code generated on : Wed Sep 12 11:44:58 2018
  *
  * Target selection: ert.tlc
  * Note: GRT includes extra infrastructure and instrumentation for prototyping
@@ -40,7 +40,7 @@
 # define rtmSetTPtr(rtm, val)          ((rtm)->Timing.t = (val))
 #endif
 
-/* Used by FromWorkspace Block: '<S8>/FromWs' */
+/* Used by FromWorkspace Block: '<S4>/FromWs' */
 #ifndef rtInterpolate
 # define rtInterpolate(v1,v2,f1,f2)    (((v1)==(v2))?((double)(v1)): (((f1)*((double)(v1)))+((f2)*((double)(v2)))))
 #endif

### 2018-09-12 DATA/data_for_paper/final2/Final_test_ert_rtw/Final_test_targ_data_map.m

@@ -28,191 +28,227 @@
     ;%
     ;% Auto data (Final_test_P)
     ;%
-      section.nData     = 41;
-      section.data(41)  = dumData; %prealloc
+      section.nData     = 49;
+      section.data(49)  = dumData; %prealloc
       
 	  ;% Final_test_P.DiscretePIDController_I
 	  section.data(1).logicalSrcIdx = 0;
 	  section.data(1).dtTransOffset = 0;
 	
-	  ;% Final_test_P.DiscretePIDController_P
+	  ;% Final_test_P.PIDController3_I
 	  section.data(2).logicalSrcIdx = 1;
 	  section.data(2).dtTransOffset = 1;
 	
-	  ;% Final_test_P.CompareToConstant_const
+	  ;% Final_test_P.PIDController3_P
 	  section.data(3).logicalSrcIdx = 2;
 	  section.data(3).dtTransOffset = 2;
 	
-	  ;% Final_test_P.DetectChange_vinit
+	  ;% Final_test_P.DiscretePIDController_P
 	  section.data(4).logicalSrcIdx = 3;
 	  section.data(4).dtTransOffset = 3;
 	
-	  ;% Final_test_P.Gain_Gain
+	  ;% Final_test_P.CompareToConstant_const
 	  section.data(5).logicalSrcIdx = 4;
 	  section.data(5).dtTransOffset = 4;
 	
-	  ;% Final_test_P.AnalogInput_SampleTime
+	  ;% Final_test_P.DetectChange_vinit
 	  section.data(6).logicalSrcIdx = 5;
 	  section.data(6).dtTransOffset = 5;
 	
-	  ;% Final_test_P.TransferFcn1_A
+	  ;% Final_test_P.DetectChange_vinit_c
 	  section.data(7).logicalSrcIdx = 6;
 	  section.data(7).dtTransOffset = 6;
 	
-	  ;% Final_test_P.TransferFcn1_C
+	  ;% Final_test_P.Gain_Gain
 	  section.data(8).logicalSrcIdx = 7;
 	  section.data(8).dtTransOffset = 7;
 	
-	  ;% Final_test_P.Wind_des_Value
+	  ;% Final_test_P.AnalogInput_SampleTime
 	  section.data(9).logicalSrcIdx = 8;
 	  section.data(9).dtTransOffset = 8;
 	
-	  ;% Final_test_P.RunSim_Value
[…]

### 2018-09-12 DATA/data_for_paper/final2/Final_test_ert_rtw/Final_test_types.h

@@ -7,9 +7,9 @@
  *
  * Code generation for model "Final_test".
  *
- * Model version              : 1.42
+ * Model version              : 1.49
  * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
- * C source code generated on : Fri Sep  7 12:34:04 2018
+ * C source code generated on : Wed Sep 12 11:44:58 2018
  *
  * Target selection: ert.tlc
  * Note: GRT includes extra infrastructure and instrumentation for prototyping
@@ -35,7 +35,20 @@ typedef struct {
 
 #endif                                 /*typedef_dsp_private_SlidingWindowAver_T*/
 
-/* Custom Type definition for MATLABSystem: '<S4>/Analog Input' */
+#ifndef typedef_dsp_private_SlidingWindowAv_f_T
+#define typedef_dsp_private_SlidingWindowAv_f_T
+
+typedef struct {
+  int32_T isInitialized;
+  boolean_T isSetupComplete;
+  real_T pCumSum;
+  real_T pCumSumRev[9];
+  real_T pCumRevIndex;
+} dsp_private_SlidingWindowAv_f_T;
+
+#endif                                 /*typedef_dsp_private_SlidingWindowAv_f_T*/
+
+/* Custom Type definition for MATLABSystem: '<S3>/Analog Input' */
 #include "MW_SVD.h"
 #ifndef typedef_cell_wrap_Final_test_T
 #define typedef_cell_wrap_Final_test_T
@@ -116,6 +129,21 @@ typedef struct {
 } dsp_simulink_MovingAverage_Fi_T;
 
 #endif                                 /*typedef_dsp_simulink_MovingAverage_Fi_T*/
+
+#ifndef typedef_dsp_simulink_MovingAverage_f_T
+#define typedef_dsp_simulink_MovingAverage_f_T
+
+typedef struct {
+  boolean_T matlabCodegenIsDeleted;
+  int32_T isInitialized;
+  boolean_T isSetupComplete;
+  boolean_T TunablePropsChanged;
+  cell_wrap_Final_test_T inputVarSize;
+  dsp_private_SlidingWindowAv_f_T *pStatistic;
+  int32_T NumChannels;
+} dsp_simulink_MovingAverage_f_T;
+
+#endif                                 /*typedef_dsp_simulink_MovingAverage_f_T*/
 
 /* Parameters (default storage) */
 typedef struct P_Final_test_T_ P_Final_test_T;

### 2018-09-12 DATA/data_for_paper/final2/Final_test_ert_rtw/html/define.js

@@ -10,36 +10,42 @@ this.def["Final_test_X"] = {file: "Final_test_c.html",line:29,type:"var"};
 this.def["Final_test_DW"] = {file: "Final_test_c.html",line:32,type:"var"};
 this.def["Final_test_M_"] = {file: "Final_test_c.html",line:35,type:"var"};
 this.def["Final_test_M"] = {file: "Final_test_c.html",line:36,type:"var"};
-this.def["rt_ertODEUpdateContinuousStates"] = {file: "Final_test_c.html",line:57,type:"fcn"};
-this.def["arduino_PWMOutput_arduino_PWMOu"] = {file: "Final_test_c.html",line:134,type:"fcn"};
-this.def["rt_powd_snf"] = {file: "Final_test_c.html",line:162,type:"fcn"};
-this.def["SystemProp_matlabCodegenSetAnyP"] = {file: "Final_test_c.html",line:208,type:"fcn"};
-this.def["Final_test_SystemCore_release"] = {file: "Final_test_c.html",line:215,type:"fcn"};
-this.def["Final_test_SystemCore_delete"] = {file: "Final_test_c.html",line:232,type:"fcn"};
-this.def["matlabCodegenHandle_matlabCodeg"] = {file: "Final_test_c.html",line:238,type:"fcn"};
-this.def["SystemProp_matlabCodegenSetA_fd"] = {file: "Final_test_c.html",line:249,type:"fcn"};
-this.def["matlabCodegenHandle_matlabCo_fd"] = {file: "Final_test_c.html",line:256,type:"fcn"};
-this.def["SystemProp_matlabCodegenSetAn_f"] = {file: "Final_test_c.html",line:266,type:"fcn"};
-this.def["matlabCodegenHandle_matlabCod_f"] = {file: "Final_test_c.html",line:273,type:"fcn"};
-this.def["Final_test_step"] = {file: "Final_test_c.html",line:284,type:"fcn"};
-this.def["Final_test_derivatives"] = {file: "Final_test_c.html",line:866,type:"fcn"};
-this.def["Final_test_initialize"] = {file: "Final_test_c.html",line:885,type:"fcn"};
-this.def["Final_test_terminate"] = {file: "Final_test_c.html",line:1110,type:"fcn"};
-this.def["B_Final_test_T"] = {file: "Final_test_h.html",line:201,type:"type"};
-this.def["DW_Final_test_T"] = {file: "Final_test_h.html",line:251,type:"type"};
[…]

### 2018-09-12 DATA/data_for_paper/final2/Final_test_ert_rtw/rtGetNaN.c

@@ -7,9 +7,9 @@
  *
  * Code generation for model "Final_test".
  *
- * Model version              : 1.42
+ * Model version              : 1.49
  * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
- * C source code generated on : Fri Sep  7 12:34:04 2018
+ * C source code generated on : Wed Sep 12 11:44:58 2018
  *
  * Target selection: ert.tlc
  * Note: GRT includes extra infrastructure and instrumentation for prototyping

### 2018-09-12 DATA/data_for_paper/final2/Final_test_ert_rtw/rtmodel.h

@@ -7,9 +7,9 @@
  *
  * Code generation for model "Final_test".
  *
- * Model version              : 1.42
+ * Model version              : 1.49
  * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
- * C source code generated on : Fri Sep  7 12:34:04 2018
+ * C source code generated on : Wed Sep 12 11:44:58 2018
  *
  * Target selection: ert.tlc
  * Note: GRT includes extra infrastructure and instrumentation for prototyping
@@ -23,7 +23,7 @@
  * Code generation for Simulink model "Final_test".
  *
  * Simulink Coder version                : 8.14 (R2018a) 06-Feb-2018
- * C source code generated on : Fri Sep  7 12:34:04 2018
+ * C source code generated on : Wed Sep 12 11:44:58 2018
  *
  * Note that the generated code is not dependent on this header file.
  * The file is used in cojuction with the automatic build procedure.

### 2018-09-12 DATA/data_for_paper/final2/datacol.m

@@ -1,7 +1,7 @@
-prop_faultT= csvread("../final3/paper_data/prop_fault.csv",1,0);
+wdpT= csvread("../final3/paper_data/wind_disturb_pulse.csv",1,0);
 %  curr_testtorq = pt;
-[r,c] = find(prop_faultT(:,10) == 0);
-prop_faultT(r,:) = [];
+[r,c] = find(wdpT(:,10) == 0);
+wdpT(r,:) = [];
 
 % [r,c] = find(curr_testtorq(:,9) == 0);
 % 

### 2018-09-13 paper/drafts/draft_final.tex
Killing the paper

@@
 	\section{1}
-	\subsection{1.1}
-	\subsection{1.2}
+	\subsection{Intro to mav and control system architecture}
+	Multirotor Aerial Vehicles (MAV), specifically quadrotors, have become quite commonplace in many industries ranging from filmography to racing to even military operations.
+Over the past decade, there has been an incredible amount of research and advancement within this field leading to its proliferation and allowing for the technology to become more accessible.
+One of the major areas of research regarding MAV's is the control system that directs the motor-rotor system.
+The control mechanism can be as simple as a motor-rotor control, all the way to controlling the torque, or thrust or one of many other variables.
+The control of the motor-rotor has to account for multiple different factors, from the ambient wind speed, the rotation, the pitch of the propeller, all the way to the high level control system of the ESC.
+\\
+	In general, there are two different types of control loops; open and closed.
+Open control loops are what the majority of MAV control systems are.
+There is a flight controller, that sends a signal to the ESC that applies a particular voltage to the motor based on previously calibrated settings.
+In this method, the final result of the motor spinning is unknown to the flight controller.
+Therefore given any disturbances, there will be large variances in the response of the overall system.
+In response to these systems there are smarter, closed loop control.
+This is the type of control we will focus on.
+Closed loop systems provide a certain way to measure the output of the rotor based on the input from the FC.
+This allows for a smarter, more robust system and greater control of the output.
+\\
+	\subsection{Intro to the problem}
+	The main problem we are trying to answer is how to create an effective, efficient, and reasonable solution to having a closed loop control system.
+This would include having a type of sensor which would measure the thrust output of the propellor and relay that onto the ESC so that the ESC can control the thrust output accordingly.
 	\subsection{1.3}
 	\subsection{1.4}
+	The scope of this paper is to introduce a wind sensor as an external sensor and develop the relationship between the downwash rotor wind speed and the thrust vector of the propeller.
+Doing that we can implement a control system by which the wind sensor can be used to maintain a thrust given disturbances or faults within the system.
+	\section{2}
+	\subsection{Wind sensor math/theory}
+	We have to start by defining the three different velocities that apply to a propeller.\\
+	\begin{eqnarray}
+	\label{e1}
+	v_x , v_y , v_z \\
+	\label{e2}
+	v^s_{x} , v^s_{y} , v^s_{z} \\
+	\label{e3}
+	v^i_{x} , v^i_{y} , v^i_{z}
+	\end{eqnarray}
+	Where equation \ref{e1} Is the velocity of the drone, the body frame velocity, equation \ref{e2} is the velocity of the wind approaching the propellers, the stream velocity, and equation \ref{e3} is the induced velocity of the propellers.\\
+	Since we are doing only the static tests, we do not have to worry about horizontal winds, so we can say 
+	\begin{eqnarray}
+	\nonumber
+	v_s = v^s_{z}\\
+	\nonumber
+	v_i = v^i_{z}
+	\end{eqnarray}
+	As well, since we have stationary system, the frame velocities can be ignored as well. What the wind sensor will notice is 
+	\begin{equation}
+	v_{tot} = v_{i} + v_{s}
+	\label{vtot}
+	\end{equation}	
+	Generally, when no disturbances are applied we can assume that $v_s$ is $0$ as a means of simplifying our system.
 
-	\section{2}
-	\subsection{2.1}
-	\subsection{2.2}
+	Modern Device \cite{md} gives us the equation 
+	\begin{eqnarray}
+		WS = \frac{(V - V_{z})*0.087288}{3.038517 * T_{c} ^{0.115157}} ^ {3.009364}
+		\label{wind_speed}
+	\end{eqnarray}
+	Where $WS$ is the wind speed,in miles/hour, $V$ is the measured voltage, $V$ is the calibrated voltage when there is no wind, and $T_c$ is the current temperature in celsius which is also measured by the sensor.
+While the basis of this paper is around the wind speed, it is not important to know the exact wind speed and therefore throughout the rest of our calculations, we only consider the measured voltage.
+
+	%How does wind speed relate to voltage
+
+	To explain the relation of wind to thrust, let's radically simplify it and assume it is a linear system.
+For the first case let this be in a situation with no stream velocity, or $v_s = 0$.
+With this being the case, it can be stated that
+	\begin{equation}
+	F_p= \frac{\partial p}{\partial t}
+	\label{fvm}
+	\end{equation}
+	where $F_p$ is the force the propeller exerts, $p$ is momentum and $t$ is time. From this we can expand this to 
+	\begin{equation}
+	F_p= \frac{mv_{tot} - mv_{s}}{\Delta t} 
+	\label{fvm2}
+	\end{equation}
+	where $m$ is the mass of air flowing. If we assume that this is over a 1 second time span we get
+	\begin{equation}
+	F_p= m*(v_{tot}-v{s}) 
+	\label{fvm3}
+	\end{equation}
+	Now to consider the efficiency of the propeller we can say 
+	\begin{eqnarray}	
+	V_{i}\prime = V_{i}* \gamma\\
+	V_{tot}\prime = V_i\prime + V_s
+	\label{eff}
+	\end{eqnarray}
+	where $\gamma$ is some efficiency factor $0 < \gamma < 1$ which degrades as the stream velocity $v_s$ approaches $v_i$ \cite{someone}. In doing so we can assume that for a non-zero $v_s$ 
+	\begin{equation}
+	F_p\prime < F_p
+	\end{equation}
+	This is the reasoning behind why as winds buffett a drone mid-flight, the drone's thrust vector tends to drop. 
+	\subsection{Kalman Math}
 	\subsection{2.3}
@@
 	The wind sensor we have chosen to use is the "Modern Device- Wind Sensor Rev.
-P" \cite{wind_sensor}.
+P" \cite{md}.
 This device is a hot wire anemometer that is designed to measure wind from any direction.
@@
 	Once the characteristics of the wind sensor were determined we ran tests to ensure the viability of our algorithm and if it would respond to external stimuli the way we expected.
+The first test that we ran was to measure the response of the kalman filter and ensure that our thrust calculation was accurate in relation to the testbed recorded thrust.
+To do this we measured  As seen in fig \ref{kalman} the kalman filter, while noisy due to the wind variations in the wind sensor data, follows the thrust value from the testbed closely.
+This result gives us the confidence to setup the PID based on the kalman filter's value.
+
+	To ensure the functionality of the controller we set up several faults and disturbances to test the response of the system.
+The first step was to create an external disturbance by placing another propeller and blowing wind perpendicular to the axis of the main propeller.
+This would be akin to horizontal crosswind flow across the propeller.
+	\begin{figure}
+		\label{content...}
+	\end{figure}
+	 Based on the results of fig \ref{wind_disturb}, the control algorithm can determine the appropriate correction for such a disturbance through
+	\begin{figure}
+		content...
+	\end{figure}
+	Next we 
 	\subsection{4.3}
@@
 		\bibitem{rcb} https://www.rcbenchmark.com/dynamometer-series-1580/
-		\bibitem{wind_sensor} https://moderndevice.com/product/wind-sensor-rev-p/
+		\bibitem{md} https://moderndevice.com/product/wind-sensor-rev-p/
 		\bibitem{hot_wire} Extended Applications of the Hot‐Wire Anemometer, Stanley Corrsin,Review of Scientific Instruments 1947 18:7, 469-471

### 2018-09-13 paper/drafts/draft_final.tex
Adding more text to the paper

@@
-\documentclass[twocolumn]{article}
-\usepackage{subfig}
+\documentclass[conference]{IEEEtran}
+\usepackage{amsmath,amssymb,amsfonts}
+\usepackage{algorithmic}
 \usepackage{graphicx}
+\usepackage{textcomp}
+\usepackage{xcolor}
+\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
+		T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
 \begin{document}
-	\title{\begin{titlepage}
-			My paper
-	\end{titlepage}}
+\title{Paper Title*\\
+	{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
+		should not be used}
+	\thanks{Identify applicable funding agency here. If none, delete this.}
+}
+
+\author{\IEEEauthorblockN{1\textsuperscript{st} Adithya Ravishankara}
+	\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
+		\textit{name of organization (of Aff.)}\\
+		City, Country \\
+		email address}
+	\and
+	\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
+	\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
+		\textit{name of organization (of Aff.)}\\
+		City, Country \\
+		email address}
+	\and
+	\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
+	\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
+		\textit{name of organization (of Aff.)}\\
+		City, Country \\
+		email address}
+	}
 	\section{1}
@@
 This would include having a type of sensor which would measure the thrust output of the propellor and relay that onto the ESC so that the ESC can control the thrust output accordingly.
-	\subsection{1.3}
+	\subsection{Lit review}
+		Mahoney et al (2017) have developed an algorithm which bases the control system around an estimation of the thrust from a propeller based on the voltage and current given to the motor by the ESC.
+Their system works to maintain a thrust given some disturbance.
+From looking over their algorithm, they have a system which runs through a for loop before detecting an appropriate response to extraneous forces.
+This system while it allows for a valid estimation of the thrust, it is a complex system that requires relatively heavy computation and therefore is not feasible.
+As well this method of thrust based control requires a significant amount of calibration for both the propellers and
+
+	Real-Time Wind Speed Estimation and Compensation for Improved Flight
+
+	Streit developed a control system to compensate for wind disturbances using a pitot-tube sensor coupled with the GPS sensor along with an accompanying estimation algorithm.
+While this seems similar to the Yeo et al paper, there are some major differences.
+Streit has only one pitot sensor onboard the UAV which is uni-directional and therefore only applies to forward motion.
+As well the pitot-tube is made of brass and therefore not feasible for all smaller UAV's as it will be too heavy.
+
+	Onboard Flow Sensing for Downwash Detection and Avoidance with a Small Quadrotor Helicopter
+
+	Yeo et al have developed a system similar to our proposed idea by fabricating pitot tubes to sit below each propeller and measure the rotor downwash and compare them to the estimated expected wind speed.
+Their system is ultimately used to localize external noise from other UAV's and therefore an exceedingly accurate measurement is not as important.
+While the sensor can accurately measure wind speed accurately during vertical motion, there is significant divergence from the ground speed measurement during lateral movement.
+As well there is a very limited range of speeds that are available for measurement from the probe.
 	\subsection{1.4}
@@
 	\end{eqnarray}
-	Where equation \ref{e1} Is the velocity of the drone, the body frame velocity, equation \ref{e2} is the velocity of the wind approaching the propellers, the stream velocity, and equation \ref{e3} is the induced velocity of the propellers.\\
+	Where \ref{e1} Is the velocity of the drone, the body frame velocity, \ref{e2} is the velocity of the wind approaching the propellers, the stream velocity, and \ref{e3} is the induced velocity of the propellers.\\
 	Since we are doing only the static tests, we do not have to worry about horizontal winds, so we can say 
@@
 	Generally, when no disturbances are applied we can assume that $v_s$ is $0$ as a means of simplifying our system.
-
 	Modern Device \cite{md} gives us the equation 
@@
 While the basis of this paper is around the wind speed, it is not important to know the exact wind speed and therefore throughout the rest of our calculations, we only consider the measured voltage.
-
 	%How does wind speed relate to voltage
-
-	To explain the relation of wind to thrust, let's radically simplify it and assume it is a linear system.
-For the first case let this be in a situation with no stream velocity, or $v_s = 0$.
-With this being the case, it can be stated that
+	To explain the relation of wind to thrust, let's radically simplify it and assume it is a linear system.  With this being the case, it can be stated that 
 	\begin{equation}
@@
 	where $F_p$ is the force the propeller exerts, $p$ is momentum and $t$ is time. From this we can expand this to 
-	\begin{equation}
-	F_p= \frac{mv_{tot} - mv_{s}}{\Delta t} 
+	\begin{eqnarray}
+	F_p= \frac{mv_{tot} - mv_{s}}{\Delta t}\\ 
 	\label{fvm2}
-	\end{equation}
-	where $m$ is the mass of air flowing. If we assume that this is over a 1 second time span we get
-	\begin{equation}
 	F_p= m*(v_{tot}-v{s}) 
 	\label{fvm3}
-	\end{equation}
-	Now to consider the efficiency of the propeller we can say 
+	\end{eqnarray}
+	where $m$ is the mass of air flowing. Then making the assumption that $\Delta t = 1$ we get \ref{fvm3}.	Now to consider the efficiency of the propeller we can say 
 	\begin{eqnarray}	
-	V_{i}\prime = V_{i}* \gamma\\
-	V_{tot}\prime = V_i\prime + V_s
+	v_{i}\prime = v_{i}* \gamma\\
+	v_{tot}\prime = v_i\prime + v_s
 	\label{eff}
 	\end{eqnarray}
-	where $\gamma$ is some efficiency factor $0 < \gamma < 1$ which degrades as the stream velocity $v_s$ approaches $v_i$ \cite{someone}. In doing so we can assume that for a non-zero $v_s$ 
+	where $\gamma$ is some efficiency factor where $0 \leq  \gamma \leq 1$ which degrades as the stream velocity $v_s$ approaches $v_i$\cite{someone}. In doing so we can assume that for a non-zero $v_s$ 
 	\begin{equation}
@@
 	\end{equation}
-	This is the reasoning behind why as winds buffett a drone mid-flight, the drone's thrust vector tends to drop. 
+	This is the reasoning behind why as winds buffet a drone mid-flight, the drone's thrust vector tends to drop. Hence we can measure this change in thrust and correct for it.
 	\subsection{Kalman Math}
@@
 	\subsection{2.4}
-
 	\section{3}
@@
 	\subsection{Experimental Setup- How we set up the kalman/Algorithm}
-	\begin{figure}[b]
+	\begin{figure}[]
 		\includegraphics[width=\textwidth]{block_diagram}
@@
 
-	These values are then passed through a Kalman Filter weighted for the wind sensor.
+	These values are then passed through a Kalman Filter weighted towards the wind sensor.
 This method allows for the system to accurately determine the thrust value output while reducing noise due to the nature of the wind.
-Next this value is passed to a PID controller which checks the current thrust value to the desired thrust value and outputs a thrust value.
-Lastly a polynomial function converts the thrust value back to PWM.
-	\begin{eqnarray}
-	PWM = -.1746*Thrust^4 + 1.008*Thrust^3\\ 
-	- 3.409*Thrust*2 + 12.29*Thrust + 1.8430 \nonumber
-	\label{pwm_poly}
-	\end{eqnarray}
+Next this value is passed to a PI controller which generates the appropriate response for the error between desired and measured.
+
 	\subsection{The tests}
-	Once the characteristics of the wind sensor were determined we ran tests to ensure the viability of our algorithm and if it would respond to external stimuli the way we expected.
+	To ensure the viability of our algorithm and if it would respond to external stimuli the way we expected, we performed several tests that caused significant errors in the propeller's response.
 The first test that we ran was to measure the response of the kalman filter and ensure that our thrust calculation was accurate in relation to the testbed recorded thrust.
 To do this we measured  As seen in fig \ref{kalman} the kalman filter, while noisy due to the wind variations in the wind sensor data, follows the thrust value from the testbed closely.
-This result gives us the confidence to setup the PID based on the kalman filter's value.
+This result gives us the confidence to setup the PI based on the kalman filter's value.
 
@@
 
-	\subsection{5.1}
-	\subsection{5.2}
-	\subsection{5.3}
+	\subsection{Reiteration of results}
+	In this paper we introduced a hot wire anemometer with the function of measuring the downwash rotor wind speed on MAV's. By this measurement we can calculate the thrust output of the propeller and 
+	\subsection{Reiteration of applications}
+	\subsection{Shortcomings and limitations}
 	\subsection{5.4}

### 2018-09-14 paper/drafts/draft_final.tex

@@
 }
-
 \author{\IEEEauthorblockN{1\textsuperscript{st} Adithya Ravishankara}
@@
 	}
-	\section{1}
+	\section{Intro}
 	\subsection{Intro to mav and control system architecture}
@@
 One of the major areas of research regarding MAV's is the control system that directs the motor-rotor system.
-The control mechanism can be as simple as a motor-rotor control, all the way to controlling the torque, or thrust or one of many other variables.
-The control of the motor-rotor has to account for multiple different factors, from the ambient wind speed, the rotation, the pitch of the propeller, all the way to the high level control system of the ESC.
+The control mechanism ranges in complexity from the common motor-rotor control, to a more complex system that takes into consideration parameters such as thrust or torque.
+The control of the motor-rotor has to account for multiple different external and internal factors, from the ambient wind speed, the rotation speed of the propeller (RPM), the pitch of the propeller, and for more complex controllers, the internal loops of the Electronic Speed Controller (ESC) or Flight Controller (FC).
 \\
@@
 Open control loops are what the majority of MAV control systems are.
-There is a flight controller, that sends a signal to the ESC that applies a particular voltage to the motor based on previously calibrated settings.
+There is an FC, that sends a value to the ESC that applies a particular voltage to the motor based on previously calibrated settings.
 In this method, the final result of the motor spinning is unknown to the flight controller.
@@
 	\subsection{Intro to the problem}
-	The main problem we are trying to answer is how to create an effective, efficient, and reasonable solution to having a closed loop control system.
-This would include having a type of sensor which would measure the thrust output of the propellor and relay that onto the ESC so that the ESC can control the thrust output accordingly.
+	The problem we address with this paper is on how to create an effective, efficient and reasonable closed loop control system for MAV motor-rotors.
+This would require a method to measure the thrust output of the MAV, relay the information back to the system upon which the system would correct for any errors due to disturbances.
 	\subsection{Lit review}
@@
 As well this method of thrust based control requires a significant amount of calibration for both the propellers and
-
 	Real-Time Wind Speed Estimation and Compensation for Improved Flight
-
 	Streit developed a control system to compensate for wind disturbances using a pitot-tube sensor coupled with the GPS sensor along with an accompanying estimation algorithm.
@@
 As well the pitot-tube is made of brass and therefore not feasible for all smaller UAV's as it will be too heavy.
-
 	Onboard Flow Sensing for Downwash Detection and Avoidance with a Small Quadrotor Helicopter
-
 	Yeo et al have developed a system similar to our proposed idea by fabricating pitot tubes to sit below each propeller and measure the rotor downwash and compare them to the estimated expected wind speed.
@@
 As well there is a very limited range of speeds that are available for measurement from the probe.
-	\subsection{1.4}
+	\subsection{Scope and application}
 	The scope of this paper is to introduce a wind sensor as an external sensor and develop the relationship between the downwash rotor wind speed and the thrust vector of the propeller.
-Doing that we can implement a control system by which the wind sensor can be used to maintain a thrust given disturbances or faults within the system.
+Doing that we can implement a closed loop control system by which the wind sensor can be used to maintain a thrust given disturbances or faults within the system.
+This allows for the MAV to have a more accurate and reliable response but also allows for a more agile system.
+In this sense for applications such as drone racing, filmography, and even research, it would allow for a smoother and and more stable system.
 	\section{2}
@@
 	Where \ref{e1} Is the velocity of the drone, the body frame velocity, \ref{e2} is the velocity of the wind approaching the propellers, the stream velocity, and \ref{e3} is the induced velocity of the propellers.\\
-	Since we are doing only the static tests, we do not have to worry about horizontal winds, so we can say 
+	Since we are doing only the static tests in this paper, we can disregard the horizontal components of the wind as well as the body frame velocities. Then we can state 
 	\begin{eqnarray}
@@
 While there is possibility for the wind sensor to measure higher wind speeds, there is a significant amount of noise even with the addition of a low-pass filter, hence we decided to limit the max speed of our experiment.
-
 	Another factor that we deem is important to characterize is the speed of response to change of wind speed.
@@
 By doing this we found that there was a negligible lag time of less than $10 ms$, which is our resolution for each measurement.
-
 	Lastly we measured the location of the wind sensor in relation to the propellers.
@@
 Resulting in a map as seen in figure \ref{area}.
-
 	By characterizing the wind sensor, we can ensure that it is in the optimal configuration for us to collect data.
-
 	\section{Results}
-
 	\subsection{Experimental Setup- How we set up the kalman/Algorithm}
@@
 	\end{figure}
-
 	We developed a control architecture as pictured in fig \ref{block_diagram} where there are two sources of measurement for the thrust value.
@@
 	\end{equation}
-
 	The second measurement of thrust is a polynomial function that converts the recorded PWM value that is used to control the propeller to thrust. \newline
@@
 	\end{eqnarray}
-
 	These values are then passed through a Kalman Filter weighted towards the wind sensor.
@@
 Next this value is passed to a PI controller which generates the appropriate response for the error between desired and measured.
-
 	\subsection{The tests}
@@
 This result gives us the confidence to setup the PI based on the kalman filter's value.
-
 	To ensure the functionality of the controller we set up several faults and disturbances to test the response of the system.
@@
 	\subsection{4.3}
-	\subsection{4.4}
+	\subsection{Shortcomings and limitations}
+	low wind speed. Have not accounted for multiple sources of wind. fixed and controlled environment. only one propeller. 
+	\section{5}
+	\subsection{Reiteration of results}
+	In this paper we presented a closed loop control system for the purposes of controlling MAV rotor systems by the introduction of a hot wire anemometer.
+The anemometer measures the rate of wind flow from the downwash of the MAV rotor and there is a linear relationship that is developed between wind flow velocity and the thrust output of the system.
+Through this relationship we developed a PI controller that corrects for any errors in thrust output due to both internal and external disturbances.
+	\subsection{Reiteration of applications}
 
-	\section{5}
-
-	\subsection{Reiteration of results}
-	In this paper we introduced a hot wire anemometer with the function of measuring the downwash rotor wind speed on MAV's. By this measurement we can calculate the thrust output of the propeller and 
-	\subsection{Reiteration of applications}
-	\subsection{Shortcomings and limitations}
+	\subsection
 	\subsection{5.4}
-
 	\begin{thebibliography}{99}

### 2018-09-14 paper/drafts/litrev.tex

@@
 
-\$ Control systems on multirotor aerial vehicles have had many different iterations, each of which have added a significant level of control to the system.
+Control systems on multirotor aerial vehicles have had many different iterations, each of which have added a significant level of control to the system.
 The control mechanism can be as simple as a motor-rotor control, all the way to controlling the torque, or thrust or one of many other variables.

### 2018-09-15 paper/drafts/draft_final.tex
PAper

@@
 \usepackage{graphicx}
+\graphicspath{images}
 \usepackage{textcomp}
@@
 	\subsection{Intro to the problem}
-	The problem we address with this paper is on how to create an effective, efficient and reasonable closed loop control system for MAV motor-rotors.
-This would require a method to measure the thrust output of the MAV, relay the information back to the system upon which the system would correct for any errors due to disturbances.
+	The main problem we address in this paper is determining a type of sensor that can accurately and efficiently measure the output of the propellers in a meaningful way such that a closed control loop can be devised.
 	\subsection{Lit review}
+	There has been an enormous strive to develop methods to obtain a closed loop control system for MAV's.
+The methods range from estimation to sensing based on different vectors.
+The majority of the estimation based controls rely on the voltage or current draw by the motors.
+Mahoney et al \cite{Mahoney1} devised such a system which estimates the thrust using a for loop based calculation of the thrust.
+This system while it allows for a valid estimation of the thrust, it is a complex system that requires relatively heavy computation and therefore is not feasible.
+As well their system requires heavy calibration and would not be easily transferable between systems.
+Similarly Awan et al \cite{awan} developed an adaptive observer based thrust estimation system.
+This method allowed for the MAV to maintain a hover with higher precision compared to previous methods involving thrust estimation.
+The main issue along this method is that their paper only accounts for hover not flight, as well their models were based around a linearized system and any nonlinear disturbances would cause errors in their system.
+In contrast Sydney et al \cite{sydney} developed a highly complex system where they modeled the entire system, both linear and nonlinear.
+By doing so their
+
 	Mahoney et al (2017) have developed an algorithm which bases the control system around an estimation of the thrust from a propeller based on the voltage and current given to the motor by the ESC.
@@
 	\subsection{Scope and application}
-	The scope of this paper is to introduce a wind sensor as an external sensor and develop the relationship between the downwash rotor wind speed and the thrust vector of the propeller.
-Doing that we can implement a closed loop control system by which the wind sensor can be used to maintain a thrust given disturbances or faults within the system.
-This allows for the MAV to have a more accurate and reliable response but also allows for a more agile system.
-In this sense for applications such as drone racing, filmography, and even research, it would allow for a smoother and and more stable system.
+	The scope of this paper is to introduce a hot wire anemometer, or wind sensor, as viable option for an external sensor and develop the relationship between the downwash rotor wind speed and the thrust vector of the propeller.
+With the addition of the sensor, we generate a control system based around the measurements of the wind sensor, using a kalman filter and a simple PI controller.
+This allows the system to be more robust towards external disturbances such as wind gusts and also more tolerant to internal errors.
+One other application of the wind sensor is to have an onboard fault detection system, which is in contrast to the majority of prior research, where the fault detection is more of an estimation.
+The applications for the sensor we introduce can be in any field where MAV's are prevalent, such as filmography, racing, and any other area that requires, agile and reliable control.
 	\section{2}
@@
 	\subsection{Experimental Setup- How we set up the kalman/Algorithm}
-	\begin{figure}[]
-		\includegraphics[width=\textwidth]{block_diagram}
-		\caption{Block Diagram}
-		\label{block_diagram}
-	\end{figure}
+
 	We developed a control architecture as pictured in fig \ref{block_diagram} where there are two sources of measurement for the thrust value.
-The first, main value, is from the wind sensor which is measured through an Arduino.
+the primary value is from the wind sensor which is measured through an Arduino.
 The voltage value that the arduino measures is then converted to a thrust value through the power function
@@
 	\end{equation}
-	The second measurement of thrust is a polynomial function that converts the recorded PWM value that is used to control the propeller to thrust. \newline
+	The secondary measurement of thrust is a polynomial function that converts the output PWM value that is used to control the propeller. \newline
 	\begin{eqnarray}
@@
 The first test that we ran was to measure the response of the kalman filter and ensure that our thrust calculation was accurate in relation to the testbed recorded thrust.
-To do this we measured  As seen in fig \ref{kalman} the kalman filter, while noisy due to the wind variations in the wind sensor data, follows the thrust value from the testbed closely.
+As seen in fig \ref{kalman} the kalman filter, while noisy due to the wind variations in the wind sensor data, follows the thrust value from the testbed closely.
 This result gives us the confidence to setup the PI based on the kalman filter's value.
@@
 	\end{figure}
-	Next we 
-	\subsection{4.3}
 	\subsection{Shortcomings and limitations}
+	As mentioned previously, having a closed loop system allows for a more robust and agile system which allows for better flight performance.
+Some of the application for this level of performance include a better landing algorithm, proximity detection of other MAV's, more sophisticated hovering control, fault detection, and fault tolerance.
+These areas would all benefit by having a physical measurement of the thrust rather than an estimation.
+
+	There are certain limitations within our setup that we have to address.
+The first of which is the low range of the wind sensor which can maximally measure only $25%$ of the motor's maximum RPM.
+The other major shortcoming of our paper is the static nature of the experiments.
+Our tests have only been in a fixed and controlled environment, with only one motor as the test.
+In real situations on a quadrotor or such, the behaviour of our system might be significantly different.
+
 	low wind speed. Have not accounted for multiple sources of wind. fixed and controlled environment. only one propeller. 
@@
 The anemometer measures the rate of wind flow from the downwash of the MAV rotor and there is a linear relationship that is developed between wind flow velocity and the thrust output of the system.
-Through this relationship we developed a PI controller that corrects for any errors in thrust output due to both internal and external disturbances.
+Through this relationship we developed a PI controller that maintains a desired thrust value against internal and external disturbances.
 	\subsection{Reiteration of applications}
 
-	\subsection
+	\subsection{}
 	\subsection{5.4}
+		\begin{figure}[b]
+		\includegraphics[width=\textwidth / 2]{images/block_diagram.png}
+		\caption{Block Diagram}
+		\label{block_diagram}
+	\end{figure}
 	\begin{thebibliography}{99}
-		\bibitem{Mahoney1} Mahoney 2012
+		\bibitem{mahoney1} Mahoney 2012
 		\bibitem{rcb} https://www.rcbenchmark.com/dynamometer-series-1580/
@@
 		\bibitem{hot_wire} Extended Applications of the Hot‐Wire Anemometer, Stanley Corrsin,Review of Scientific Instruments 1947 18:7, 469-471 
+		\bibitem{awan} A.
+U.
+Awan, J.
+Park and H.
+J.
+Kim, "Thrust estimation of quadrotor UAV using adaptive observer," 2011 11th International Conference on Control, Automation and Systems, Gyeonggi-do, 2011, pp.
+131-136.
+		\bibitem{sydney} N.
+Sydney, B.
+Smyth and D.
+A.
+Paley, "Dynamic control of autonomous quadrotor flight in an estimated wind field," 52nd IEEE Conference on Decision and Control, Florence, 2013, pp.
+3609-3616.
+		doi: 10.1109/CDC.2013.6760438
 

### 2018-09-15 paper/drafts/data_for_paper/Final_test_ert_rtw/Final_test.c

@@ -1,0 +1,1310 @@
+/*
+ * Final_test.c
+ *
+ * Academic License - for use in teaching, academic research, and meeting
+ * course requirements at degree granting institutions only.  Not for
+ * government, commercial, or other organizational use.
+ *
+ * Code generation for model "Final_test".
+ *
+ * Model version              : 1.49
+ * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
+ * C source code generated on : Fri Sep 14 14:53:31 2018
+ *
+ * Target selection: ert.tlc
+ * Note: GRT includes extra infrastructure and instrumentation for prototyping
+ * Embedded hardware selection: ARM Compatible->ARM Cortex
+ * Code generation objectives: Unspecified
+ * Validation result: Not run
+ */
+
+#include "Final_test.h"
+#include "Final_test_private.h"
+#include "Final_test_dt.h"
+
+/* Block signals (default storage) */
+B_Final_test_T Final_test_B;
+
+/* Continuous states */
+X_Final_test_T Final_test_X;
+
+/* Block states (default storage) */
+DW_Final_test_T Final_test_DW;
+
+/* Real-time model */
+RT_MODEL_Final_test_T Final_test_M_;
+RT_MODEL_Final_test_T *const Final_test_M = &Final_test_M_;
+
+/* Forward declaration for local functions */
+static codertarget_arduinobase_int_f_T *arduino_PWMOutput_arduino_PWMOu
+  (codertarget_arduinobase_int_f_T *obj);
+static void SystemProp_matlabCodegenSetAn_f(dsp_simulink_MovingAverage_f_T *obj,
+  boolean_T value);
+static void Final_test_SystemCore_release_f(dsp_simulink_MovingAverage_f_T *obj);
+static void Final_test_SystemCore_delete_f(dsp_simulink_MovingAverage_f_T *obj);
+static void matlabCodegenHandle_matlabCod_f(dsp_simulink_MovingAverage_f_T *obj);
[…]

### 2018-09-15 paper/drafts/data_for_paper/Final_test_ert_rtw/Final_test.h

@@ -1,0 +1,632 @@
+/*
+ * Final_test.h
+ *
+ * Academic License - for use in teaching, academic research, and meeting
+ * course requirements at degree granting institutions only.  Not for
+ * government, commercial, or other organizational use.
+ *
+ * Code generation for model "Final_test".
+ *
+ * Model version              : 1.49
+ * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
+ * C source code generated on : Fri Sep 14 14:53:31 2018
+ *
+ * Target selection: ert.tlc
+ * Note: GRT includes extra infrastructure and instrumentation for prototyping
+ * Embedded hardware selection: ARM Compatible->ARM Cortex
+ * Code generation objectives: Unspecified
+ * Validation result: Not run
+ */
+
+#ifndef RTW_HEADER_Final_test_h_
+#define RTW_HEADER_Final_test_h_
+#include <math.h>
+#include <string.h>
+#include <float.h>
+#include <stddef.h>
+#ifndef Final_test_COMMON_INCLUDES_
+# define Final_test_COMMON_INCLUDES_
+#include "rtwtypes.h"
+#include "rtw_extmode.h"
+#include "sysran_types.h"
+#include "rtw_continuous.h"
+#include "rtw_solver.h"
+#include "dt_info.h"
+#include "ext_work.h"
+#include "MW_PWM.h"
+#include "MW_AnalogIn.h"
+#endif                                 /* Final_test_COMMON_INCLUDES_ */
+
+#include "Final_test_types.h"
+
+/* Shared type includes */
+#include "multiword_types.h"
+#include "MW_target_hardware_resources.h"
+#include "rt_nonfinite.h"
+#include "rtGetInf.h"
+
+/* Macros for accessing real-time model data structure */
+#ifndef rtmGetContStateDisabled
+# define rtmGetContStateDisabled(rtm)  ((rtm)->contStateDisabled)
+#endif
+
+#ifndef rtmSetContStateDisabled
+# define rtmSetContStateDisabled(rtm, val) ((rtm)->contStateDisabled = (val))
+#endif
+
+#ifndef rtmGetContStates
+# define rtmGetContStates(rtm)         ((rtm)->contStates)
+#endif
+
+#ifndef rtmSetContStates
+# define rtmSetContStates(rtm, val)    ((rtm)->contStates = (val))
+#endif
+
[…]

### 2018-09-15 paper/drafts/data_for_paper/Final_test_ert_rtw/Final_test_data.c

@@ -1,0 +1,290 @@
+/*
+ * Final_test_data.c
+ *
+ * Academic License - for use in teaching, academic research, and meeting
+ * course requirements at degree granting institutions only.  Not for
+ * government, commercial, or other organizational use.
+ *
+ * Code generation for model "Final_test".
+ *
+ * Model version              : 1.49
+ * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
+ * C source code generated on : Fri Sep 14 14:53:31 2018
+ *
+ * Target selection: ert.tlc
+ * Note: GRT includes extra infrastructure and instrumentation for prototyping
+ * Embedded hardware selection: ARM Compatible->ARM Cortex
+ * Code generation objectives: Unspecified
+ * Validation result: Not run
+ */
+
+#include "Final_test.h"
+#include "Final_test_private.h"
+
+/* Block parameters (default storage) */
+P_Final_test_T Final_test_P = {
+  /* Mask Parameter: DiscretePIDController_I
+   * Referenced by: '<S17>/Integral Gain'
+   */
+  0.01,
+
+  /* Mask Parameter: PIDController3_I
+   * Referenced by: '<S22>/Integral Gain'
+   */
+  5.23638207345188,
+
+  /* Mask Parameter: PIDController3_P
+   * Referenced by: '<S22>/Proportional Gain'
+   */
+  10.1984567978833,
+
+  /* Mask Parameter: DiscretePIDController_P
+   * Referenced by: '<S17>/Proportional Gain'
+   */
+  0.05,
+
+  /* Mask Parameter: CompareToConstant_const
+   * Referenced by: '<S13>/Constant'
+   */
+  3.0,
+
+  /* Mask Parameter: DetectChange_vinit
+   * Referenced by: '<S18>/Delay Input1'
+   */
+  0.0,
+
+  /* Mask Parameter: DetectChange_vinit_c
+   * Referenced by: '<S16>/Delay Input1'
+   */
+  0.0,
+
+  /* Expression: 0.8
+   * Referenced by: '<Root>/Gain'
+   */
+  0.8,
+
+  /* Expression: 0.01
+   * Referenced by: '<S3>/Analog Input'
+   */
[…]

### 2018-09-15 paper/drafts/data_for_paper/Final_test_ert_rtw/Final_test_dt.h

@@ -1,0 +1,118 @@
+/*
+ * Final_test_dt.h
+ *
+ * Academic License - for use in teaching, academic research, and meeting
+ * course requirements at degree granting institutions only.  Not for
+ * government, commercial, or other organizational use.
+ *
+ * Code generation for model "Final_test".
+ *
+ * Model version              : 1.49
+ * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
+ * C source code generated on : Fri Sep 14 14:53:31 2018
+ *
+ * Target selection: ert.tlc
+ * Note: GRT includes extra infrastructure and instrumentation for prototyping
+ * Embedded hardware selection: ARM Compatible->ARM Cortex
+ * Code generation objectives: Unspecified
+ * Validation result: Not run
+ */
+
+#include "ext_types.h"
+
+/* data type size table */
+static uint_T rtDataTypeSizes[] = {
+  sizeof(real_T),
+  sizeof(real32_T),
+  sizeof(int8_T),
+  sizeof(uint8_T),
+  sizeof(int16_T),
+  sizeof(uint16_T),
+  sizeof(int32_T),
+  sizeof(uint32_T),
+  sizeof(boolean_T),
+  sizeof(fcn_call_T),
+  sizeof(int_T),
+  sizeof(pointer_T),
+  sizeof(action_T),
+  2*sizeof(uint32_T),
+  sizeof(dsp_simulink_MovingAverage_f_T),
+  sizeof(dsp_private_SlidingWindowAv_f_T),
+  sizeof(dsp_simulink_MovingAverage_Fi_T),
+  sizeof(dsp_private_SlidingWindowAver_T),
+  sizeof(codertarget_arduinobase_int_f_T),
+  sizeof(codertarget_arduinobase_in_fd_T)
+};
+
+/* data type name table */
+static const char_T * rtDataTypeNames[] = {
+  "real_T",
+  "real32_T",
+  "int8_T",
+  "uint8_T",
+  "int16_T",
+  "uint16_T",
+  "int32_T",
+  "uint32_T",
+  "boolean_T",
+  "fcn_call_T",
+  "int_T",
+  "pointer_T",
+  "action_T",
+  "timer_uint32_pair_T",
+  "dsp_simulink_MovingAverage_f_T",
+  "dsp_private_SlidingWindowAv_f_T",
[…]

### 2018-09-15 paper/drafts/data_for_paper/Final_test_ert_rtw/Final_test_private.h

@@ -1,0 +1,57 @@
+/*
+ * Final_test_private.h
+ *
+ * Academic License - for use in teaching, academic research, and meeting
+ * course requirements at degree granting institutions only.  Not for
+ * government, commercial, or other organizational use.
+ *
+ * Code generation for model "Final_test".
+ *
+ * Model version              : 1.49
+ * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
+ * C source code generated on : Fri Sep 14 14:53:31 2018
+ *
+ * Target selection: ert.tlc
+ * Note: GRT includes extra infrastructure and instrumentation for prototyping
+ * Embedded hardware selection: ARM Compatible->ARM Cortex
+ * Code generation objectives: Unspecified
+ * Validation result: Not run
+ */
+
+#ifndef RTW_HEADER_Final_test_private_h_
+#define RTW_HEADER_Final_test_private_h_
+#include "rtwtypes.h"
+#include "multiword_types.h"
+
+/* Private macros used by the generated code to access rtModel */
+#ifndef rtmIsMajorTimeStep
+# define rtmIsMajorTimeStep(rtm)       (((rtm)->Timing.simTimeStep) == MAJOR_TIME_STEP)
+#endif
+
+#ifndef rtmIsMinorTimeStep
+# define rtmIsMinorTimeStep(rtm)       (((rtm)->Timing.simTimeStep) == MINOR_TIME_STEP)
+#endif
+
+#ifndef rtmSetTFinal
+# define rtmSetTFinal(rtm, val)        ((rtm)->Timing.tFinal = (val))
+#endif
+
+#ifndef rtmSetTPtr
+# define rtmSetTPtr(rtm, val)          ((rtm)->Timing.t = (val))
+#endif
+
+/* Used by FromWorkspace Block: '<S6>/FromWs' */
+#ifndef rtInterpolate
+# define rtInterpolate(v1,v2,f1,f2)    (((v1)==(v2))?((double)(v1)): (((f1)*((double)(v1)))+((f2)*((double)(v2)))))
+#endif
+
+#ifndef rtRound
+# define rtRound(v)                    ( ((v) >= 0) ? floor((v) + 0.5) : ceil((v) - 0.5) )
+#endif
+
+extern real_T rt_powd_snf(real_T u0, real_T u1);
+
+/* private model entry point functions */
+extern void Final_test_derivatives(void);
+
+#endif                                 /* RTW_HEADER_Final_test_private_h_ */

### 2018-09-15 paper/drafts/data_for_paper/Final_test_ert_rtw/Final_test_targ_data_map.m

@@ -1,0 +1,677 @@
+  function targMap = targDataMap(),
+
+  ;%***********************
+  ;% Create Parameter Map *
+  ;%***********************
+      
+    nTotData      = 0; %add to this count as we go
+    nTotSects     = 2;
+    sectIdxOffset = 0;
+    
+    ;%
+    ;% Define dummy sections & preallocate arrays
+    ;%
+    dumSection.nData = -1;  
+    dumSection.data  = [];
+    
+    dumData.logicalSrcIdx = -1;
+    dumData.dtTransOffset = -1;
+    
+    ;%
+    ;% Init/prealloc paramMap
+    ;%
+    paramMap.nSections           = nTotSects;
+    paramMap.sectIdxOffset       = sectIdxOffset;
+      paramMap.sections(nTotSects) = dumSection; %prealloc
+    paramMap.nTotData            = -1;
+    
+    ;%
+    ;% Auto data (Final_test_P)
+    ;%
+      section.nData     = 49;
+      section.data(49)  = dumData; %prealloc
+      
+	  ;% Final_test_P.DiscretePIDController_I
+	  section.data(1).logicalSrcIdx = 0;
+	  section.data(1).dtTransOffset = 0;
+	
+	  ;% Final_test_P.PIDController3_I
+	  section.data(2).logicalSrcIdx = 1;
+	  section.data(2).dtTransOffset = 1;
+	
+	  ;% Final_test_P.PIDController3_P
+	  section.data(3).logicalSrcIdx = 2;
+	  section.data(3).dtTransOffset = 2;
+	
+	  ;% Final_test_P.DiscretePIDController_P
+	  section.data(4).logicalSrcIdx = 3;
+	  section.data(4).dtTransOffset = 3;
+	
+	  ;% Final_test_P.CompareToConstant_const
+	  section.data(5).logicalSrcIdx = 4;
+	  section.data(5).dtTransOffset = 4;
+	
+	  ;% Final_test_P.DetectChange_vinit
+	  section.data(6).logicalSrcIdx = 5;
+	  section.data(6).dtTransOffset = 5;
+	
+	  ;% Final_test_P.DetectChange_vinit_c
+	  section.data(7).logicalSrcIdx = 6;
+	  section.data(7).dtTransOffset = 6;
+	
+	  ;% Final_test_P.Gain_Gain
[…]

### 2018-09-15 paper/drafts/data_for_paper/Final_test_ert_rtw/Final_test_types.h

@@ -1,0 +1,154 @@
+/*
+ * Final_test_types.h
+ *
+ * Academic License - for use in teaching, academic research, and meeting
+ * course requirements at degree granting institutions only.  Not for
+ * government, commercial, or other organizational use.
+ *
+ * Code generation for model "Final_test".
+ *
+ * Model version              : 1.49
+ * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
+ * C source code generated on : Fri Sep 14 14:53:31 2018
+ *
+ * Target selection: ert.tlc
+ * Note: GRT includes extra infrastructure and instrumentation for prototyping
+ * Embedded hardware selection: ARM Compatible->ARM Cortex
+ * Code generation objectives: Unspecified
+ * Validation result: Not run
+ */
+
+#ifndef RTW_HEADER_Final_test_types_h_
+#define RTW_HEADER_Final_test_types_h_
+#include "rtwtypes.h"
+#include "multiword_types.h"
+#ifndef typedef_dsp_private_SlidingWindowAver_T
+#define typedef_dsp_private_SlidingWindowAver_T
+
+typedef struct {
+  int32_T isInitialized;
+  boolean_T isSetupComplete;
+  real_T pCumSum;
+  real_T pCumSumRev[4];
+  real_T pCumRevIndex;
+} dsp_private_SlidingWindowAver_T;
+
+#endif                                 /*typedef_dsp_private_SlidingWindowAver_T*/
+
+#ifndef typedef_dsp_private_SlidingWindowAv_f_T
+#define typedef_dsp_private_SlidingWindowAv_f_T
+
+typedef struct {
+  int32_T isInitialized;
+  boolean_T isSetupComplete;
+  real_T pCumSum;
+  real_T pCumSumRev[9];
+  real_T pCumRevIndex;
+} dsp_private_SlidingWindowAv_f_T;
+
+#endif                                 /*typedef_dsp_private_SlidingWindowAv_f_T*/
+
+/* Custom Type definition for MATLABSystem: '<S3>/Analog Input' */
+#include "MW_SVD.h"
+#ifndef typedef_cell_wrap_Final_test_T
+#define typedef_cell_wrap_Final_test_T
+
+typedef struct {
+  uint32_T f1[8];
+} cell_wrap_Final_test_T;
+
[…]

### 2018-09-15 paper/drafts/data_for_paper/Final_test_ert_rtw/MW_target_hardware_resources.h

@@ -1,0 +1,61 @@
+#ifndef PORTABLE_WORDSIZES
+#ifdef __MW_TARGET_USE_HARDWARE_RESOURCES_H__
+#ifndef __MW_TARGET_HARDWARE_RESOURCES_H__
+#define __MW_TARGET_HARDWARE_RESOURCES_H__
+
+#define MW_MULTI_TASKING_MODE 1
+#include "MW_ArduinoHWInit.h"
+#include "arduinoARMScheduler.h"
+
+#define MW_USECODERTARGET 1
+#define MW_TARGETHARDWARE Arduino Due
+#define MW_CONNECTIONINFO_SERIAL_IPADDRESS codertarget.arduinobase.registry.getLoopbackIP;
+#define MW_CONNECTIONINFO_SERIAL_PORT 17725
+#define MW_CONNECTIONINFO_SERIAL_VERBOSE 0
+#define MW_CONNECTIONINFO_TCPIP_IPADDRESS codertarget.arduinobase.internal.getExternalModeMexArgs('Ethernet')
+#define MW_CONNECTIONINFO_TCPIP_PORT 17725
+#define MW_CONNECTIONINFO_TCPIP_VERBOSE 0
+#define MW_CONNECTIONINFO_WIFI_IPADDRESS codertarget.arduinobase.internal.getExternalModeMexArgs('Wifi')
+#define MW_CONNECTIONINFO_WIFI_PORT 17725
+#define MW_CONNECTIONINFO_WIFI_VERBOSE 0
+#define MW_EXTMODE_CONFIGURATION Serial
+#define MW_EXTMODE_COMPORTBAUD 115200
+#define MW_EXTMODE_RUNNING on
+#define MW_RTOS Baremetal
+#define MW_SCHEDULER_INTERRUPT_SOURCE 0
+#define MW_RUNTIME_BUILDACTION 1
+#define MW_HOSTCOMPORT_SET_HOST_COM_PORT 0
+#define MW_HOSTCOMPORT_COM_PORT_NUMBER /dev/ttyACM0
+#define MW_SIMULINKIO_ENABLE_SIMULINKIO 1
+#define MW_OVERRUNDETECTION_ENABLE_OVERRUN_DETECTION 0
[…]

### 2018-09-15 paper/drafts/data_for_paper/Final_test_ert_rtw/ert_main.c

@@ -1,0 +1,104 @@
+#include "Final_test.h"
+#include "rtwtypes.h"
+#include <ext_work.h>
+#include <ext_svr.h>
+#include <ext_share.h>
+#include <updown.h>
+
+volatile int IsrOverrun = 0;
+static boolean_T OverrunFlag = 0;
+void rt_OneStep(void)
+{
+  /* Check for overrun. Protect OverrunFlag against preemption */
+  if (OverrunFlag++) {
+    IsrOverrun = 1;
+    OverrunFlag--;
+    return;
+  }
+
+#ifndef _MW_ARDUINO_LOOP_
+
+  interrupts();
+
+#endif;
+
+  Final_test_step();
+
+  /* Get model outputs here */
+#ifndef _MW_ARDUINO_LOOP_
+
+  noInterrupts();
+
+#endif;
+
+  OverrunFlag--;
+  rtExtModeCheckEndTrigger();
+}
+
+volatile boolean_T stopRequested = false;
+int main(void)
+{
+  volatile boolean_T runModel = true;
+  float modelBaseRate = 0.01;
+  float systemClock = 0;
+  init();
+  MW_Arduino_Init();
+  rtmSetErrorStatus(Final_test_M, 0);
+
+  /* initialize external mode */
+  rtParseArgsForExtMode(0, NULL);
+  Final_test_initialize();
+  interrupts();
+
+  /* External mode */
+  rtSetTFinalForExtMode(&rtmGetTFinal(Final_test_M));
+  rtExtModeCheckInit(2);
+
+  {
+    boolean_T rtmStopReq = false;
+    rtExtModeWaitForStartPkt(Final_test_M->extModeInfo, 2, &rtmStopReq);
+    if (rtmStopReq) {
+      rtmSetStopRequested(Final_test_M, true);
+    }
+  }
+
+  rtERTExtModeStartMsg();
+  noInterrupts();
+  configureArduinoARMTimer();
+  runModel =
+    (rtmGetErrorStatus(Final_test_M) == (NULL)) && !rtmGetStopRequested
+    (Final_test_M);
+
+#ifndef _MW_ARDUINO_LOOP_
+
+  interrupts();
+
+#endif;
+
+  interrupts();
+  while (runModel) {
+    /* External mode */
+    {
+      boolean_T rtmStopReq = false;
+      rtExtModeOneStep(Final_test_M->extModeInfo, 2, &rtmStopReq);
+      if (rtmStopReq) {
[…]

### 2018-09-15 paper/drafts/data_for_paper/Final_test_ert_rtw/html/define.js

@@ -1,0 +1,193 @@
+function CodeDefine() { 
+this.def = new Array();
+this.def["IsrOverrun"] = {file: "ert_main_c.html",line:8,type:"var"};
+this.def["OverrunFlag"] = {file: "ert_main_c.html",line:9,type:"var"};
+this.def["rt_OneStep"] = {file: "ert_main_c.html",line:10,type:"fcn"};
+this.def["stopRequested"] = {file: "ert_main_c.html",line:38,type:"var"};
+this.def["main"] = {file: "ert_main_c.html",line:39,type:"fcn"};
+this.def["Final_test_B"] = {file: "Final_test_c.html",line:26,type:"var"};
+this.def["Final_test_X"] = {file: "Final_test_c.html",line:29,type:"var"};
+this.def["Final_test_DW"] = {file: "Final_test_c.html",line:32,type:"var"};
+this.def["Final_test_M_"] = {file: "Final_test_c.html",line:35,type:"var"};
+this.def["Final_test_M"] = {file: "Final_test_c.html",line:36,type:"var"};
+this.def["rt_ertODEUpdateContinuousStates"] = {file: "Final_test_c.html",line:62,type:"fcn"};
+this.def["arduino_PWMOutput_arduino_PWMOu"] = {file: "Final_test_c.html",line:139,type:"fcn"};
+this.def["rt_powd_snf"] = {file: "Final_test_c.html",line:167,type:"fcn"};
+this.def["SystemProp_matlabCodegenSetAn_f"] = {file: "Final_test_c.html",line:213,type:"fcn"};
+this.def["Final_test_SystemCore_release_f"] = {file: "Final_test_c.html",line:220,type:"fcn"};
+this.def["Final_test_SystemCore_delete_f"] = {file: "Final_test_c.html",line:237,type:"fcn"};
+this.def["matlabCodegenHandle_matlabCod_f"] = {file: "Final_test_c.html",line:243,type:"fcn"};
+this.def["SystemProp_matlabCodegenSetAnyP"] = {file: "Final_test_c.html",line:254,type:"fcn"};
+this.def["Final_test_SystemCore_release"] = {file: "Final_test_c.html",line:261,type:"fcn"};
+this.def["Final_test_SystemCore_delete"] = {file: "Final_test_c.html",line:278,type:"fcn"};
[…]

### 2018-09-15 paper/drafts/data_for_paper/Final_test_ert_rtw/multiword_types.h

@@ -1,0 +1,165 @@
+/*
+ * multiword_types.h
+ *
+ * Academic License - for use in teaching, academic research, and meeting
+ * course requirements at degree granting institutions only.  Not for
+ * government, commercial, or other organizational use.
+ *
+ * Code generation for model "Final_test".
+ *
+ * Model version              : 1.49
+ * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
+ * C source code generated on : Fri Sep 14 14:53:31 2018
+ *
+ * Target selection: ert.tlc
+ * Note: GRT includes extra infrastructure and instrumentation for prototyping
+ * Embedded hardware selection: ARM Compatible->ARM Cortex
+ * Code generation objectives: Unspecified
+ * Validation result: Not run
+ */
+
+#ifndef MULTIWORD_TYPES_H
+#define MULTIWORD_TYPES_H
+#include "rtwtypes.h"
+
+/*
+ * Definitions supporting external data access
+ */
+typedef int32_T chunk_T;
+typedef uint32_T uchunk_T;
+
+/*
+ * MultiWord supporting definitions
+ */
+typedef long int long_T;
+
+/*
+ * MultiWord types
+ */
+typedef struct {
+  uint32_T chunks[2];
+} int64m_T;
+
+typedef struct {
+  int64m_T re;
+  int64m_T im;
+} cint64m_T;
+
+typedef struct {
+  uint32_T chunks[2];
+} uint64m_T;
+
+typedef struct {
+  uint64m_T re;
+  uint64m_T im;
+} cuint64m_T;
+
+typedef struct {
+  uint32_T chunks[3];
+} int96m_T;
+
+typedef struct {
+  int96m_T re;
+  int96m_T im;
+} cint96m_T;
+
+typedef struct {
+  uint32_T chunks[3];
+} uint96m_T;
+
+typedef struct {
+  uint96m_T re;
+  uint96m_T im;
+} cuint96m_T;
+
+typedef struct {
+  uint32_T chunks[4];
+} int128m_T;
+
+typedef struct {
+  int128m_T re;
+  int128m_T im;
+} cint128m_T;
+
+typedef struct {
+  uint32_T chunks[4];
+} uint128m_T;
+
+typedef struct {
+  uint128m_T re;
+  uint128m_T im;
+} cuint128m_T;
+
+typedef struct {
[…]

### 2018-09-15 paper/drafts/data_for_paper/Final_test_ert_rtw/rtGetInf.c

@@ -1,0 +1,144 @@
+/*
+ * rtGetInf.c
+ *
+ * Academic License - for use in teaching, academic research, and meeting
+ * course requirements at degree granting institutions only.  Not for
+ * government, commercial, or other organizational use.
+ *
+ * Code generation for model "Final_test".
+ *
+ * Model version              : 1.49
+ * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
+ * C source code generated on : Fri Sep 14 14:53:31 2018
+ *
+ * Target selection: ert.tlc
+ * Note: GRT includes extra infrastructure and instrumentation for prototyping
+ * Embedded hardware selection: ARM Compatible->ARM Cortex
+ * Code generation objectives: Unspecified
+ * Validation result: Not run
+ */
+
+/*
+ * Abstract:
+ *      Function to initialize non-finite, Inf
+ */
+#include "rtGetInf.h"
+#define NumBitsPerChar                 8U
+
+/*
+ * Initialize rtInf needed by the generated code.
+ * Inf is initialized as non-signaling. Assumes IEEE.
+ */
+real_T rtGetInf(void)
+{
+  size_t bitsPerReal = sizeof(real_T) * (NumBitsPerChar);
+  real_T inf = 0.0;
+  if (bitsPerReal == 32U) {
+    inf = rtGetInfF();
+  } else {
+    uint16_T one = 1U;
+    enum {
+      LittleEndian,
+      BigEndian
+    } machByteOrder = (*((uint8_T *) &one) == 1U) ? LittleEndian : BigEndian;
+    switch (machByteOrder) {
+     case LittleEndian:
+      {
+        union {
+          LittleEndianIEEEDouble bitVal;
+          real_T fltVal;
+        } tmpVal;
+
+        tmpVal.bitVal.words.wordH = 0x7FF00000U;
+        tmpVal.bitVal.words.wordL = 0x00000000U;
+        inf = tmpVal.fltVal;
+        break;
+      }
+
+     case BigEndian:
+      {
+        union {
+          BigEndianIEEEDouble bitVal;
+          real_T fltVal;
+        } tmpVal;
+
+        tmpVal.bitVal.words.wordH = 0x7FF00000U;
+        tmpVal.bitVal.words.wordL = 0x00000000U;
+        inf = tmpVal.fltVal;
+        break;
[…]

### 2018-09-15 paper/drafts/data_for_paper/Final_test_ert_rtw/rtGetInf.h

@@ -1,0 +1,32 @@
+/*
+ * rtGetInf.h
+ *
+ * Academic License - for use in teaching, academic research, and meeting
+ * course requirements at degree granting institutions only.  Not for
+ * government, commercial, or other organizational use.
+ *
+ * Code generation for model "Final_test".
+ *
+ * Model version              : 1.49
+ * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
+ * C source code generated on : Fri Sep 14 14:53:31 2018
+ *
+ * Target selection: ert.tlc
+ * Note: GRT includes extra infrastructure and instrumentation for prototyping
+ * Embedded hardware selection: ARM Compatible->ARM Cortex
+ * Code generation objectives: Unspecified
+ * Validation result: Not run
+ */
+
+#ifndef RTW_HEADER_rtGetInf_h_
+#define RTW_HEADER_rtGetInf_h_
+#include <stddef.h>
+#include "rtwtypes.h"
+#include "rt_nonfinite.h"
+
+extern real_T rtGetInf(void);
+extern real32_T rtGetInfF(void);
+extern real_T rtGetMinusInf(void);
+extern real32_T rtGetMinusInfF(void);
+
+#endif                                 /* RTW_HEADER_rtGetInf_h_ */

### 2018-09-15 paper/drafts/data_for_paper/Final_test_ert_rtw/rtGetNaN.c

@@ -1,0 +1,104 @@
+/*
+ * rtGetNaN.c
+ *
+ * Academic License - for use in teaching, academic research, and meeting
+ * course requirements at degree granting institutions only.  Not for
+ * government, commercial, or other organizational use.
+ *
+ * Code generation for model "Final_test".
+ *
+ * Model version              : 1.49
+ * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
+ * C source code generated on : Fri Sep 14 14:53:31 2018
+ *
+ * Target selection: ert.tlc
+ * Note: GRT includes extra infrastructure and instrumentation for prototyping
+ * Embedded hardware selection: ARM Compatible->ARM Cortex
+ * Code generation objectives: Unspecified
+ * Validation result: Not run
+ */
+
+/*
+ * Abstract:
+ *      Function to initialize non-finite, NaN
+ */
+#include "rtGetNaN.h"
+#define NumBitsPerChar                 8U
+
+/*
+ * Initialize rtNaN needed by the generated code.
+ * NaN is initialized as non-signaling. Assumes IEEE.
+ */
+real_T rtGetNaN(void)
+{
+  size_t bitsPerReal = sizeof(real_T) * (NumBitsPerChar);
+  real_T nan = 0.0;
+  if (bitsPerReal == 32U) {
+    nan = rtGetNaNF();
+  } else {
+    uint16_T one = 1U;
+    enum {
+      LittleEndian,
+      BigEndian
+    } machByteOrder = (*((uint8_T *) &one) == 1U) ? LittleEndian : BigEndian;
+    switch (machByteOrder) {
+     case LittleEndian:
+      {
+        union {
+          LittleEndianIEEEDouble bitVal;
+          real_T fltVal;
+        } tmpVal;
+
+        tmpVal.bitVal.words.wordH = 0xFFF80000U;
+        tmpVal.bitVal.words.wordL = 0x00000000U;
+        nan = tmpVal.fltVal;
+        break;
+      }
+
+     case BigEndian:
+      {
+        union {
+          BigEndianIEEEDouble bitVal;
+          real_T fltVal;
+        } tmpVal;
+
+        tmpVal.bitVal.words.wordH = 0x7FFFFFFFU;
+        tmpVal.bitVal.words.wordL = 0xFFFFFFFFU;
+        nan = tmpVal.fltVal;
[…]

### 2018-09-15 paper/drafts/data_for_paper/Final_test_ert_rtw/rtGetNaN.h

@@ -1,0 +1,30 @@
+/*
+ * rtGetNaN.h
+ *
+ * Academic License - for use in teaching, academic research, and meeting
+ * course requirements at degree granting institutions only.  Not for
+ * government, commercial, or other organizational use.
+ *
+ * Code generation for model "Final_test".
+ *
+ * Model version              : 1.49
+ * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
+ * C source code generated on : Fri Sep 14 14:53:31 2018
+ *
+ * Target selection: ert.tlc
+ * Note: GRT includes extra infrastructure and instrumentation for prototyping
+ * Embedded hardware selection: ARM Compatible->ARM Cortex
+ * Code generation objectives: Unspecified
+ * Validation result: Not run
+ */
+
+#ifndef RTW_HEADER_rtGetNaN_h_
+#define RTW_HEADER_rtGetNaN_h_
+#include <stddef.h>
+#include "rtwtypes.h"
+#include "rt_nonfinite.h"
+
+extern real_T rtGetNaN(void);
+extern real32_T rtGetNaNF(void);
+
+#endif                                 /* RTW_HEADER_rtGetNaN_h_ */

### 2018-09-15 paper/drafts/data_for_paper/Final_test_ert_rtw/rt_nonfinite.c

@@ -1,0 +1,74 @@
+/*
+ * rt_nonfinite.c
+ *
+ * Academic License - for use in teaching, academic research, and meeting
+ * course requirements at degree granting institutions only.  Not for
+ * government, commercial, or other organizational use.
+ *
+ * Code generation for model "Final_test".
+ *
+ * Model version              : 1.49
+ * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
+ * C source code generated on : Fri Sep 14 14:53:31 2018
+ *
+ * Target selection: ert.tlc
+ * Note: GRT includes extra infrastructure and instrumentation for prototyping
+ * Embedded hardware selection: ARM Compatible->ARM Cortex
+ * Code generation objectives: Unspecified
+ * Validation result: Not run
+ */
+
+/*
+ * Abstract:
+ *      Function to initialize non-finites,
+ *      (Inf, NaN and -Inf).
+ */
+#include "rt_nonfinite.h"
+#include "rtGetNaN.h"
+#include "rtGetInf.h"
+
+real_T rtInf;
+real_T rtMinusInf;
+real_T rtNaN;
+real32_T rtInfF;
+real32_T rtMinusInfF;
+real32_T rtNaNF;
+
+/*
+ * Initialize the rtInf, rtMinusInf, and rtNaN needed by the
+ * generated code. NaN is initialized as non-signaling. Assumes IEEE.
+ */
+void rt_InitInfAndNaN(size_t realSize)
+{
+  (void) (realSize);
+  rtNaN = rtGetNaN();
+  rtNaNF = rtGetNaNF();
+  rtInf = rtGetInf();
+  rtInfF = rtGetInfF();
+  rtMinusInf = rtGetMinusInf();
+  rtMinusInfF = rtGetMinusInfF();
+}
+
+/* Test if value is infinite */
+boolean_T rtIsInf(real_T value)
+{
+  return (boolean_T)((value==rtInf || value==rtMinusInf) ? 1U : 0U);
+}
+
+/* Test if single-precision value is infinite */
+boolean_T rtIsInfF(real32_T value)
+{
+  return (boolean_T)(((value)==rtInfF || (value)==rtMinusInfF) ? 1U : 0U);
+}
+
+/* Test if value is not a number */
+boolean_T rtIsNaN(real_T value)
+{
+  return (boolean_T)((value!=value) ? 1U : 0U);
+}
+
[…]

### 2018-09-15 paper/drafts/data_for_paper/Final_test_ert_rtw/rt_nonfinite.h

@@ -1,0 +1,58 @@
+/*
+ * rt_nonfinite.h
+ *
+ * Academic License - for use in teaching, academic research, and meeting
+ * course requirements at degree granting institutions only.  Not for
+ * government, commercial, or other organizational use.
+ *
+ * Code generation for model "Final_test".
+ *
+ * Model version              : 1.49
+ * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
+ * C source code generated on : Fri Sep 14 14:53:31 2018
+ *
+ * Target selection: ert.tlc
+ * Note: GRT includes extra infrastructure and instrumentation for prototyping
+ * Embedded hardware selection: ARM Compatible->ARM Cortex
+ * Code generation objectives: Unspecified
+ * Validation result: Not run
+ */
+
+#ifndef RTW_HEADER_rt_nonfinite_h_
+#define RTW_HEADER_rt_nonfinite_h_
+#include <stddef.h>
+#include "rtwtypes.h"
+
+extern real_T rtInf;
+extern real_T rtMinusInf;
+extern real_T rtNaN;
+extern real32_T rtInfF;
+extern real32_T rtMinusInfF;
+extern real32_T rtNaNF;
+extern void rt_InitInfAndNaN(size_t realSize);
+extern boolean_T rtIsInf(real_T value);
+extern boolean_T rtIsInfF(real32_T value);
+extern boolean_T rtIsNaN(real_T value);
+extern boolean_T rtIsNaNF(real32_T value);
+typedef struct {
+  struct {
+    uint32_T wordH;
+    uint32_T wordL;
+  } words;
+} BigEndianIEEEDouble;
+
+typedef struct {
+  struct {
+    uint32_T wordL;
+    uint32_T wordH;
+  } words;
+} LittleEndianIEEEDouble;
+
+typedef struct {
+  union {
+    real32_T wordLreal;
+    uint32_T wordLuint;
+  } wordL;
+} IEEESingle;
+
+#endif                                 /* RTW_HEADER_rt_nonfinite_h_ */

### 2018-09-15 paper/drafts/data_for_paper/Final_test_ert_rtw/rtmodel.h

@@ -1,0 +1,43 @@
+/*
+ *  rtmodel.h:
+ *
+ * Academic License - for use in teaching, academic research, and meeting
+ * course requirements at degree granting institutions only.  Not for
+ * government, commercial, or other organizational use.
+ *
+ * Code generation for model "Final_test".
+ *
+ * Model version              : 1.49
+ * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
+ * C source code generated on : Fri Sep 14 14:53:31 2018
+ *
+ * Target selection: ert.tlc
+ * Note: GRT includes extra infrastructure and instrumentation for prototyping
+ * Embedded hardware selection: ARM Compatible->ARM Cortex
+ * Code generation objectives: Unspecified
+ * Validation result: Not run
+ */
+/*
+ * rtmodel.h
+ *
+ * Code generation for Simulink model "Final_test".
+ *
+ * Simulink Coder version                : 8.14 (R2018a) 06-Feb-2018
+ * C source code generated on : Fri Sep 14 14:53:31 2018
+ *
+ * Note that the generated code is not dependent on this header file.
+ * The file is used in cojuction with the automatic build procedure.
+ * It is included by the sample main executable harness
+ * MATLAB/rtw/c/src/common/rt_main.c.
+ *
+ */
+#ifndef RTW_HEADER_rtmodel_h_
+#define RTW_HEADER_rtmodel_h_
+
+/*
+ *  Includes the appropriate headers when we are using rtModel
+ */
+#include "Final_test.h"
+#define GRTINTERFACE                   0
+#include "Final_test.h"
+#endif                                 /* RTW_HEADER_rtmodel_h_ */

### 2018-09-15 paper/drafts/data_for_paper/Final_test_ert_rtw/rtwtypes.h

@@ -1,0 +1,42 @@
+/*
+ * rtwtypes.h
+ *
+ * Academic License - for use in teaching, academic research, and meeting
+ * course requirements at degree granting institutions only.  Not for
+ * government, commercial, or other organizational use.
+ *
+ * Code generation for model "Final_test".
+ *
+ * Model version              : 1.49
+ * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
+ * C source code generated on : Fri Sep 14 14:53:31 2018
+ *
+ * Target selection: ert.tlc
+ * Note: GRT includes extra infrastructure and instrumentation for prototyping
+ * Embedded hardware selection: ARM Compatible->ARM Cortex
+ * Code generation objectives: Unspecified
+ * Validation result: Not run
+ */
+
+#ifndef RTWTYPES_H
+#define RTWTYPES_H
+#include "tmwtypes.h"
+#include "simstruc_types.h"
+#ifndef POINTER_T
+# define POINTER_T
+
+typedef void * pointer_T;
+
+#endif
+
+/* Logical type definitions */
+#if (!defined(__cplusplus))
+#  ifndef false
+#   define false                       (0U)
+#  endif
+
+#  ifndef true
+#   define true                        (1U)
+#  endif
+#endif
+#endif                                 /* RTWTYPES_H */

### 2018-09-15 paper/drafts/draft_final.tex
updated paper

@@
 The majority of the estimation based controls rely on the voltage or current draw by the motors.
-Mahoney et al \cite{Mahoney1} devised such a system which estimates the thrust using a for loop based calculation of the thrust.
+Mahoney et al \cite{mahoney1} devised such a system which estimates the thrust using a for loop based calculation of the thrust.
 This system while it allows for a valid estimation of the thrust, it is a complex system that requires relatively heavy computation and therefore is not feasible.
@@
 	There are certain limitations within our setup that we have to address.
-The first of which is the low range of the wind sensor which can maximally measure only $25%$ of the motor's maximum RPM.
+The first of which is the low range of the wind sensor which can maximally measure only $25\%$ of the motor's maximum RPM.
 The other major shortcoming of our paper is the static nature of the experiments.
@@
 In real situations on a quadrotor or such, the behaviour of our system might be significantly different.
-
 	low wind speed. Have not accounted for multiple sources of wind. fixed and controlled environment. only one propeller. 

### 2018-09-15 bara/sherman/ws/test2/AFKF.m
something

@@ -1,0 +1,87 @@
+%% This is for IMU/Optical Flow/Sonar sensor fusion algorithm 
+clc
+clear 
+close all
+
+
+%% Load Kalman matrices 
+load('input1.mat')
+load('Kalman1.mat')
+load('measured1.mat')
+load('true1.mat')
+load('xhafkf.mat')
+FAKF = readfis('FAKF');
+
+
+%% Kalman Declaration
+xh= zeros(2,1);
+P= eye(2);
+Crk=0;
+N=50; % estimation window
+        
+Ad = [0.9998  0.009851; -0.0394    0.9702];
+Bd = [0.000198; 0.0394];
+Cd = [1 0];
+
+Q = 1;
+R = diag([0.2,5]);
+H1 = [1 0];
+Ts = 0.0001;
+
+%% Kalman Procedure
+
+ for counter = 2:50000
+% Model information
+xh_bar(:,counter) = xh(:,counter-1)+(Ad * xh(:,counter-1) + Bd * input1(counter,1))*Ts;
+P_bar = Ad * P * Ad' + R;
+
+% Measurement update
+
+K = P_bar * Cd' * (Cd * P_bar * Cd' + Q)^-1;
+S1= Cd * P_bar * Cd' + Q;
+xh = xh_bar +  K * (measured1(counter,1) - Cd * xh_bar(:,counter));
+P = (1 - K * Cd) * P_bar;
+
+% R matrix adaptation
+r= Cd * xh_bar(:,counter);
+% 
+
+% Fuzzy code begins 
+
+for s= counter-N+1:counter 
+Crk=Crk+((r)*(r)'/N);
+%Crk=((r)*(r)'/N);
+end
+ 
+DoM(1,1)=S1(1,1)- Crk(1,1);% deg of Matching 
+Domk= 2*DoM(1,1); % Input for the FIS
+Domk= min(max(Domk,-10),10);
+R_delta(1,1)=evalfis(Domk,FAKF);
+R(1,1)=R(1,1)+0.001*R_delta(1,1);% 0.0018 for the disturbance rejection
+
+end
+ 
+% %% RMSE calculations for each state
+% K=1:11;
+% RMSE = sqrt(mean((states.signals.values(2000:3000,K) - X_KF(K,2000:3000)').^2))';% sqrt(mean(real - estimated).^2))'
+
+%% State estimation plots 
+
+i =1:50000;
+
+figure (1)
[…]

### 2018-09-16 paper/Matlab_code/Final_test_ert_rtw/Final_test.c
Included images for wind sensor

@@ -1,0 +1,1379 @@
+/*
+ * Final_test.c
+ *
+ * Academic License - for use in teaching, academic research, and meeting
+ * course requirements at degree granting institutions only.  Not for
+ * government, commercial, or other organizational use.
+ *
+ * Code generation for model "Final_test".
+ *
+ * Model version              : 1.53
+ * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
+ * C source code generated on : Sat Sep 15 16:14:57 2018
+ *
+ * Target selection: ert.tlc
+ * Note: GRT includes extra infrastructure and instrumentation for prototyping
+ * Embedded hardware selection: ARM Compatible->ARM Cortex
+ * Code generation objectives: Unspecified
+ * Validation result: Not run
+ */
+
+#include "Final_test.h"
+#include "Final_test_private.h"
+#include "Final_test_dt.h"
+
+/* Block signals (default storage) */
+B_Final_test_T Final_test_B;
+
+/* Continuous states */
+X_Final_test_T Final_test_X;
+
+/* Block states (default storage) */
+DW_Final_test_T Final_test_DW;
+
+/* Real-time model */
+RT_MODEL_Final_test_T Final_test_M_;
+RT_MODEL_Final_test_T *const Final_test_M = &Final_test_M_;
+
+/* Forward declaration for local functions */
+static codertarget_arduinobase_int_f_T *arduino_PWMOutput_arduino_PWMOu
+  (codertarget_arduinobase_int_f_T *obj);
+static void SystemProp_matlabCodegenSetAn_f(dsp_simulink_MovingAverage_f_T *obj,
+  boolean_T value);
+static void Final_test_SystemCore_release_f(dsp_simulink_MovingAverage_f_T *obj);
+static void Final_test_SystemCore_delete_f(dsp_simulink_MovingAverage_f_T *obj);
+static void matlabCodegenHandle_matlabCod_f(dsp_simulink_MovingAverage_f_T *obj);
[…]

### 2018-09-16 paper/Matlab_code/Final_test_ert_rtw/Final_test.h

@@ -1,0 +1,664 @@
+/*
+ * Final_test.h
+ *
+ * Academic License - for use in teaching, academic research, and meeting
+ * course requirements at degree granting institutions only.  Not for
+ * government, commercial, or other organizational use.
+ *
+ * Code generation for model "Final_test".
+ *
+ * Model version              : 1.53
+ * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
+ * C source code generated on : Sat Sep 15 16:14:57 2018
+ *
+ * Target selection: ert.tlc
+ * Note: GRT includes extra infrastructure and instrumentation for prototyping
+ * Embedded hardware selection: ARM Compatible->ARM Cortex
+ * Code generation objectives: Unspecified
+ * Validation result: Not run
+ */
+
+#ifndef RTW_HEADER_Final_test_h_
+#define RTW_HEADER_Final_test_h_
+#include <math.h>
+#include <string.h>
+#include <float.h>
+#include <stddef.h>
+#ifndef Final_test_COMMON_INCLUDES_
+# define Final_test_COMMON_INCLUDES_
+#include "rtwtypes.h"
+#include "rtw_extmode.h"
+#include "sysran_types.h"
+#include "rtw_continuous.h"
+#include "rtw_solver.h"
+#include "dt_info.h"
+#include "ext_work.h"
+#include "MW_PWM.h"
+#include "MW_AnalogIn.h"
+#endif                                 /* Final_test_COMMON_INCLUDES_ */
+
+#include "Final_test_types.h"
+
+/* Shared type includes */
+#include "multiword_types.h"
+#include "MW_target_hardware_resources.h"
+#include "rt_nonfinite.h"
+#include "rtGetInf.h"
+
+/* Macros for accessing real-time model data structure */
+#ifndef rtmGetContStateDisabled
+# define rtmGetContStateDisabled(rtm)  ((rtm)->contStateDisabled)
+#endif
+
+#ifndef rtmSetContStateDisabled
+# define rtmSetContStateDisabled(rtm, val) ((rtm)->contStateDisabled = (val))
+#endif
+
+#ifndef rtmGetContStates
+# define rtmGetContStates(rtm)         ((rtm)->contStates)
+#endif
+
+#ifndef rtmSetContStates
[…]

### 2018-09-16 paper/Matlab_code/Final_test_ert_rtw/Final_test_data.c

@@ -1,0 +1,300 @@
+/*
+ * Final_test_data.c
+ *
+ * Academic License - for use in teaching, academic research, and meeting
+ * course requirements at degree granting institutions only.  Not for
+ * government, commercial, or other organizational use.
+ *
+ * Code generation for model "Final_test".
+ *
+ * Model version              : 1.53
+ * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
+ * C source code generated on : Sat Sep 15 16:14:57 2018
+ *
+ * Target selection: ert.tlc
+ * Note: GRT includes extra infrastructure and instrumentation for prototyping
+ * Embedded hardware selection: ARM Compatible->ARM Cortex
+ * Code generation objectives: Unspecified
+ * Validation result: Not run
+ */
+
+#include "Final_test.h"
+#include "Final_test_private.h"
+
+/* Block parameters (default storage) */
+P_Final_test_T Final_test_P = {
+  /* Mask Parameter: PIDController3_I
+   * Referenced by: '<S27>/Integral Gain'
+   */
+  5.23638207345188,
+
+  /* Mask Parameter: DiscretePIDController_I
+   * Referenced by: '<S22>/Integral Gain'
+   */
+  0.01,
+
+  /* Mask Parameter: DiscretePIDController_P
+   * Referenced by: '<S22>/Proportional Gain'
+   */
+  0.05,
+
+  /* Mask Parameter: PIDController3_P
+   * Referenced by: '<S27>/Proportional Gain'
+   */
+  10.1984567978833,
+
+  /* Mask Parameter: CompareToConstant_const
+   * Referenced by: '<S18>/Constant'
+   */
+  3.0,
+
+  /* Mask Parameter: DetectChange_vinit
+   * Referenced by: '<S21>/Delay Input1'
+   */
+  0.0,
+
+  /* Mask Parameter: DetectChange_vinit_i
+   * Referenced by: '<S23>/Delay Input1'
+   */
+  0.0,
+
+  /* Expression: 0.8
+   * Referenced by: '<Root>/Gain'
+   */
+  0.8,
+
+  /* Expression: 0.8
+   * Referenced by: '<Root>/Gain1'
+   */
+  0.8,
+
[…]

### 2018-09-16 paper/Matlab_code/Final_test_ert_rtw/Final_test_dt.h

@@ -1,0 +1,120 @@
+/*
+ * Final_test_dt.h
+ *
+ * Academic License - for use in teaching, academic research, and meeting
+ * course requirements at degree granting institutions only.  Not for
+ * government, commercial, or other organizational use.
+ *
+ * Code generation for model "Final_test".
+ *
+ * Model version              : 1.53
+ * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
+ * C source code generated on : Sat Sep 15 16:14:57 2018
+ *
+ * Target selection: ert.tlc
+ * Note: GRT includes extra infrastructure and instrumentation for prototyping
+ * Embedded hardware selection: ARM Compatible->ARM Cortex
+ * Code generation objectives: Unspecified
+ * Validation result: Not run
+ */
+
+#include "ext_types.h"
+
+/* data type size table */
+static uint_T rtDataTypeSizes[] = {
+  sizeof(real_T),
+  sizeof(real32_T),
+  sizeof(int8_T),
+  sizeof(uint8_T),
+  sizeof(int16_T),
+  sizeof(uint16_T),
+  sizeof(int32_T),
+  sizeof(uint32_T),
+  sizeof(boolean_T),
+  sizeof(fcn_call_T),
+  sizeof(int_T),
+  sizeof(pointer_T),
+  sizeof(action_T),
+  2*sizeof(uint32_T),
+  sizeof(dsp_simulink_MovingAverage_f_T),
+  sizeof(dsp_private_SlidingWindowAv_f_T),
+  sizeof(dsp_simulink_MovingAverage_Fi_T),
+  sizeof(dsp_private_SlidingWindowAver_T),
+  sizeof(codertarget_arduinobase_int_f_T),
+  sizeof(codertarget_arduinobase_in_fd_T)
+};
+
+/* data type name table */
+static const char_T * rtDataTypeNames[] = {
+  "real_T",
+  "real32_T",
+  "int8_T",
+  "uint8_T",
+  "int16_T",
+  "uint16_T",
+  "int32_T",
+  "uint32_T",
+  "boolean_T",
+  "fcn_call_T",
+  "int_T",
+  "pointer_T",
+  "action_T",
+  "timer_uint32_pair_T",
+  "dsp_simulink_MovingAverage_f_T",
+  "dsp_private_SlidingWindowAv_f_T",
[…]

### 2018-09-16 paper/Matlab_code/Final_test_ert_rtw/Final_test_private.h

@@ -1,0 +1,57 @@
+/*
+ * Final_test_private.h
+ *
+ * Academic License - for use in teaching, academic research, and meeting
+ * course requirements at degree granting institutions only.  Not for
+ * government, commercial, or other organizational use.
+ *
+ * Code generation for model "Final_test".
+ *
+ * Model version              : 1.53
+ * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
+ * C source code generated on : Sat Sep 15 16:14:57 2018
+ *
+ * Target selection: ert.tlc
+ * Note: GRT includes extra infrastructure and instrumentation for prototyping
+ * Embedded hardware selection: ARM Compatible->ARM Cortex
+ * Code generation objectives: Unspecified
+ * Validation result: Not run
+ */
+
+#ifndef RTW_HEADER_Final_test_private_h_
+#define RTW_HEADER_Final_test_private_h_
+#include "rtwtypes.h"
+#include "multiword_types.h"
+
+/* Private macros used by the generated code to access rtModel */
+#ifndef rtmIsMajorTimeStep
+# define rtmIsMajorTimeStep(rtm)       (((rtm)->Timing.simTimeStep) == MAJOR_TIME_STEP)
+#endif
+
+#ifndef rtmIsMinorTimeStep
+# define rtmIsMinorTimeStep(rtm)       (((rtm)->Timing.simTimeStep) == MINOR_TIME_STEP)
+#endif
+
+#ifndef rtmSetTFinal
+# define rtmSetTFinal(rtm, val)        ((rtm)->Timing.tFinal = (val))
+#endif
+
+#ifndef rtmSetTPtr
+# define rtmSetTPtr(rtm, val)          ((rtm)->Timing.t = (val))
+#endif
+
+/* Used by FromWorkspace Block: '<S10>/FromWs' */
+#ifndef rtInterpolate
+# define rtInterpolate(v1,v2,f1,f2)    (((v1)==(v2))?((double)(v1)): (((f1)*((double)(v1)))+((f2)*((double)(v2)))))
+#endif
+
+#ifndef rtRound
+# define rtRound(v)                    ( ((v) >= 0) ? floor((v) + 0.5) : ceil((v) - 0.5) )
+#endif
+
+extern real_T rt_powd_snf(real_T u0, real_T u1);
+
+/* private model entry point functions */
+extern void Final_test_derivatives(void);
+
+#endif                                 /* RTW_HEADER_Final_test_private_h_ */

### 2018-09-16 paper/Matlab_code/Final_test_ert_rtw/Final_test_targ_data_map.m

@@ -1,0 +1,708 @@
+  function targMap = targDataMap(),
+
+  ;%***********************
+  ;% Create Parameter Map *
+  ;%***********************
+      
+    nTotData      = 0; %add to this count as we go
+    nTotSects     = 2;
+    sectIdxOffset = 0;
+    
+    ;%
+    ;% Define dummy sections & preallocate arrays
+    ;%
+    dumSection.nData = -1;  
+    dumSection.data  = [];
+    
+    dumData.logicalSrcIdx = -1;
+    dumData.dtTransOffset = -1;
+    
+    ;%
+    ;% Init/prealloc paramMap
+    ;%
+    paramMap.nSections           = nTotSects;
+    paramMap.sectIdxOffset       = sectIdxOffset;
+      paramMap.sections(nTotSects) = dumSection; %prealloc
+    paramMap.nTotData            = -1;
+    
+    ;%
+    ;% Auto data (Final_test_P)
+    ;%
+      section.nData     = 49;
+      section.data(49)  = dumData; %prealloc
+      
+	  ;% Final_test_P.PIDController3_I
+	  section.data(1).logicalSrcIdx = 0;
+	  section.data(1).dtTransOffset = 0;
+	
+	  ;% Final_test_P.DiscretePIDController_I
+	  section.data(2).logicalSrcIdx = 1;
+	  section.data(2).dtTransOffset = 1;
+	
+	  ;% Final_test_P.DiscretePIDController_P
+	  section.data(3).logicalSrcIdx = 2;
+	  section.data(3).dtTransOffset = 2;
+	
+	  ;% Final_test_P.PIDController3_P
+	  section.data(4).logicalSrcIdx = 3;
+	  section.data(4).dtTransOffset = 3;
+	
+	  ;% Final_test_P.CompareToConstant_const
+	  section.data(5).logicalSrcIdx = 4;
+	  section.data(5).dtTransOffset = 4;
+	
+	  ;% Final_test_P.DetectChange_vinit
+	  section.data(6).logicalSrcIdx = 5;
+	  section.data(6).dtTransOffset = 5;
+	
+	  ;% Final_test_P.DetectChange_vinit_i
+	  section.data(7).logicalSrcIdx = 6;
+	  section.data(7).dtTransOffset = 6;
+	
+	  ;% Final_test_P.Gain_Gain
[…]

### 2018-09-16 paper/Matlab_code/Final_test_ert_rtw/Final_test_types.h

@@ -1,0 +1,154 @@
+/*
+ * Final_test_types.h
+ *
+ * Academic License - for use in teaching, academic research, and meeting
+ * course requirements at degree granting institutions only.  Not for
+ * government, commercial, or other organizational use.
+ *
+ * Code generation for model "Final_test".
+ *
+ * Model version              : 1.53
+ * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
+ * C source code generated on : Sat Sep 15 16:14:57 2018
+ *
+ * Target selection: ert.tlc
+ * Note: GRT includes extra infrastructure and instrumentation for prototyping
+ * Embedded hardware selection: ARM Compatible->ARM Cortex
+ * Code generation objectives: Unspecified
+ * Validation result: Not run
+ */
+
+#ifndef RTW_HEADER_Final_test_types_h_
+#define RTW_HEADER_Final_test_types_h_
+#include "rtwtypes.h"
+#include "multiword_types.h"
+#ifndef typedef_dsp_private_SlidingWindowAver_T
+#define typedef_dsp_private_SlidingWindowAver_T
+
+typedef struct {
+  int32_T isInitialized;
+  boolean_T isSetupComplete;
+  real_T pCumSum;
+  real_T pCumSumRev[4];
+  real_T pCumRevIndex;
+} dsp_private_SlidingWindowAver_T;
+
+#endif                                 /*typedef_dsp_private_SlidingWindowAver_T*/
+
+#ifndef typedef_dsp_private_SlidingWindowAv_f_T
+#define typedef_dsp_private_SlidingWindowAv_f_T
+
+typedef struct {
+  int32_T isInitialized;
+  boolean_T isSetupComplete;
+  real_T pCumSum;
+  real_T pCumSumRev[9];
+  real_T pCumRevIndex;
+} dsp_private_SlidingWindowAv_f_T;
+
+#endif                                 /*typedef_dsp_private_SlidingWindowAv_f_T*/
+
+/* Custom Type definition for MATLABSystem: '<S4>/Analog Input' */
+#include "MW_SVD.h"
+#ifndef typedef_cell_wrap_Final_test_T
+#define typedef_cell_wrap_Final_test_T
+
+typedef struct {
+  uint32_T f1[8];
+} cell_wrap_Final_test_T;
+
[…]

### 2018-09-16 paper/Matlab_code/Final_test_ert_rtw/html/define.js

@@ -1,0 +1,193 @@
+function CodeDefine() { 
+this.def = new Array();
+this.def["IsrOverrun"] = {file: "ert_main_c.html",line:8,type:"var"};
+this.def["OverrunFlag"] = {file: "ert_main_c.html",line:9,type:"var"};
+this.def["rt_OneStep"] = {file: "ert_main_c.html",line:10,type:"fcn"};
+this.def["stopRequested"] = {file: "ert_main_c.html",line:38,type:"var"};
+this.def["main"] = {file: "ert_main_c.html",line:39,type:"fcn"};
+this.def["Final_test_B"] = {file: "Final_test_c.html",line:26,type:"var"};
+this.def["Final_test_X"] = {file: "Final_test_c.html",line:29,type:"var"};
+this.def["Final_test_DW"] = {file: "Final_test_c.html",line:32,type:"var"};
+this.def["Final_test_M_"] = {file: "Final_test_c.html",line:35,type:"var"};
+this.def["Final_test_M"] = {file: "Final_test_c.html",line:36,type:"var"};
+this.def["rt_ertODEUpdateContinuousStates"] = {file: "Final_test_c.html",line:62,type:"fcn"};
+this.def["arduino_PWMOutput_arduino_PWMOu"] = {file: "Final_test_c.html",line:139,type:"fcn"};
+this.def["rt_powd_snf"] = {file: "Final_test_c.html",line:167,type:"fcn"};
+this.def["SystemProp_matlabCodegenSetAn_f"] = {file: "Final_test_c.html",line:213,type:"fcn"};
+this.def["Final_test_SystemCore_release_f"] = {file: "Final_test_c.html",line:220,type:"fcn"};
+this.def["Final_test_SystemCore_delete_f"] = {file: "Final_test_c.html",line:237,type:"fcn"};
+this.def["matlabCodegenHandle_matlabCod_f"] = {file: "Final_test_c.html",line:243,type:"fcn"};
+this.def["SystemProp_matlabCodegenSetAnyP"] = {file: "Final_test_c.html",line:254,type:"fcn"};
+this.def["Final_test_SystemCore_release"] = {file: "Final_test_c.html",line:261,type:"fcn"};
+this.def["Final_test_SystemCore_delete"] = {file: "Final_test_c.html",line:278,type:"fcn"};
[…]

### 2018-09-16 paper/Matlab_code/Final_test_ert_rtw/multiword_types.h

@@ -1,0 +1,165 @@
+/*
+ * multiword_types.h
+ *
+ * Academic License - for use in teaching, academic research, and meeting
+ * course requirements at degree granting institutions only.  Not for
+ * government, commercial, or other organizational use.
+ *
+ * Code generation for model "Final_test".
+ *
+ * Model version              : 1.53
+ * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
+ * C source code generated on : Sat Sep 15 16:14:57 2018
+ *
+ * Target selection: ert.tlc
+ * Note: GRT includes extra infrastructure and instrumentation for prototyping
+ * Embedded hardware selection: ARM Compatible->ARM Cortex
+ * Code generation objectives: Unspecified
+ * Validation result: Not run
+ */
+
+#ifndef MULTIWORD_TYPES_H
+#define MULTIWORD_TYPES_H
+#include "rtwtypes.h"
+
+/*
+ * Definitions supporting external data access
+ */
+typedef int32_T chunk_T;
+typedef uint32_T uchunk_T;
+
+/*
+ * MultiWord supporting definitions
+ */
+typedef long int long_T;
+
+/*
+ * MultiWord types
+ */
+typedef struct {
+  uint32_T chunks[2];
+} int64m_T;
+
+typedef struct {
+  int64m_T re;
+  int64m_T im;
+} cint64m_T;
+
+typedef struct {
+  uint32_T chunks[2];
+} uint64m_T;
+
+typedef struct {
+  uint64m_T re;
+  uint64m_T im;
+} cuint64m_T;
+
+typedef struct {
+  uint32_T chunks[3];
+} int96m_T;
+
+typedef struct {
+  int96m_T re;
+  int96m_T im;
+} cint96m_T;
+
+typedef struct {
+  uint32_T chunks[3];
+} uint96m_T;
+
+typedef struct {
+  uint96m_T re;
+  uint96m_T im;
+} cuint96m_T;
+
+typedef struct {
+  uint32_T chunks[4];
+} int128m_T;
+
+typedef struct {
+  int128m_T re;
+  int128m_T im;
+} cint128m_T;
+
+typedef struct {
+  uint32_T chunks[4];
+} uint128m_T;
+
+typedef struct {
+  uint128m_T re;
+  uint128m_T im;
+} cuint128m_T;
+
+typedef struct {
[…]

### 2018-09-16 paper/Matlab_code/Final_test_ert_rtw/rtGetInf.c

@@ -1,0 +1,144 @@
+/*
+ * rtGetInf.c
+ *
+ * Academic License - for use in teaching, academic research, and meeting
+ * course requirements at degree granting institutions only.  Not for
+ * government, commercial, or other organizational use.
+ *
+ * Code generation for model "Final_test".
+ *
+ * Model version              : 1.53
+ * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
+ * C source code generated on : Sat Sep 15 16:14:57 2018
+ *
+ * Target selection: ert.tlc
+ * Note: GRT includes extra infrastructure and instrumentation for prototyping
+ * Embedded hardware selection: ARM Compatible->ARM Cortex
+ * Code generation objectives: Unspecified
+ * Validation result: Not run
+ */
+
+/*
+ * Abstract:
+ *      Function to initialize non-finite, Inf
+ */
+#include "rtGetInf.h"
+#define NumBitsPerChar                 8U
+
+/*
+ * Initialize rtInf needed by the generated code.
+ * Inf is initialized as non-signaling. Assumes IEEE.
+ */
+real_T rtGetInf(void)
+{
+  size_t bitsPerReal = sizeof(real_T) * (NumBitsPerChar);
+  real_T inf = 0.0;
+  if (bitsPerReal == 32U) {
+    inf = rtGetInfF();
+  } else {
+    uint16_T one = 1U;
+    enum {
+      LittleEndian,
+      BigEndian
+    } machByteOrder = (*((uint8_T *) &one) == 1U) ? LittleEndian : BigEndian;
+    switch (machByteOrder) {
+     case LittleEndian:
+      {
+        union {
+          LittleEndianIEEEDouble bitVal;
+          real_T fltVal;
+        } tmpVal;
+
+        tmpVal.bitVal.words.wordH = 0x7FF00000U;
+        tmpVal.bitVal.words.wordL = 0x00000000U;
+        inf = tmpVal.fltVal;
+        break;
+      }
+
+     case BigEndian:
+      {
+        union {
+          BigEndianIEEEDouble bitVal;
+          real_T fltVal;
+        } tmpVal;
+
+        tmpVal.bitVal.words.wordH = 0x7FF00000U;
+        tmpVal.bitVal.words.wordL = 0x00000000U;
+        inf = tmpVal.fltVal;
+        break;
[…]

### 2018-09-16 paper/Matlab_code/Final_test_ert_rtw/rtGetInf.h

@@ -1,0 +1,32 @@
+/*
+ * rtGetInf.h
+ *
+ * Academic License - for use in teaching, academic research, and meeting
+ * course requirements at degree granting institutions only.  Not for
+ * government, commercial, or other organizational use.
+ *
+ * Code generation for model "Final_test".
+ *
+ * Model version              : 1.53
+ * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
+ * C source code generated on : Sat Sep 15 16:14:57 2018
+ *
+ * Target selection: ert.tlc
+ * Note: GRT includes extra infrastructure and instrumentation for prototyping
+ * Embedded hardware selection: ARM Compatible->ARM Cortex
+ * Code generation objectives: Unspecified
+ * Validation result: Not run
+ */
+
+#ifndef RTW_HEADER_rtGetInf_h_
+#define RTW_HEADER_rtGetInf_h_
+#include <stddef.h>
+#include "rtwtypes.h"
+#include "rt_nonfinite.h"
+
+extern real_T rtGetInf(void);
+extern real32_T rtGetInfF(void);
+extern real_T rtGetMinusInf(void);
+extern real32_T rtGetMinusInfF(void);
+
+#endif                                 /* RTW_HEADER_rtGetInf_h_ */

### 2018-09-16 paper/Matlab_code/Final_test_ert_rtw/rtGetNaN.c

@@ -1,0 +1,104 @@
+/*
+ * rtGetNaN.c
+ *
+ * Academic License - for use in teaching, academic research, and meeting
+ * course requirements at degree granting institutions only.  Not for
+ * government, commercial, or other organizational use.
+ *
+ * Code generation for model "Final_test".
+ *
+ * Model version              : 1.53
+ * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
+ * C source code generated on : Sat Sep 15 16:14:57 2018
+ *
+ * Target selection: ert.tlc
+ * Note: GRT includes extra infrastructure and instrumentation for prototyping
+ * Embedded hardware selection: ARM Compatible->ARM Cortex
+ * Code generation objectives: Unspecified
+ * Validation result: Not run
+ */
+
+/*
+ * Abstract:
+ *      Function to initialize non-finite, NaN
+ */
+#include "rtGetNaN.h"
+#define NumBitsPerChar                 8U
+
+/*
+ * Initialize rtNaN needed by the generated code.
+ * NaN is initialized as non-signaling. Assumes IEEE.
+ */
+real_T rtGetNaN(void)
+{
+  size_t bitsPerReal = sizeof(real_T) * (NumBitsPerChar);
+  real_T nan = 0.0;
+  if (bitsPerReal == 32U) {
+    nan = rtGetNaNF();
+  } else {
+    uint16_T one = 1U;
+    enum {
+      LittleEndian,
+      BigEndian
+    } machByteOrder = (*((uint8_T *) &one) == 1U) ? LittleEndian : BigEndian;
+    switch (machByteOrder) {
+     case LittleEndian:
+      {
+        union {
+          LittleEndianIEEEDouble bitVal;
+          real_T fltVal;
+        } tmpVal;
+
+        tmpVal.bitVal.words.wordH = 0xFFF80000U;
+        tmpVal.bitVal.words.wordL = 0x00000000U;
+        nan = tmpVal.fltVal;
+        break;
+      }
+
+     case BigEndian:
+      {
+        union {
+          BigEndianIEEEDouble bitVal;
+          real_T fltVal;
+        } tmpVal;
+
+        tmpVal.bitVal.words.wordH = 0x7FFFFFFFU;
+        tmpVal.bitVal.words.wordL = 0xFFFFFFFFU;
+        nan = tmpVal.fltVal;
[…]

### 2018-09-16 paper/Matlab_code/Final_test_ert_rtw/rtGetNaN.h

@@ -1,0 +1,30 @@
+/*
+ * rtGetNaN.h
+ *
+ * Academic License - for use in teaching, academic research, and meeting
+ * course requirements at degree granting institutions only.  Not for
+ * government, commercial, or other organizational use.
+ *
+ * Code generation for model "Final_test".
+ *
+ * Model version              : 1.53
+ * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
+ * C source code generated on : Sat Sep 15 16:14:57 2018
+ *
+ * Target selection: ert.tlc
+ * Note: GRT includes extra infrastructure and instrumentation for prototyping
+ * Embedded hardware selection: ARM Compatible->ARM Cortex
+ * Code generation objectives: Unspecified
+ * Validation result: Not run
+ */
+
+#ifndef RTW_HEADER_rtGetNaN_h_
+#define RTW_HEADER_rtGetNaN_h_
+#include <stddef.h>
+#include "rtwtypes.h"
+#include "rt_nonfinite.h"
+
+extern real_T rtGetNaN(void);
+extern real32_T rtGetNaNF(void);
+
+#endif                                 /* RTW_HEADER_rtGetNaN_h_ */

### 2018-09-16 paper/Matlab_code/Final_test_ert_rtw/rt_nonfinite.c

@@ -1,0 +1,74 @@
+/*
+ * rt_nonfinite.c
+ *
+ * Academic License - for use in teaching, academic research, and meeting
+ * course requirements at degree granting institutions only.  Not for
+ * government, commercial, or other organizational use.
+ *
+ * Code generation for model "Final_test".
+ *
+ * Model version              : 1.53
+ * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
+ * C source code generated on : Sat Sep 15 16:14:57 2018
+ *
+ * Target selection: ert.tlc
+ * Note: GRT includes extra infrastructure and instrumentation for prototyping
+ * Embedded hardware selection: ARM Compatible->ARM Cortex
+ * Code generation objectives: Unspecified
+ * Validation result: Not run
+ */
+
+/*
+ * Abstract:
+ *      Function to initialize non-finites,
+ *      (Inf, NaN and -Inf).
+ */
+#include "rt_nonfinite.h"
+#include "rtGetNaN.h"
+#include "rtGetInf.h"
+
+real_T rtInf;
+real_T rtMinusInf;
+real_T rtNaN;
+real32_T rtInfF;
+real32_T rtMinusInfF;
+real32_T rtNaNF;
+
+/*
+ * Initialize the rtInf, rtMinusInf, and rtNaN needed by the
+ * generated code. NaN is initialized as non-signaling. Assumes IEEE.
+ */
+void rt_InitInfAndNaN(size_t realSize)
+{
+  (void) (realSize);
+  rtNaN = rtGetNaN();
+  rtNaNF = rtGetNaNF();
+  rtInf = rtGetInf();
+  rtInfF = rtGetInfF();
+  rtMinusInf = rtGetMinusInf();
+  rtMinusInfF = rtGetMinusInfF();
+}
+
+/* Test if value is infinite */
+boolean_T rtIsInf(real_T value)
+{
+  return (boolean_T)((value==rtInf || value==rtMinusInf) ? 1U : 0U);
+}
+
+/* Test if single-precision value is infinite */
+boolean_T rtIsInfF(real32_T value)
+{
+  return (boolean_T)(((value)==rtInfF || (value)==rtMinusInfF) ? 1U : 0U);
+}
+
+/* Test if value is not a number */
+boolean_T rtIsNaN(real_T value)
+{
+  return (boolean_T)((value!=value) ? 1U : 0U);
+}
+
[…]

### 2018-09-16 paper/Matlab_code/Final_test_ert_rtw/rt_nonfinite.h

@@ -1,0 +1,58 @@
+/*
+ * rt_nonfinite.h
+ *
+ * Academic License - for use in teaching, academic research, and meeting
+ * course requirements at degree granting institutions only.  Not for
+ * government, commercial, or other organizational use.
+ *
+ * Code generation for model "Final_test".
+ *
+ * Model version              : 1.53
+ * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
+ * C source code generated on : Sat Sep 15 16:14:57 2018
+ *
+ * Target selection: ert.tlc
+ * Note: GRT includes extra infrastructure and instrumentation for prototyping
+ * Embedded hardware selection: ARM Compatible->ARM Cortex
+ * Code generation objectives: Unspecified
+ * Validation result: Not run
+ */
+
+#ifndef RTW_HEADER_rt_nonfinite_h_
+#define RTW_HEADER_rt_nonfinite_h_
+#include <stddef.h>
+#include "rtwtypes.h"
+
+extern real_T rtInf;
+extern real_T rtMinusInf;
+extern real_T rtNaN;
+extern real32_T rtInfF;
+extern real32_T rtMinusInfF;
+extern real32_T rtNaNF;
+extern void rt_InitInfAndNaN(size_t realSize);
+extern boolean_T rtIsInf(real_T value);
+extern boolean_T rtIsInfF(real32_T value);
+extern boolean_T rtIsNaN(real_T value);
+extern boolean_T rtIsNaNF(real32_T value);
+typedef struct {
+  struct {
+    uint32_T wordH;
+    uint32_T wordL;
+  } words;
+} BigEndianIEEEDouble;
+
+typedef struct {
+  struct {
+    uint32_T wordL;
+    uint32_T wordH;
+  } words;
+} LittleEndianIEEEDouble;
+
+typedef struct {
+  union {
+    real32_T wordLreal;
+    uint32_T wordLuint;
+  } wordL;
+} IEEESingle;
+
+#endif                                 /* RTW_HEADER_rt_nonfinite_h_ */

### 2018-09-16 paper/Matlab_code/Final_test_ert_rtw/rtmodel.h

@@ -1,0 +1,43 @@
+/*
+ *  rtmodel.h:
+ *
+ * Academic License - for use in teaching, academic research, and meeting
+ * course requirements at degree granting institutions only.  Not for
+ * government, commercial, or other organizational use.
+ *
+ * Code generation for model "Final_test".
+ *
+ * Model version              : 1.53
+ * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
+ * C source code generated on : Sat Sep 15 16:14:57 2018
+ *
+ * Target selection: ert.tlc
+ * Note: GRT includes extra infrastructure and instrumentation for prototyping
+ * Embedded hardware selection: ARM Compatible->ARM Cortex
+ * Code generation objectives: Unspecified
+ * Validation result: Not run
+ */
+/*
+ * rtmodel.h
+ *
+ * Code generation for Simulink model "Final_test".
+ *
+ * Simulink Coder version                : 8.14 (R2018a) 06-Feb-2018
+ * C source code generated on : Sat Sep 15 16:14:57 2018
+ *
+ * Note that the generated code is not dependent on this header file.
+ * The file is used in cojuction with the automatic build procedure.
+ * It is included by the sample main executable harness
+ * MATLAB/rtw/c/src/common/rt_main.c.
+ *
+ */
+#ifndef RTW_HEADER_rtmodel_h_
+#define RTW_HEADER_rtmodel_h_
+
+/*
+ *  Includes the appropriate headers when we are using rtModel
+ */
+#include "Final_test.h"
+#define GRTINTERFACE                   0
+#include "Final_test.h"
+#endif                                 /* RTW_HEADER_rtmodel_h_ */

### 2018-09-16 paper/Matlab_code/Final_test_ert_rtw/rtwtypes.h

@@ -1,0 +1,42 @@
+/*
+ * rtwtypes.h
+ *
+ * Academic License - for use in teaching, academic research, and meeting
+ * course requirements at degree granting institutions only.  Not for
+ * government, commercial, or other organizational use.
+ *
+ * Code generation for model "Final_test".
+ *
+ * Model version              : 1.53
+ * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
+ * C source code generated on : Sat Sep 15 16:14:57 2018
+ *
+ * Target selection: ert.tlc
+ * Note: GRT includes extra infrastructure and instrumentation for prototyping
+ * Embedded hardware selection: ARM Compatible->ARM Cortex
+ * Code generation objectives: Unspecified
+ * Validation result: Not run
+ */
+
+#ifndef RTWTYPES_H
+#define RTWTYPES_H
+#include "tmwtypes.h"
+#include "simstruc_types.h"
+#ifndef POINTER_T
+# define POINTER_T
+
+typedef void * pointer_T;
+
+#endif
+
+/* Logical type definitions */
+#if (!defined(__cplusplus))
+#  ifndef false
+#   define false                       (0U)
+#  endif
+
+#  ifndef true
+#   define true                        (1U)
+#  endif
+#endif
+#endif                                 /* RTWTYPES_H */

### 2018-09-16 paper/Matlab_code/no_disturbance.m

@@ -1,0 +1,9 @@
+close all
+figure(1)
+hold on
+plot(orient1(:,1),orient1(:,2))
+plot(orient2(:,1),orient2(:,2))
+plot(orient3(:,1),orient3(:,2))
+xlabel("Time (s)"); ylabel("Wind Voltage (mV)");
+title("Orientation of Sensor");
+legend("Normal","Parallel","Inline");

### 2018-09-16 paper/Matlab_code/plotting_figures.m

@@ -1,0 +1,55 @@
+close all
+% figure(1)
+% hold on
+% plot(orient1(:,1),orient1(:,2))
+% plot(orient2(:,1),orient2(:,2))
+% plot(orient3(:,1),orient3(:,2))
+% xlabel("Time (s)"); ylabel("Wind Voltage (mV)");
+% title("Orientation of Sensor");
+% legend("Normal","Parallel","Inline");
+% 
+% figure(2)
+% data = [510,550,520,630,660,667,610;
+%    597,589,659,680,682,676,660;
+%    657,675,667,635,668,672,673;
+%    599,650,670,680,640,630,675;
+%    540,660,650,630,660,670,620];
+% 
+% data2 = [676;686;676;681;680;679;680;676;672;670];
+% m = heatmap(data,'ColorbarVisible','off')
+% p = caxis
+% colormap jet
+% n = heatmap(data2,'ColorbarVisible','off')
+% colormap jet
+% 
+% xlim({'1','1'})
+% ylim({'1','10'})
+
+% figure(2)
+% hold on
+% yyaxis left
+% plot(resp(:,1),resp(:,2)+13.29)
+% ylabel("Wind Voltage (mV)");
+% 
+% yyaxis right
+% plot(respT(:,1)-4.59,respT(:,10))
+% ylabel("Thrust Value (N)");
+% xlabel("Time (s)");
+% title("Demonstration of Wind Sensor Range");
+% legend("Wind Response","Thrust Response");
+% hold off
+
+figure(3)
+title("PWM_r");
+hold on
+plot(pwm_r_comparison(:,1),pwm_r_comparison(:,8))
+plot(pwm_r(:,1),pwm_r(:,10))
+plot(pwm_r_comparison(:,1),pwm_r_comparison(:,7))
+
+legend("Desired","Actual Thrust","Kalman Estimation")
+
+figure(4)
+title("wind");
+hold on
+plot
+

### 2018-09-16 paper/drafts/data_for_paper/Final_test_ert_rtw/Final_test.c

@@ -7,9 +7,9 @@
  *
  * Code generation for model "Final_test".
  *
- * Model version              : 1.49
+ * Model version              : 1.54
  * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
- * C source code generated on : Fri Sep 14 14:53:31 2018
+ * C source code generated on : Sat Sep 15 17:33:20 2018
  *
  * Target selection: ert.tlc
  * Note: GRT includes extra infrastructure and instrumentation for prototyping
@@ -295,18 +295,18 @@ static void matlabCodegenHandle_matlabCodeg(dsp_simulink_MovingAverage_Fi_T *obj
 static void SystemProp_matlabCodegenSet_fdg(codertarget_arduinobase_in_fd_T *obj,
   boolean_T value)
 {
-  /* Start for MATLABSystem: '<S3>/Analog Input' */
+  /* Start for MATLABSystem: '<S4>/Analog Input' */
   obj->matlabCodegenIsDeleted = value;
 }
 
 static void matlabCodegenHandle_matlabC_fdg(codertarget_arduinobase_in_fd_T *obj)
 {
-  /* Start for MATLABSystem: '<S3>/Analog Input' */
+  /* Start for MATLABSystem: '<S4>/Analog Input' */
   if (!obj->matlabCodegenIsDeleted) {
     SystemProp_matlabCodegenSet_fdg(obj, true);
   }
 
-  /* End of Start for MATLABSystem: '<S3>/Analog Input' */
+  /* End of Start for MATLABSystem: '<S4>/Analog Input' */
 }
 
 static void SystemProp_matlabCodegenSetA_fd(codertarget_arduinobase_int_f_T *obj,
@@ -332,7 +332,7 @@ void Final_test_step(void)
   /* local block i/o variables */
   real_T rtb_PWMsaturation;
   real_T rtb_IntegralGain;
-  real_T rtb_IntegralGain_g;
+  real_T rtb_IntegralGain_c;
   boolean_T rtb_FixPtRelationalOperator;
   boolean_T rtb_FixPtRelationalOperator_b;
   static const int8_T R[4] = { 20, 0, 0, 20 };
@@ -340,9 +340,9 @@ void Final_test_step(void)
   static const real_T a[4] = { 0.9998, -0.0394, 0.009851, 0.9702 };
 
[…]

### 2018-09-16 paper/drafts/data_for_paper/Final_test_ert_rtw/Final_test.h

@@ -7,9 +7,9 @@
  *
  * Code generation for model "Final_test".
  *
- * Model version              : 1.49
+ * Model version              : 1.54
  * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
- * C source code generated on : Fri Sep 14 14:53:31 2018
+ * C source code generated on : Sat Sep 15 17:33:20 2018
  *
  * Target selection: ert.tlc
  * Note: GRT includes extra infrastructure and instrumentation for prototyping
@@ -176,35 +176,36 @@
 
 /* Block signals (default storage) */
 typedef struct {
+  real_T ManualSwitch4;                /* '<Root>/Manual Switch4' */
+  real_T e;                            /* '<S13>/Sum' */
+  real_T TransferFcn1;                 /* '<S4>/Transfer Fcn1' */
+  real_T Product;                      /* '<S12>/Product' */
+  real_T Sum2;                         /* '<S12>/Sum2' */
+  real_T Sum1;                         /* '<S12>/Sum1' */
+  real_T Product_d;                    /* '<S13>/Product' */
+  real_T Sum;                          /* '<S27>/Sum' */
+  real_T Saturation;                   /* '<S13>/Saturation' */
+  real_T ManualPWM;                    /* '<Root>/Manual PWM' */
+  real_T Add;                          /* '<S2>/Add' */
+  real_T Merge;                        /* '<S2>/Merge' */
+  real_T Integrator1;                  /* '<S14>/Integrator1' */
+  real_T Sum_k;                        /* '<S15>/Sum' */
+  real_T Clock;                        /* '<Root>/Clock' */
+  real_T Sum_b;                        /* '<Root>/Sum' */
+  real_T ManualSwitch1[9];             /* '<Root>/Manual Switch1' */
   real_T csumrev[9];
   real_T P_bar[4];
   real_T a[4];
   real_T xh_bar[2];
   real_T K[2];
-  real_T e;                            /* '<S8>/Sum' */
-  real_T TransferFcn1;                 /* '<S3>/Transfer Fcn1' */
-  real_T Sum;                          /* '<S22>/Sum' */
-  real_T Saturation;                   /* '<S8>/Saturation' */
-  real_T Product;                      /* '<S7>/Product' */
-  real_T Sum2;                         /* '<S7>/Sum2' */
-  real_T Product_m;                    /* '<S2>/Product' */
-  real_T ManualPWM;                    /* '<Root>/Manual PWM' */
[…]

### 2018-09-16 paper/drafts/data_for_paper/Final_test_ert_rtw/Final_test_data.c

@@ -7,9 +7,9 @@
  *
  * Code generation for model "Final_test".
  *
- * Model version              : 1.49
+ * Model version              : 1.54
  * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
- * C source code generated on : Fri Sep 14 14:53:31 2018
+ * C source code generated on : Sat Sep 15 17:33:20 2018
  *
  * Target selection: ert.tlc
  * Note: GRT includes extra infrastructure and instrumentation for prototyping
@@ -23,38 +23,38 @@
 
 /* Block parameters (default storage) */
 P_Final_test_T Final_test_P = {
-  /* Mask Parameter: DiscretePIDController_I
-   * Referenced by: '<S17>/Integral Gain'
-   */
-  0.01,
-
   /* Mask Parameter: PIDController3_I
-   * Referenced by: '<S22>/Integral Gain'
+   * Referenced by: '<S27>/Integral Gain'
    */
   5.23638207345188,
 
-  /* Mask Parameter: PIDController3_P
-   * Referenced by: '<S22>/Proportional Gain'
+  /* Mask Parameter: DiscretePIDController_I
+   * Referenced by: '<S22>/Integral Gain'
    */
-  10.1984567978833,
+  0.01,
 
   /* Mask Parameter: DiscretePIDController_P
-   * Referenced by: '<S17>/Proportional Gain'
+   * Referenced by: '<S22>/Proportional Gain'
    */
   0.05,
 
+  /* Mask Parameter: PIDController3_P
+   * Referenced by: '<S27>/Proportional Gain'
+   */
+  10.1984567978833,
+
   /* Mask Parameter: CompareToConstant_const
-   * Referenced by: '<S13>/Constant'
+   * Referenced by: '<S18>/Constant'
    */
   3.0,
 
   /* Mask Parameter: DetectChange_vinit
-   * Referenced by: '<S18>/Delay Input1'
+   * Referenced by: '<S21>/Delay Input1'
    */
   0.0,
 
-  /* Mask Parameter: DetectChange_vinit_c
-   * Referenced by: '<S16>/Delay Input1'
+  /* Mask Parameter: DetectChange_vinit_i
+   * Referenced by: '<S23>/Delay Input1'
    */
   0.0,
 
[…]

### 2018-09-16 paper/drafts/data_for_paper/Final_test_ert_rtw/Final_test_dt.h

@@ -7,9 +7,9 @@
  *
  * Code generation for model "Final_test".
  *
- * Model version              : 1.49
+ * Model version              : 1.54
  * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
- * C source code generated on : Fri Sep 14 14:53:31 2018
+ * C source code generated on : Sat Sep 15 17:33:20 2018
  *
  * Target selection: ert.tlc
  * Note: GRT includes extra infrastructure and instrumentation for prototyping
@@ -70,7 +70,9 @@ static const char_T * rtDataTypeNames[] = {
 
 /* data type transitions for block I/O structure */
 static DataTypeTransition rtBTransitions[] = {
-  { (char_T *)(&Final_test_B.e), 0, 0, 27 }
+  { (char_T *)(&Final_test_B.ManualSwitch4), 0, 0, 25 },
+
+  { (char_T *)(&Final_test_B.Integrator), 0, 0, 6 }
   ,
 
   { (char_T *)(&Final_test_DW.gobj_0), 15, 0, 2 },
@@ -87,9 +89,9 @@ static DataTypeTransition rtBTransitions[] = {
 
   { (char_T *)(&Final_test_DW.DelayInput1_DSTATE), 0, 0, 11 },
 
-  { (char_T *)(&Final_test_DW.FromWs_PWORK.TimePtr), 11, 0, 11 },
+  { (char_T *)(&Final_test_DW.FromWs_PWORK.TimePtr), 11, 0, 12 },
 
-  { (char_T *)(&Final_test_DW.FromWs_IWORK.PrevIndex), 10, 0, 1 },
+  { (char_T *)(&Final_test_DW.FromWs_IWORK.PrevIndex), 10, 0, 2 },
 
   { (char_T *)(&Final_test_DW.Integrator_PrevResetState), 2, 0, 5 },
 
@@ -98,15 +100,15 @@ static DataTypeTransition rtBTransitions[] = {
 
 /* data type transition table for block I/O structure */
 static DataTypeTransitionTable rtBTransTable = {
-  12U,
+  13U,
   rtBTransitions
 };
 
 /* data type transitions for Parameters structure */
 static DataTypeTransition rtPTransitions[] = {
-  { (char_T *)(&Final_test_P.DiscretePIDController_I), 0, 0, 49 },
+  { (char_T *)(&Final_test_P.PIDController3_I), 0, 0, 49 },
 
[…]

### 2018-09-16 paper/drafts/data_for_paper/Final_test_ert_rtw/Final_test_private.h

@@ -7,9 +7,9 @@
  *
  * Code generation for model "Final_test".
  *
- * Model version              : 1.49
+ * Model version              : 1.54
  * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
- * C source code generated on : Fri Sep 14 14:53:31 2018
+ * C source code generated on : Sat Sep 15 17:33:20 2018
  *
  * Target selection: ert.tlc
  * Note: GRT includes extra infrastructure and instrumentation for prototyping
@@ -40,7 +40,7 @@
 # define rtmSetTPtr(rtm, val)          ((rtm)->Timing.t = (val))
 #endif
 
-/* Used by FromWorkspace Block: '<S6>/FromWs' */
+/* Used by FromWorkspace Block: '<S10>/FromWs' */
 #ifndef rtInterpolate
 # define rtInterpolate(v1,v2,f1,f2)    (((v1)==(v2))?((double)(v1)): (((f1)*((double)(v1)))+((f2)*((double)(v2)))))
 #endif

### 2018-09-16 paper/drafts/data_for_paper/Final_test_ert_rtw/Final_test_types.h

@@ -7,9 +7,9 @@
  *
  * Code generation for model "Final_test".
  *
- * Model version              : 1.49
+ * Model version              : 1.54
  * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
- * C source code generated on : Fri Sep 14 14:53:31 2018
+ * C source code generated on : Sat Sep 15 17:33:20 2018
  *
  * Target selection: ert.tlc
  * Note: GRT includes extra infrastructure and instrumentation for prototyping
@@ -48,7 +48,7 @@ typedef struct {
 
 #endif                                 /*typedef_dsp_private_SlidingWindowAv_f_T*/
 
-/* Custom Type definition for MATLABSystem: '<S3>/Analog Input' */
+/* Custom Type definition for MATLABSystem: '<S4>/Analog Input' */
 #include "MW_SVD.h"
 #ifndef typedef_cell_wrap_Final_test_T
 #define typedef_cell_wrap_Final_test_T

### 2018-09-16 paper/drafts/data_for_paper/Final_test_ert_rtw/html/define.js

@@ -26,15 +26,15 @@ this.def["matlabCodegenHandle_matlabC_fdg"] = {file: "Final_test_c.html",line:30
 this.def["SystemProp_matlabCodegenSetA_fd"] = {file: "Final_test_c.html",line:312,type:"fcn"};
 this.def["matlabCodegenHandle_matlabCo_fd"] = {file: "Final_test_c.html",line:319,type:"fcn"};
 this.def["Final_test_step"] = {file: "Final_test_c.html",line:330,type:"fcn"};
-this.def["Final_test_derivatives"] = {file: "Final_test_c.html",line:1016,type:"fcn"};
-this.def["Final_test_initialize"] = {file: "Final_test_c.html",line:1035,type:"fcn"};
-this.def["Final_test_terminate"] = {file: "Final_test_c.html",line:1297,type:"fcn"};
-this.def["B_Final_test_T"] = {file: "Final_test_h.html",line:208,type:"type"};
-this.def["DW_Final_test_T"] = {file: "Final_test_h.html",line:282,type:"type"};
-this.def["X_Final_test_T"] = {file: "Final_test_h.html",line:289,type:"type"};
-this.def["XDot_Final_test_T"] = {file: "Final_test_h.html",line:296,type:"type"};
-this.def["XDis_Final_test_T"] = {file: "Final_test_h.html",line:303,type:"type"};
-this.def["ODE3_IntgData"] = {file: "Final_test_h.html",line:312,type:"type"};
+this.def["Final_test_derivatives"] = {file: "Final_test_c.html",line:1073,type:"fcn"};
+this.def["Final_test_initialize"] = {file: "Final_test_c.html",line:1092,type:"fcn"};
+this.def["Final_test_terminate"] = {file: "Final_test_c.html",line:1366,type:"fcn"};
+this.def["B_Final_test_T"] = {file: "Final_test_h.html",line:209,type:"type"};
+this.def["DW_Final_test_T"] = {file: "Final_test_h.html",line:293,type:"type"};
+this.def["X_Final_test_T"] = {file: "Final_test_h.html",line:300,type:"type"};
+this.def["XDot_Final_test_T"] = {file: "Final_test_h.html",line:307,type:"type"};
+this.def["XDis_Final_test_T"] = {file: "Final_test_h.html",line:314,type:"type"};
[…]

### 2018-09-16 paper/drafts/data_for_paper/Final_test_ert_rtw/rt_nonfinite.c

@@ -7,9 +7,9 @@
  *
  * Code generation for model "Final_test".
  *
- * Model version              : 1.49
+ * Model version              : 1.54
  * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
- * C source code generated on : Fri Sep 14 14:53:31 2018
+ * C source code generated on : Sat Sep 15 17:33:20 2018
  *
  * Target selection: ert.tlc
  * Note: GRT includes extra infrastructure and instrumentation for prototyping

### 2018-09-16 paper/drafts/data_for_paper/Final_test_ert_rtw/rtmodel.h

@@ -7,9 +7,9 @@
  *
  * Code generation for model "Final_test".
  *
- * Model version              : 1.49
+ * Model version              : 1.54
  * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
- * C source code generated on : Fri Sep 14 14:53:31 2018
+ * C source code generated on : Sat Sep 15 17:33:20 2018
  *
  * Target selection: ert.tlc
  * Note: GRT includes extra infrastructure and instrumentation for prototyping
@@ -23,7 +23,7 @@
  * Code generation for Simulink model "Final_test".
  *
  * Simulink Coder version                : 8.14 (R2018a) 06-Feb-2018
- * C source code generated on : Fri Sep 14 14:53:31 2018
+ * C source code generated on : Sat Sep 15 17:33:20 2018
  *
  * Note that the generated code is not dependent on this header file.
  * The file is used in cojuction with the automatic build procedure.

### 2018-09-16 paper/drafts/data_for_paper/friday_night/Final_test_ert_rtw/Final_test.c

@@ -1,0 +1,1349 @@
+/*
+ * Final_test.c
+ *
+ * Academic License - for use in teaching, academic research, and meeting
+ * course requirements at degree granting institutions only.  Not for
+ * government, commercial, or other organizational use.
+ *
+ * Code generation for model "Final_test".
+ *
+ * Model version              : 1.54
+ * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
+ * C source code generated on : Sat Sep 15 17:18:11 2018
+ *
+ * Target selection: ert.tlc
+ * Note: GRT includes extra infrastructure and instrumentation for prototyping
+ * Embedded hardware selection: ARM Compatible->ARM Cortex
+ * Code generation objectives: Unspecified
+ * Validation result: Not run
+ */
+
+#include "Final_test.h"
+#include "Final_test_private.h"
+#include "Final_test_dt.h"
+
+/* Block signals (default storage) */
+B_Final_test_T Final_test_B;
+
+/* Continuous states */
+X_Final_test_T Final_test_X;
+
+/* Block states (default storage) */
+DW_Final_test_T Final_test_DW;
+
+/* Real-time model */
+RT_MODEL_Final_test_T Final_test_M_;
+RT_MODEL_Final_test_T *const Final_test_M = &Final_test_M_;
+
+/* Forward declaration for local functions */
+static codertarget_arduinobase_int_f_T *arduino_PWMOutput_arduino_PWMOu
+  (codertarget_arduinobase_int_f_T *obj);
+static void SystemProp_matlabCodegenSetAn_f(dsp_simulink_MovingAverage_f_T *obj,
+  boolean_T value);
+static void Final_test_SystemCore_release_f(dsp_simulink_MovingAverage_f_T *obj);
+static void Final_test_SystemCore_delete_f(dsp_simulink_MovingAverage_f_T *obj);
+static void matlabCodegenHandle_matlabCod_f(dsp_simulink_MovingAverage_f_T *obj);
[…]

### 2018-09-16 paper/drafts/data_for_paper/friday_night/Final_test_ert_rtw/Final_test.h

@@ -1,0 +1,664 @@
+/*
+ * Final_test.h
+ *
+ * Academic License - for use in teaching, academic research, and meeting
+ * course requirements at degree granting institutions only.  Not for
+ * government, commercial, or other organizational use.
+ *
+ * Code generation for model "Final_test".
+ *
+ * Model version              : 1.54
+ * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
+ * C source code generated on : Sat Sep 15 17:18:11 2018
+ *
+ * Target selection: ert.tlc
+ * Note: GRT includes extra infrastructure and instrumentation for prototyping
+ * Embedded hardware selection: ARM Compatible->ARM Cortex
+ * Code generation objectives: Unspecified
+ * Validation result: Not run
+ */
+
+#ifndef RTW_HEADER_Final_test_h_
+#define RTW_HEADER_Final_test_h_
+#include <math.h>
+#include <string.h>
+#include <float.h>
+#include <stddef.h>
+#ifndef Final_test_COMMON_INCLUDES_
+# define Final_test_COMMON_INCLUDES_
+#include "rtwtypes.h"
+#include "rtw_extmode.h"
+#include "sysran_types.h"
+#include "rtw_continuous.h"
+#include "rtw_solver.h"
+#include "dt_info.h"
+#include "ext_work.h"
+#include "MW_PWM.h"
+#include "MW_AnalogIn.h"
+#endif                                 /* Final_test_COMMON_INCLUDES_ */
+
+#include "Final_test_types.h"
+
+/* Shared type includes */
+#include "multiword_types.h"
+#include "MW_target_hardware_resources.h"
+#include "rt_nonfinite.h"
+#include "rtGetInf.h"
+
+/* Macros for accessing real-time model data structure */
+#ifndef rtmGetContStateDisabled
+# define rtmGetContStateDisabled(rtm)  ((rtm)->contStateDisabled)
+#endif
+
+#ifndef rtmSetContStateDisabled
+# define rtmSetContStateDisabled(rtm, val) ((rtm)->contStateDisabled = (val))
+#endif
+
+#ifndef rtmGetContStates
+# define rtmGetContStates(rtm)         ((rtm)->contStates)
+#endif
+
+#ifndef rtmSetContStates
[…]

### 2018-09-16 paper/drafts/data_for_paper/friday_night/Final_test_ert_rtw/Final_test_data.c

@@ -1,0 +1,300 @@
+/*
+ * Final_test_data.c
+ *
+ * Academic License - for use in teaching, academic research, and meeting
+ * course requirements at degree granting institutions only.  Not for
+ * government, commercial, or other organizational use.
+ *
+ * Code generation for model "Final_test".
+ *
+ * Model version              : 1.54
+ * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
+ * C source code generated on : Sat Sep 15 17:18:11 2018
+ *
+ * Target selection: ert.tlc
+ * Note: GRT includes extra infrastructure and instrumentation for prototyping
+ * Embedded hardware selection: ARM Compatible->ARM Cortex
+ * Code generation objectives: Unspecified
+ * Validation result: Not run
+ */
+
+#include "Final_test.h"
+#include "Final_test_private.h"
+
+/* Block parameters (default storage) */
+P_Final_test_T Final_test_P = {
+  /* Mask Parameter: PIDController3_I
+   * Referenced by: '<S27>/Integral Gain'
+   */
+  5.23638207345188,
+
+  /* Mask Parameter: DiscretePIDController_I
+   * Referenced by: '<S22>/Integral Gain'
+   */
+  0.01,
+
+  /* Mask Parameter: DiscretePIDController_P
+   * Referenced by: '<S22>/Proportional Gain'
+   */
+  0.05,
+
+  /* Mask Parameter: PIDController3_P
+   * Referenced by: '<S27>/Proportional Gain'
+   */
+  10.1984567978833,
+
+  /* Mask Parameter: CompareToConstant_const
+   * Referenced by: '<S18>/Constant'
+   */
+  3.0,
+
+  /* Mask Parameter: DetectChange_vinit
+   * Referenced by: '<S21>/Delay Input1'
+   */
+  0.0,
+
+  /* Mask Parameter: DetectChange_vinit_i
+   * Referenced by: '<S23>/Delay Input1'
+   */
+  0.0,
+
+  /* Expression: 0.8
+   * Referenced by: '<Root>/Gain'
+   */
+  0.8,
+
+  /* Expression: 0.8
+   * Referenced by: '<Root>/Gain1'
+   */
+  0.8,
+
[…]

### 2018-09-16 paper/drafts/data_for_paper/friday_night/Final_test_ert_rtw/Final_test_dt.h

@@ -1,0 +1,120 @@
+/*
+ * Final_test_dt.h
+ *
+ * Academic License - for use in teaching, academic research, and meeting
+ * course requirements at degree granting institutions only.  Not for
+ * government, commercial, or other organizational use.
+ *
+ * Code generation for model "Final_test".
+ *
+ * Model version              : 1.54
+ * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
+ * C source code generated on : Sat Sep 15 17:18:11 2018
+ *
+ * Target selection: ert.tlc
+ * Note: GRT includes extra infrastructure and instrumentation for prototyping
+ * Embedded hardware selection: ARM Compatible->ARM Cortex
+ * Code generation objectives: Unspecified
+ * Validation result: Not run
+ */
+
+#include "ext_types.h"
+
+/* data type size table */
+static uint_T rtDataTypeSizes[] = {
+  sizeof(real_T),
+  sizeof(real32_T),
+  sizeof(int8_T),
+  sizeof(uint8_T),
+  sizeof(int16_T),
+  sizeof(uint16_T),
+  sizeof(int32_T),
+  sizeof(uint32_T),
+  sizeof(boolean_T),
+  sizeof(fcn_call_T),
+  sizeof(int_T),
+  sizeof(pointer_T),
+  sizeof(action_T),
+  2*sizeof(uint32_T),
+  sizeof(dsp_simulink_MovingAverage_f_T),
+  sizeof(dsp_private_SlidingWindowAv_f_T),
+  sizeof(dsp_simulink_MovingAverage_Fi_T),
+  sizeof(dsp_private_SlidingWindowAver_T),
+  sizeof(codertarget_arduinobase_int_f_T),
+  sizeof(codertarget_arduinobase_in_fd_T)
+};
+
+/* data type name table */
+static const char_T * rtDataTypeNames[] = {
+  "real_T",
+  "real32_T",
+  "int8_T",
+  "uint8_T",
+  "int16_T",
+  "uint16_T",
+  "int32_T",
+  "uint32_T",
+  "boolean_T",
+  "fcn_call_T",
+  "int_T",
+  "pointer_T",
+  "action_T",
+  "timer_uint32_pair_T",
+  "dsp_simulink_MovingAverage_f_T",
+  "dsp_private_SlidingWindowAv_f_T",
[…]

### 2018-09-16 paper/drafts/data_for_paper/friday_night/Final_test_ert_rtw/Final_test_private.h

@@ -1,0 +1,57 @@
+/*
+ * Final_test_private.h
+ *
+ * Academic License - for use in teaching, academic research, and meeting
+ * course requirements at degree granting institutions only.  Not for
+ * government, commercial, or other organizational use.
+ *
+ * Code generation for model "Final_test".
+ *
+ * Model version              : 1.54
+ * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
+ * C source code generated on : Sat Sep 15 17:18:11 2018
+ *
+ * Target selection: ert.tlc
+ * Note: GRT includes extra infrastructure and instrumentation for prototyping
+ * Embedded hardware selection: ARM Compatible->ARM Cortex
+ * Code generation objectives: Unspecified
+ * Validation result: Not run
+ */
+
+#ifndef RTW_HEADER_Final_test_private_h_
+#define RTW_HEADER_Final_test_private_h_
+#include "rtwtypes.h"
+#include "multiword_types.h"
+
+/* Private macros used by the generated code to access rtModel */
+#ifndef rtmIsMajorTimeStep
+# define rtmIsMajorTimeStep(rtm)       (((rtm)->Timing.simTimeStep) == MAJOR_TIME_STEP)
+#endif
+
+#ifndef rtmIsMinorTimeStep
+# define rtmIsMinorTimeStep(rtm)       (((rtm)->Timing.simTimeStep) == MINOR_TIME_STEP)
+#endif
+
+#ifndef rtmSetTFinal
+# define rtmSetTFinal(rtm, val)        ((rtm)->Timing.tFinal = (val))
+#endif
+
+#ifndef rtmSetTPtr
+# define rtmSetTPtr(rtm, val)          ((rtm)->Timing.t = (val))
+#endif
+
+/* Used by FromWorkspace Block: '<S10>/FromWs' */
+#ifndef rtInterpolate
+# define rtInterpolate(v1,v2,f1,f2)    (((v1)==(v2))?((double)(v1)): (((f1)*((double)(v1)))+((f2)*((double)(v2)))))
+#endif
+
+#ifndef rtRound
+# define rtRound(v)                    ( ((v) >= 0) ? floor((v) + 0.5) : ceil((v) - 0.5) )
+#endif
+
+extern real_T rt_powd_snf(real_T u0, real_T u1);
+
+/* private model entry point functions */
+extern void Final_test_derivatives(void);
+
+#endif                                 /* RTW_HEADER_Final_test_private_h_ */

### 2018-09-16 paper/drafts/data_for_paper/friday_night/Final_test_ert_rtw/Final_test_types.h

@@ -1,0 +1,154 @@
+/*
+ * Final_test_types.h
+ *
+ * Academic License - for use in teaching, academic research, and meeting
+ * course requirements at degree granting institutions only.  Not for
+ * government, commercial, or other organizational use.
+ *
+ * Code generation for model "Final_test".
+ *
+ * Model version              : 1.54
+ * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
+ * C source code generated on : Sat Sep 15 17:18:11 2018
+ *
+ * Target selection: ert.tlc
+ * Note: GRT includes extra infrastructure and instrumentation for prototyping
+ * Embedded hardware selection: ARM Compatible->ARM Cortex
+ * Code generation objectives: Unspecified
+ * Validation result: Not run
+ */
+
+#ifndef RTW_HEADER_Final_test_types_h_
+#define RTW_HEADER_Final_test_types_h_
+#include "rtwtypes.h"
+#include "multiword_types.h"
+#ifndef typedef_dsp_private_SlidingWindowAver_T
+#define typedef_dsp_private_SlidingWindowAver_T
+
+typedef struct {
+  int32_T isInitialized;
+  boolean_T isSetupComplete;
+  real_T pCumSum;
+  real_T pCumSumRev[4];
+  real_T pCumRevIndex;
+} dsp_private_SlidingWindowAver_T;
+
+#endif                                 /*typedef_dsp_private_SlidingWindowAver_T*/
+
+#ifndef typedef_dsp_private_SlidingWindowAv_f_T
+#define typedef_dsp_private_SlidingWindowAv_f_T
+
+typedef struct {
+  int32_T isInitialized;
+  boolean_T isSetupComplete;
+  real_T pCumSum;
+  real_T pCumSumRev[9];
+  real_T pCumRevIndex;
+} dsp_private_SlidingWindowAv_f_T;
+
+#endif                                 /*typedef_dsp_private_SlidingWindowAv_f_T*/
+
+/* Custom Type definition for MATLABSystem: '<S4>/Analog Input' */
+#include "MW_SVD.h"
+#ifndef typedef_cell_wrap_Final_test_T
+#define typedef_cell_wrap_Final_test_T
+
+typedef struct {
+  uint32_T f1[8];
+} cell_wrap_Final_test_T;
+
[…]

### 2018-09-16 paper/drafts/data_for_paper/friday_night/Final_test_ert_rtw/html/define.js

@@ -1,0 +1,193 @@
+function CodeDefine() { 
+this.def = new Array();
+this.def["IsrOverrun"] = {file: "ert_main_c.html",line:8,type:"var"};
+this.def["OverrunFlag"] = {file: "ert_main_c.html",line:9,type:"var"};
+this.def["rt_OneStep"] = {file: "ert_main_c.html",line:10,type:"fcn"};
+this.def["stopRequested"] = {file: "ert_main_c.html",line:38,type:"var"};
+this.def["main"] = {file: "ert_main_c.html",line:39,type:"fcn"};
+this.def["Final_test_B"] = {file: "Final_test_c.html",line:26,type:"var"};
+this.def["Final_test_X"] = {file: "Final_test_c.html",line:29,type:"var"};
+this.def["Final_test_DW"] = {file: "Final_test_c.html",line:32,type:"var"};
+this.def["Final_test_M_"] = {file: "Final_test_c.html",line:35,type:"var"};
+this.def["Final_test_M"] = {file: "Final_test_c.html",line:36,type:"var"};
+this.def["rt_ertODEUpdateContinuousStates"] = {file: "Final_test_c.html",line:62,type:"fcn"};
+this.def["arduino_PWMOutput_arduino_PWMOu"] = {file: "Final_test_c.html",line:139,type:"fcn"};
+this.def["rt_powd_snf"] = {file: "Final_test_c.html",line:165,type:"fcn"};
+this.def["SystemProp_matlabCodegenSetAn_f"] = {file: "Final_test_c.html",line:211,type:"fcn"};
+this.def["Final_test_SystemCore_release_f"] = {file: "Final_test_c.html",line:217,type:"fcn"};
+this.def["Final_test_SystemCore_delete_f"] = {file: "Final_test_c.html",line:230,type:"fcn"};
+this.def["matlabCodegenHandle_matlabCod_f"] = {file: "Final_test_c.html",line:235,type:"fcn"};
+this.def["SystemProp_matlabCodegenSetAnyP"] = {file: "Final_test_c.html",line:243,type:"fcn"};
+this.def["Final_test_SystemCore_release"] = {file: "Final_test_c.html",line:249,type:"fcn"};
+this.def["Final_test_SystemCore_delete"] = {file: "Final_test_c.html",line:262,type:"fcn"};
[…]

### 2018-09-16 paper/drafts/data_for_paper/friday_night/Final_test_ert_rtw/multiword_types.h

@@ -1,0 +1,165 @@
+/*
+ * multiword_types.h
+ *
+ * Academic License - for use in teaching, academic research, and meeting
+ * course requirements at degree granting institutions only.  Not for
+ * government, commercial, or other organizational use.
+ *
+ * Code generation for model "Final_test".
+ *
+ * Model version              : 1.54
+ * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
+ * C source code generated on : Sat Sep 15 17:18:11 2018
+ *
+ * Target selection: ert.tlc
+ * Note: GRT includes extra infrastructure and instrumentation for prototyping
+ * Embedded hardware selection: ARM Compatible->ARM Cortex
+ * Code generation objectives: Unspecified
+ * Validation result: Not run
+ */
+
+#ifndef MULTIWORD_TYPES_H
+#define MULTIWORD_TYPES_H
+#include "rtwtypes.h"
+
+/*
+ * Definitions supporting external data access
+ */
+typedef int32_T chunk_T;
+typedef uint32_T uchunk_T;
+
+/*
+ * MultiWord supporting definitions
+ */
+typedef long int long_T;
+
+/*
+ * MultiWord types
+ */
+typedef struct {
+  uint32_T chunks[2];
+} int64m_T;
+
+typedef struct {
+  int64m_T re;
+  int64m_T im;
+} cint64m_T;
+
+typedef struct {
+  uint32_T chunks[2];
+} uint64m_T;
+
+typedef struct {
+  uint64m_T re;
+  uint64m_T im;
+} cuint64m_T;
+
+typedef struct {
+  uint32_T chunks[3];
+} int96m_T;
+
+typedef struct {
+  int96m_T re;
+  int96m_T im;
+} cint96m_T;
+
+typedef struct {
+  uint32_T chunks[3];
+} uint96m_T;
+
+typedef struct {
+  uint96m_T re;
+  uint96m_T im;
+} cuint96m_T;
+
+typedef struct {
+  uint32_T chunks[4];
+} int128m_T;
+
+typedef struct {
+  int128m_T re;
+  int128m_T im;
+} cint128m_T;
+
+typedef struct {
+  uint32_T chunks[4];
+} uint128m_T;
+
+typedef struct {
+  uint128m_T re;
+  uint128m_T im;
+} cuint128m_T;
+
+typedef struct {
[…]

### 2018-09-16 paper/drafts/data_for_paper/friday_night/Final_test_ert_rtw/rtGetInf.c

@@ -1,0 +1,144 @@
+/*
+ * rtGetInf.c
+ *
+ * Academic License - for use in teaching, academic research, and meeting
+ * course requirements at degree granting institutions only.  Not for
+ * government, commercial, or other organizational use.
+ *
+ * Code generation for model "Final_test".
+ *
+ * Model version              : 1.54
+ * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
+ * C source code generated on : Sat Sep 15 17:18:11 2018
+ *
+ * Target selection: ert.tlc
+ * Note: GRT includes extra infrastructure and instrumentation for prototyping
+ * Embedded hardware selection: ARM Compatible->ARM Cortex
+ * Code generation objectives: Unspecified
+ * Validation result: Not run
+ */
+
+/*
+ * Abstract:
+ *      Function to initialize non-finite, Inf
+ */
+#include "rtGetInf.h"
+#define NumBitsPerChar                 8U
+
+/*
+ * Initialize rtInf needed by the generated code.
+ * Inf is initialized as non-signaling. Assumes IEEE.
+ */
+real_T rtGetInf(void)
+{
+  size_t bitsPerReal = sizeof(real_T) * (NumBitsPerChar);
+  real_T inf = 0.0;
+  if (bitsPerReal == 32U) {
+    inf = rtGetInfF();
+  } else {
+    uint16_T one = 1U;
+    enum {
+      LittleEndian,
+      BigEndian
+    } machByteOrder = (*((uint8_T *) &one) == 1U) ? LittleEndian : BigEndian;
+    switch (machByteOrder) {
+     case LittleEndian:
+      {
+        union {
+          LittleEndianIEEEDouble bitVal;
+          real_T fltVal;
+        } tmpVal;
+
+        tmpVal.bitVal.words.wordH = 0x7FF00000U;
+        tmpVal.bitVal.words.wordL = 0x00000000U;
+        inf = tmpVal.fltVal;
+        break;
+      }
+
+     case BigEndian:
+      {
+        union {
+          BigEndianIEEEDouble bitVal;
+          real_T fltVal;
+        } tmpVal;
+
+        tmpVal.bitVal.words.wordH = 0x7FF00000U;
+        tmpVal.bitVal.words.wordL = 0x00000000U;
+        inf = tmpVal.fltVal;
+        break;
[…]

### 2018-09-16 paper/drafts/data_for_paper/friday_night/Final_test_ert_rtw/rtGetInf.h

@@ -1,0 +1,32 @@
+/*
+ * rtGetInf.h
+ *
+ * Academic License - for use in teaching, academic research, and meeting
+ * course requirements at degree granting institutions only.  Not for
+ * government, commercial, or other organizational use.
+ *
+ * Code generation for model "Final_test".
+ *
+ * Model version              : 1.54
+ * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
+ * C source code generated on : Sat Sep 15 17:18:11 2018
+ *
+ * Target selection: ert.tlc
+ * Note: GRT includes extra infrastructure and instrumentation for prototyping
+ * Embedded hardware selection: ARM Compatible->ARM Cortex
+ * Code generation objectives: Unspecified
+ * Validation result: Not run
+ */
+
+#ifndef RTW_HEADER_rtGetInf_h_
+#define RTW_HEADER_rtGetInf_h_
+#include <stddef.h>
+#include "rtwtypes.h"
+#include "rt_nonfinite.h"
+
+extern real_T rtGetInf(void);
+extern real32_T rtGetInfF(void);
+extern real_T rtGetMinusInf(void);
+extern real32_T rtGetMinusInfF(void);
+
+#endif                                 /* RTW_HEADER_rtGetInf_h_ */

### 2018-09-16 paper/drafts/data_for_paper/friday_night/Final_test_ert_rtw/rtGetNaN.c

@@ -1,0 +1,104 @@
+/*
+ * rtGetNaN.c
+ *
+ * Academic License - for use in teaching, academic research, and meeting
+ * course requirements at degree granting institutions only.  Not for
+ * government, commercial, or other organizational use.
+ *
+ * Code generation for model "Final_test".
+ *
+ * Model version              : 1.54
+ * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
+ * C source code generated on : Sat Sep 15 17:18:11 2018
+ *
+ * Target selection: ert.tlc
+ * Note: GRT includes extra infrastructure and instrumentation for prototyping
+ * Embedded hardware selection: ARM Compatible->ARM Cortex
+ * Code generation objectives: Unspecified
+ * Validation result: Not run
+ */
+
+/*
+ * Abstract:
+ *      Function to initialize non-finite, NaN
+ */
+#include "rtGetNaN.h"
+#define NumBitsPerChar                 8U
+
+/*
+ * Initialize rtNaN needed by the generated code.
+ * NaN is initialized as non-signaling. Assumes IEEE.
+ */
+real_T rtGetNaN(void)
+{
+  size_t bitsPerReal = sizeof(real_T) * (NumBitsPerChar);
+  real_T nan = 0.0;
+  if (bitsPerReal == 32U) {
+    nan = rtGetNaNF();
+  } else {
+    uint16_T one = 1U;
+    enum {
+      LittleEndian,
+      BigEndian
+    } machByteOrder = (*((uint8_T *) &one) == 1U) ? LittleEndian : BigEndian;
+    switch (machByteOrder) {
+     case LittleEndian:
+      {
+        union {
+          LittleEndianIEEEDouble bitVal;
+          real_T fltVal;
+        } tmpVal;
+
+        tmpVal.bitVal.words.wordH = 0xFFF80000U;
+        tmpVal.bitVal.words.wordL = 0x00000000U;
+        nan = tmpVal.fltVal;
+        break;
+      }
+
+     case BigEndian:
+      {
+        union {
+          BigEndianIEEEDouble bitVal;
+          real_T fltVal;
+        } tmpVal;
+
+        tmpVal.bitVal.words.wordH = 0x7FFFFFFFU;
+        tmpVal.bitVal.words.wordL = 0xFFFFFFFFU;
+        nan = tmpVal.fltVal;
[…]

### 2018-09-16 paper/drafts/data_for_paper/friday_night/Final_test_ert_rtw/rtGetNaN.h

@@ -1,0 +1,30 @@
+/*
+ * rtGetNaN.h
+ *
+ * Academic License - for use in teaching, academic research, and meeting
+ * course requirements at degree granting institutions only.  Not for
+ * government, commercial, or other organizational use.
+ *
+ * Code generation for model "Final_test".
+ *
+ * Model version              : 1.54
+ * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
+ * C source code generated on : Sat Sep 15 17:18:11 2018
+ *
+ * Target selection: ert.tlc
+ * Note: GRT includes extra infrastructure and instrumentation for prototyping
+ * Embedded hardware selection: ARM Compatible->ARM Cortex
+ * Code generation objectives: Unspecified
+ * Validation result: Not run
+ */
+
+#ifndef RTW_HEADER_rtGetNaN_h_
+#define RTW_HEADER_rtGetNaN_h_
+#include <stddef.h>
+#include "rtwtypes.h"
+#include "rt_nonfinite.h"
+
+extern real_T rtGetNaN(void);
+extern real32_T rtGetNaNF(void);
+
+#endif                                 /* RTW_HEADER_rtGetNaN_h_ */

### 2018-09-16 paper/drafts/data_for_paper/friday_night/Final_test_ert_rtw/rt_nonfinite.c

@@ -1,0 +1,74 @@
+/*
+ * rt_nonfinite.c
+ *
+ * Academic License - for use in teaching, academic research, and meeting
+ * course requirements at degree granting institutions only.  Not for
+ * government, commercial, or other organizational use.
+ *
+ * Code generation for model "Final_test".
+ *
+ * Model version              : 1.54
+ * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
+ * C source code generated on : Sat Sep 15 17:18:11 2018
+ *
+ * Target selection: ert.tlc
+ * Note: GRT includes extra infrastructure and instrumentation for prototyping
+ * Embedded hardware selection: ARM Compatible->ARM Cortex
+ * Code generation objectives: Unspecified
+ * Validation result: Not run
+ */
+
+/*
+ * Abstract:
+ *      Function to initialize non-finites,
+ *      (Inf, NaN and -Inf).
+ */
+#include "rt_nonfinite.h"
+#include "rtGetNaN.h"
+#include "rtGetInf.h"
+
+real_T rtInf;
+real_T rtMinusInf;
+real_T rtNaN;
+real32_T rtInfF;
+real32_T rtMinusInfF;
+real32_T rtNaNF;
+
+/*
+ * Initialize the rtInf, rtMinusInf, and rtNaN needed by the
+ * generated code. NaN is initialized as non-signaling. Assumes IEEE.
+ */
+void rt_InitInfAndNaN(size_t realSize)
+{
+  (void) (realSize);
+  rtNaN = rtGetNaN();
+  rtNaNF = rtGetNaNF();
+  rtInf = rtGetInf();
+  rtInfF = rtGetInfF();
+  rtMinusInf = rtGetMinusInf();
+  rtMinusInfF = rtGetMinusInfF();
+}
+
+/* Test if value is infinite */
+boolean_T rtIsInf(real_T value)
+{
+  return (boolean_T)((value==rtInf || value==rtMinusInf) ? 1U : 0U);
+}
+
+/* Test if single-precision value is infinite */
+boolean_T rtIsInfF(real32_T value)
+{
+  return (boolean_T)(((value)==rtInfF || (value)==rtMinusInfF) ? 1U : 0U);
+}
+
+/* Test if value is not a number */
+boolean_T rtIsNaN(real_T value)
+{
+  return (boolean_T)((value!=value) ? 1U : 0U);
+}
+
[…]

### 2018-09-16 paper/drafts/data_for_paper/friday_night/Final_test_ert_rtw/rt_nonfinite.h

@@ -1,0 +1,58 @@
+/*
+ * rt_nonfinite.h
+ *
+ * Academic License - for use in teaching, academic research, and meeting
+ * course requirements at degree granting institutions only.  Not for
+ * government, commercial, or other organizational use.
+ *
+ * Code generation for model "Final_test".
+ *
+ * Model version              : 1.54
+ * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
+ * C source code generated on : Sat Sep 15 17:18:11 2018
+ *
+ * Target selection: ert.tlc
+ * Note: GRT includes extra infrastructure and instrumentation for prototyping
+ * Embedded hardware selection: ARM Compatible->ARM Cortex
+ * Code generation objectives: Unspecified
+ * Validation result: Not run
+ */
+
+#ifndef RTW_HEADER_rt_nonfinite_h_
+#define RTW_HEADER_rt_nonfinite_h_
+#include <stddef.h>
+#include "rtwtypes.h"
+
+extern real_T rtInf;
+extern real_T rtMinusInf;
+extern real_T rtNaN;
+extern real32_T rtInfF;
+extern real32_T rtMinusInfF;
+extern real32_T rtNaNF;
+extern void rt_InitInfAndNaN(size_t realSize);
+extern boolean_T rtIsInf(real_T value);
+extern boolean_T rtIsInfF(real32_T value);
+extern boolean_T rtIsNaN(real_T value);
+extern boolean_T rtIsNaNF(real32_T value);
+typedef struct {
+  struct {
+    uint32_T wordH;
+    uint32_T wordL;
+  } words;
+} BigEndianIEEEDouble;
+
+typedef struct {
+  struct {
+    uint32_T wordL;
+    uint32_T wordH;
+  } words;
+} LittleEndianIEEEDouble;
+
+typedef struct {
+  union {
+    real32_T wordLreal;
+    uint32_T wordLuint;
+  } wordL;
+} IEEESingle;
+
+#endif                                 /* RTW_HEADER_rt_nonfinite_h_ */

### 2018-09-16 paper/drafts/data_for_paper/friday_night/Final_test_ert_rtw/rtmodel.h

@@ -1,0 +1,43 @@
+/*
+ *  rtmodel.h:
+ *
+ * Academic License - for use in teaching, academic research, and meeting
+ * course requirements at degree granting institutions only.  Not for
+ * government, commercial, or other organizational use.
+ *
+ * Code generation for model "Final_test".
+ *
+ * Model version              : 1.54
+ * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
+ * C source code generated on : Sat Sep 15 17:18:11 2018
+ *
+ * Target selection: ert.tlc
+ * Note: GRT includes extra infrastructure and instrumentation for prototyping
+ * Embedded hardware selection: ARM Compatible->ARM Cortex
+ * Code generation objectives: Unspecified
+ * Validation result: Not run
+ */
+/*
+ * rtmodel.h
+ *
+ * Code generation for Simulink model "Final_test".
+ *
+ * Simulink Coder version                : 8.14 (R2018a) 06-Feb-2018
+ * C source code generated on : Sat Sep 15 17:18:11 2018
+ *
+ * Note that the generated code is not dependent on this header file.
+ * The file is used in cojuction with the automatic build procedure.
+ * It is included by the sample main executable harness
+ * MATLAB/rtw/c/src/common/rt_main.c.
+ *
+ */
+#ifndef RTW_HEADER_rtmodel_h_
+#define RTW_HEADER_rtmodel_h_
+
+/*
+ *  Includes the appropriate headers when we are using rtModel
+ */
+#include "Final_test.h"
+#define GRTINTERFACE                   0
+#include "Final_test.h"
+#endif                                 /* RTW_HEADER_rtmodel_h_ */

### 2018-09-16 paper/drafts/data_for_paper/friday_night/Final_test_ert_rtw/rtwtypes.h

@@ -1,0 +1,42 @@
+/*
+ * rtwtypes.h
+ *
+ * Academic License - for use in teaching, academic research, and meeting
+ * course requirements at degree granting institutions only.  Not for
+ * government, commercial, or other organizational use.
+ *
+ * Code generation for model "Final_test".
+ *
+ * Model version              : 1.54
+ * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
+ * C source code generated on : Sat Sep 15 17:18:11 2018
+ *
+ * Target selection: ert.tlc
+ * Note: GRT includes extra infrastructure and instrumentation for prototyping
+ * Embedded hardware selection: ARM Compatible->ARM Cortex
+ * Code generation objectives: Unspecified
+ * Validation result: Not run
+ */
+
+#ifndef RTWTYPES_H
+#define RTWTYPES_H
+#include "tmwtypes.h"
+#include "simstruc_types.h"
+#ifndef POINTER_T
+# define POINTER_T
+
+typedef void * pointer_T;
+
+#endif
+
+/* Logical type definitions */
+#if (!defined(__cplusplus))
+#  ifndef false
+#   define false                       (0U)
+#  endif
+
+#  ifndef true
+#   define true                        (1U)
+#  endif
+#endif
+#endif                                 /* RTWTYPES_H */

### 2018-09-16 paper/drafts/data_for_paper/tstand_data.m

@@ -1,0 +1,10 @@
+wind= csvread("last_tests/wind.csv",1,0);
+%  curr_testtorq = pt;
+[r,c] = find(wind(:,10) == 0);
+wind(r,:) = [];
+
+% [r,c] = find(curr_testtorq(:,9) == 0);
+% 
+% curr_testtorq(r,:) = [];
+% 
+clear r c

### 2018-09-16 paper/drafts/IEEE_VERSION.tex
bara look at IEEE_VERSION

--- 2018-09-15 paper/drafts/draft_final.tex
@@
 \documentclass[conference]{IEEEtran}
+\IEEEoverridecommandlockouts
+% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
+\usepackage{cite}
 \usepackage{amsmath,amssymb,amsfonts}
@@
 \usepackage{graphicx}
-\graphicspath{images}
 \usepackage{textcomp}
@@
 \begin{document}
-\title{Paper Title*\\
-	{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
-		should not be used}
-	\thanks{Identify applicable funding agency here. If none, delete this.}
+
+\title{Real-time Thrust Estimation and Regulation for Multirotor Aerial Vehicle\\
+{}
+\thanks{}
 }
+
 \author{\IEEEauthorblockN{1\textsuperscript{st} Adithya Ravishankara}
@@
 \and
-	\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
+\IEEEauthorblockN{2\textsuperscript{nd} Bara Emran}
 \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
@@
 \and
-	\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
+\IEEEauthorblockN{3\textsuperscript{rd} Sherman}
 \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
@@
 email address}
+\and
+\IEEEauthorblockN{4\textsuperscript{th} Homayoun Najjaran}
+\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
+\textit{name of organization (of Aff.)}\\
+City, Country \\
+email address}
+
 }
-	\section{Intro}
-	\subsection{Intro to mav and control system architecture}
-	Multirotor Aerial Vehicles (MAV), specifically quadrotors, have become quite commonplace in many industries ranging from filmography to racing to even military operations.
+
+\maketitle
+
+\begin{abstract}
+In this paper, we present a real-time approach to sense and regulate the thrust produced by rotors with fixed-pitch blade commonly used on multirotor aerial vehicles (MAV).
+The proposed schemes consist of integrating a wind sensor mounted onboard to measure the wind speed generated by the rotor directly.
+The wind measurement is then used with a simple control system and effective estimation algorithms to perform a precise controlling of the rotor thrust in real time.
+This integration significantly improves the disturbance rejection and fault estimation of the thrust and rotor, respectively.
+Specifically, a direct regulation of the thrust will improve the MAV systems performance while performing aggressive maneuvers or when subjected to external disturbances.
+Moreover, this approach can be employed to estimate the effective loss of a rotor for fault-tolerant control systems.
+The features of the proposed approach are demonstrated using a testbed and compared to a classical electrical speed control.
+Different experiments were performed to validate the efficiency of the proposed approach in maintaining the thrust in the presence of a wind gust and rotor efficiency loss.
+\end{abstract}
+
+\begin{IEEEkeywords}
+Sensor,Control,Kalman,Quadrotor
+\end{IEEEkeywords}
+
+\section{Introduction}
+Unmanned aerial vehicles (UAV), especially multirotor, have become quite commonplace in many industries ranging from inspection, racing to military applications \cite{bara}, \cite{Mathe}.
 Over the past decade, there has been an incredible amount of research and advancement within this field leading to its proliferation and allowing for the technology to become more accessible.
-One of the major areas of research regarding MAV's is the control system that directs the motor-rotor system.
-The control mechanism ranges in complexity from the common motor-rotor control, to a more complex system that takes into consideration parameters such as thrust or torque.
-The control of the motor-rotor has to account for multiple different external and internal factors, from the ambient wind speed, the rotation speed of the propeller (RPM), the pitch of the propeller, and for more complex controllers, the internal loops of the Electronic Speed Controller (ESC) or Flight Controller (FC).
-\\
-	In general, there are two different types of control loops; open and closed.
-Open control loops are what the majority of MAV control systems are.
-There is an FC, that sends a value to the ESC that applies a particular voltage to the motor based on previously calibrated settings.
-In this method, the final result of the motor spinning is unknown to the flight controller.
-Therefore given any disturbances, there will be large variances in the response of the overall system.
-In response to these systems there are smarter, closed loop control.
-This is the type of control we will focus on.
-Closed loop systems provide a certain way to measure the output of the rotor based on the input from the FC.
-This allows for a smarter, more robust system and greater control of the output.
-\\
-	\subsection{Intro to the problem}
-	The main problem we address in this paper is determining a type of sensor that can accurately and efficiently measure the output of the propellers in a meaningful way such that a closed control loop can be devised.
-	\subsection{Lit review}
-	There has been an enormous strive to develop methods to obtain a closed loop control system for MAV's.
-The methods range from estimation to sensing based on different vectors.
-The majority of the estimation based controls rely on the voltage or current draw by the motors.
-Mahoney et al \cite{mahoney1} devised such a system which estimates the thrust using a for loop based calculation of the thrust.
-This system while it allows for a valid estimation of the thrust, it is a complex system that requires relatively heavy computation and therefore is not feasible.
-As well their system requires heavy calibration and would not be easily transferable between systems.
-Similarly Awan et al \cite{awan} developed an adaptive observer based thrust estimation system.
-This method allowed for the MAV to maintain a hover with higher precision compared to previous methods involving thrust estimation.
-The main issue along this method is that their paper only accounts for hover not flight, as well their models were based around a linearized system and any nonlinear disturbances would cause errors in their system.
-In contrast Sydney et al \cite{sydney} developed a highly complex system where they modeled the entire system, both linear and nonlinear.
-By doing so their
+One of the major areas of research regarding UAV is the control system that directs the motor-rotor system.
+The control mechanism ranges in complexity from the common motor-rotor control to a more complex system that takes into consideration parameters such as thrust or torque.
+The control of the motor-rotor has to account for different external and internal factors, such as the ambient wind speed, the rotation speed of the propeller (RPM), the pitch of the propeller and the internal loops of the Electronic Speed Controller (ESC).
+Typically, rotor control systems in UAV are operated in open control loops.
+That is, the flight controller (FC) sends the desired speed value to the ESC that applies a particular voltage to the motor based on previously calibrated settings.
+The ESC uses the feedback signals of the rotor’s current and voltage to maintain its desired speed.
+In this method, however, the thrust generated by the propeller spinning is unknown to the FC.
+Recently, advanced FC employs static aerodynamic models relating rotor speed to estimate and control the generated thrust.
+Usually, these models are obtained after intensive experiments performed in static-free air environment to detrain the motor’s and propeller’s characteristics.
+However, when the system is subjected to a disturbance, these models become inaccurate.
+These external disturbances could accrue due to wind or when the vehicle is performing an agile maneuver.
+Thus, the lack of a direct measurement of the actual thrust is attracting the interest of the robot community recently.
+In this paper, we focus on determining a type of sensor that can efficiently measure the generated thrust of a propeller to use it for controlling the UAV.
+This allows for a smarter and more robust control system.
 
-	Mahoney et al (2017) have developed an algorithm which bases the control system around an estimation of the thrust from a propeller based on the voltage and current given to the motor by the ESC.
+There has been an enormous strive to develop methods to obtain a closed loop control system for UAVs.
+The methods range from thrust modeling to estimation using different sensors.
+The majority of the estimation-based controls rely on the voltage or current drawn by the motors.
+Awan et.
+al.
+\cite{awan} developed an adaptive observer-based thrust estimation system.
+This method allowed the MAV to maintain a hover with higher precision compared to previous methods involving thrust estimation.
+However, their proposed structure only accounts for hovering condition and the models were based around a linearized system.
+As a result, the system was highly violable for disturbances.
+This was accounted in Sydney et.
+al.
+\cite{sydney}, where they have proposed a highly complex estimation system and considered the nonlinear model of the system.
+Similarly, Mahoney et.
+al.
+\cite{mahoney1} devised a system which estimates the thrust using an iterative based calculation.
+This system while it allows for a valid estimation of the thrust, it is relatively complex and requires heavy computation.
+Letter in Mahony (2017), they have improved the estimation algorithm using the feedback signal of the voltage and current given to the motor by the ESC.
 Their system works to maintain a thrust given some disturbance.
-From looking over their algorithm, they have a system which runs through a for loop before detecting an appropriate response to extraneous forces.
-This system while it allows for a valid estimation of the thrust, it is a complex system that requires relatively heavy computation and therefore is not feasible.
-As well this method of thrust based control requires a significant amount of calibration for both the propellers and
-	Real-Time Wind Speed Estimation and Compensation for Improved Flight
-	Streit developed a control system to compensate for wind disturbances using a pitot-tube sensor coupled with the GPS sensor along with an accompanying estimation algorithm.
+Still, their system runs through an iterative loop before detecting an appropriate response to extraneous forces.
+This system while it allows for a robust estimation of the thrust, it is still a complex system.
+As well their method requires a significant amount of calibration for both the propellers and rotors which makes it harder to employ in different systems.
+Streit \cite{str} developed a control system to compensate for wind disturbances using a pitot-tube sensor along with an accompanying estimation algorithm.
 While this seems similar to the Yeo et al paper, there are some major differences.
-Streit has only one pitot sensor onboard the UAV which is uni-directional and therefore only applies to forward motion.
-As well the pitot-tube is made of brass and therefore not feasible for all smaller UAV's as it will be too heavy.
-	Onboard Flow Sensing for Downwash Detection and Avoidance with a Small Quadrotor Helicopter
-	Yeo et al have developed a system similar to our proposed idea by fabricating pitot tubes to sit below each propeller and measure the rotor downwash and compare them to the estimated expected wind speed.
-Their system is ultimately used to localize external noise from other UAV's and therefore an exceedingly accurate measurement is not as important.
-While the sensor can accurately measure wind speed accurately during vertical motion, there is significant divergence from the ground speed measurement during lateral movement.
+Streit has only one pitot sensor onboard the UAV which is unidirectional and therefore only applies to forward motion.
+As well the pitot-tube is made of brass and therefore not feasible for all smaller UAV’s as it will be too heavy.
+Yeo et al have used fabricated pitot tubes placed below each propeller to measure the rotor downwash and compare them to the estimated expected wind speed.
+Their system is ultimately used to localize external noise from other UAV’s and therefore an exceedingly accurate measurement is not as important.
+While the sensor can accurately measure wind speed accurately during vertical motion, there is a significant divergence from the ground speed measurement during lateral movement.
 As well there is a very limited range of speeds that are available for measurement from the probe.
-	\subsection{Scope and application}
-	The scope of this paper is to introduce a hot wire anemometer, or wind sensor, as viable option for an external sensor and develop the relationship between the downwash rotor wind speed and the thrust vector of the propeller.
-With the addition of the sensor, we generate a control system based around the measurements of the wind sensor, using a kalman filter and a simple PI controller.
-This allows the system to be more robust towards external disturbances such as wind gusts and also more tolerant to internal errors.
-One other application of the wind sensor is to have an onboard fault detection system, which is in contrast to the majority of prior research, where the fault detection is more of an estimation.
-The applications for the sensor we introduce can be in any field where MAV's are prevalent, such as filmography, racing, and any other area that requires, agile and reliable control.
+
 \section{2}
@@
 This is the reasoning behind why as winds buffet a drone mid-flight, the drone's thrust vector tends to drop. Hence we can measure this change in thrust and correct for it.
-	\subsection{Kalman Math}
-	\subsection{2.3}
-	\subsection{2.4}
+\subsection{Adaptive Fuzzy Kalman Filter }
+
+Accurate a priori information of the measurement and process noise statistical matrices of the state estimator is needed to avoid the divergence of the filter [3], [4].
+To resolve the problem of having imperfect a priori information, adapting R and/or Q matrices was introduced using several adaptive estimation techniques [5]–[7].
+Among these, the Innovative-based Adaptive Estimation (IAE) and Multiple Model Adaptive Estimation (MMAE) are commonly utilized to adapt the Kalman filter.
+Incorporating the rules of fuzzy logic to adjust the variances of these matrices has been studied in several research works.
+The Adaptive Fuzzy Kalman Filter q (AFKF) has been designed to improve the performance of the conventional filter in rejecting the measurement noise and estimating the navigational states accurately [8], [9].
+The recurrent adjustment process of the variances of the statistical matrices Rk is designed based on an IAE approach.
+This approach is based on a covariance-matching algorithm which examines the degree of the mismatch DoM between the actual covariance $v_{K+1}$ of the residual with its theoretical value $S_{K+1}$.
+\begin{equation}
+DoM = S_{k+1} - C_{k+1}
+\label{dom}
+\end{equation}
+After calculating DoM, a Fuzzy Inference System (FIS) has been tuned to compute the adjustment of the measurement noise matrix $R_{k+1}$ and update the matrix at each cycle of state estimation.
+\begin{equation}
+R_{k+1} = R_k +\delta R_{K+1}
+\label{rk1}
+\end{equation} 
 	\section{3}
-	\subsection{Thrust stand}
+\subsection{RCBenchmark Thrust Stand Dynamometer}
 %THE THRUST STAND
@@
 This is more than adequate for the purposes of modeling the thrust response of the propeller to various stimuli.
-	\subsection{Wind Sensor Intro}
+\subsection{Modern Device Wind Sensor}
 The wind sensor we have chosen to use is the "Modern Device- Wind Sensor Rev.
@@
 This system allows us to measure the wind speed that is resultant of the propeller.
-	\subsection{Wind Sensor Proof}
 To understand the limitations of the wind sensor, we performed a series of tests to characterize the sensor.
@@
 \subsection{The tests}
+Figures \ref{akf1},\ref{akf2} demonstrate the thrust estimation using the conventional and the adaptive fuzzy state estimation techniques.
+As can be seen, the proposed AFKF has exhibited better performance in terms of rejecting the noise associated with the measurement compared to the classical KF.
+Figures \ref{akf1},\ref{akf2} presents the estimation errors of the position states.
+The AFKF shows lower magnitudes of estimation error compared to these of the KF.
+
 To ensure the viability of our algorithm and if it would respond to external stimuli the way we expected, we performed several tests that caused significant errors in the propeller's response.
@@
 This would be akin to horizontal crosswind flow across the propeller.
-	\begin{figure}
-		\label{content...}
-	\end{figure}
+
 Based on the results of fig \ref{wind_disturb}, the control algorithm can determine the appropriate correction for such a disturbance through
-	\begin{figure}
-		content...
-	\end{figure}
+
 \subsection{Shortcomings and limitations}
@@
 \subsection{}
-	\subsection{5.4}
-		\begin{figure}[b]
-		\includegraphics[width=\textwidth / 2]{images/block_diagram.png}
+	\begin{figure}[htbp]
+	\includegraphics[width=10cm]{images/block_diagram.png}
 	\caption{Block Diagram}
@@
 	\end{figure}
-	\begin{thebibliography}{99}
+	\begin{figure}[htbp]
+	\includegraphics[width=10cm]{images/figure_1/area_heatmap.jpg}
+	\caption{Block Diagram}
+	\label{area}
+	\end{figure}
+	\begin{figure}[htbp]
+	\includegraphics[width = 7cm]{images/figure_1/dist_heatmap.jpg}
+	\caption{Block Diagram}
+	\label{dist}
+\end{figure}
+	\begin{figure}[htbp]
+	\includegraphics[width=10cm]{images/figure_1/orientation.jpg}
+	\caption{Block Diagram}
+	\label{orientation}
+\end{figure}
+	\begin{figure}[htbp]
+	\includegraphics[width=10cm]{images/figure_1/range.jpg}
+	\caption{range}
+	\label{range}
+\end{figure}
+	\begin{figure}[htbp]
+	\includegraphics[width=10cm]{images/figure_1/response.jpg}
+	\caption{response}
+	\label{response}
+\end{figure}
+%	\begin{figure}[b]
+%	\includegraphics[width=\textwidth / 2]{images/block_diagram.png}
+%	\caption{Block Diagram}
+%	\label{block_diagram}
+%\end{figure}
+%	\begin{figure}[b]
+%	\includegraphics[width=\textwidth / 2]{images/block_diagram.png}
+%	\caption{Block Diagram}
+%	\label{block_diagram}
+%\end{figure}
+%	\begin{figure}[b]
+%	\includegraphics[width=\textwidth / 2]{images/block_diagram.png}
+%	\caption{Block Diagram}
+%	\label{block_diagram}
+%\end{figure}
+
+\subsection{5.4}
+\begin{thebibliography}{00}
+\bibitem{bara}B. J. Emran, D. D. Tannant, and H. Najjaran, “Low-altitude aerial methane concentration mapping,” Remote Sens., vol. 9, no. 8, 2017.
+\bibitem{Mathe} K.
+Máthé and L.
+Buşoniu, “Vision and Control for UAVs: A Survey of General Methods andof Inexpensive Platforms for Infrastructure Inspection,” Sensors, vol.
+15, no.
+7, pp.
+14887–14916, 2015.
+\bibitem{akf} A.H.Mohamed and K. P. Schwarz, “Adaptive Kalman Filtering for INS/GPS,” J. Geod., vol. 73, no. 4, pp. 193–203, 1999.
+\bibitem{fuzzy} P. J. Escamilla-Ambrosio and N. Mort, “Development of a fuzzy logic-based adaptive Kalman filter,” in Control Conference (ECC), 2001 European, 2001, pp. 1768–1773.
+\bibitem{sebesta} K. D. Sebesta and N. Boizot, “A real-time adaptive high-gain EKF, applied to a quadcopter inertial navigation system,” IEEE Trans. Ind. Electron., vol. 61, no. 1, pp. 495–503, 2014.
+\bibitem{Manki} A.
+Makni, H.
+Fourati, and A.
+Y.
+Kibangou, “Energy-Aware Adaptive Attitude Estimation under External Acceleration for Pedestrian Navigation,” IEEE/ASME Trans.
+Mechatronics, vol.
+21, no.
+3, pp.
+1366–1375, 2016.
+\bibitem{Lin} C. M. Lin and C. S. Hsueh, “Adaptive EKF-CMAC-based multisensor data fusion for maneuvering target,” IEEE Trans. Instrum. Meas., vol. 62, no. 7, pp. 2058–2066, 2013.
+\bibitem{Sharman} M.
+K.
+Al-Sharman, M.
+A.
+Jaradat, and M.
+F.
+Abdel-Hafez, “Intelligent attitude and flapping angles estimation of flybarless helicopters under near-hover conditions,” J.
+Franklin Inst., 2018.
+\bibitem{Emran} M.
+K.
+Al-Sharman, B.
+J.
+Emran, M.
+A.
+Jaradat, H.
+Najjaran, R.
+Al-Husari, and Y.
+Zweiri, “Precision landing using an adaptive fuzzy multi-sensor data fusion architecture,” Appl.
+Soft Comput.
+J., vol.
+69, 2018.
 		\bibitem{mahoney1} Mahoney 2012
@@
 3609-3616.
-		doi: 10.1109/CDC.2013.6760438
-
 \end{thebibliography}
-
 \end{document}

### 2018-09-16 paper/drafts/draft_final.tex
Firdya night data. I dont wanna look at a computer anymore
bara look at IEEE_VERSION

@@
 	\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
-	\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
+	\IEEEauthorblockA{\textit{dept. namefdsfsdf of organization (of Aff.)} \\
 		\textit{name of organization (of Aff.)}\\
@@
 	\subsection{Kalman Math}
-	\subsection{2.3}
-	\subsection{2.4}
+	Adaptive Fuzzy Kalman Filter 
+	Accurate a priori information of the measurement and process noise statistical matrices of the state estimator is needed to avoid the divergence of the filter [3], [4].
+To resolve the problem of having imperfect a priori information, adapting R and/or Q matrices was introduced using several adaptive estimation techniques [5]–[7].
+Among these, the Innovative-based Adaptive Estimation (IAE) and Multiple Model Adaptive Estimation (MMAE) are commonly utilized to adapt the Kalman filter.
+Incorporating the rules of fuzzy logic to adjust the variances of these matrices has been studied in several research works.
+The Adaptive Fuzzy Kalman Filter q (AFKF) has been designed to improve the performance of the conventional filter in rejecting the measurement noise and estimating the navigational states accurately [8], [9].
+	The recurrent adjustment process of the variances of the statistical matrices Rk is designed based on an IAE approach.
+This approach is based on a covariance-matching algorithm which examines the degree of the mismatch DoM between the actual covariance $v_{K+1}$ of the residual with its theoretical value $S_{K+1}$.
+	\begin{equation}
+	DoM = S_{k+1} - C_{k+1}
+	\label{dom}
+	\end{equation}
+	After calculating DoM, a Fuzzy Inference System (FIS) has been tuned to compute the adjustment of the measurement noise matrix $R_{k+1}$ and update the matrix at each cycle of state estimation.
+	\begin{equation}
+	R_{k+1} = R_k +\delta R_{K+1}
+	\label{rk1}
+	\end{equation}
+
 	\section{3}
@@
 	\subsection{The tests}
+	Figures \ref{akf1},\ref{akf2} demonstrate the thrust estimation using the conventional and the adaptive fuzzy state estimation techniques.
+As can be seen, the proposed AFKF has exhibited better performance in terms of rejecting the noise associated with the measurement compared to the classical KF.
+Figures \ref{akf1},\ref{akf2} presents the estimation errors of the position states.
+The AFKF shows lower magnitudes of estimation error compared to these of the KF.
+
 	To ensure the viability of our algorithm and if it would respond to external stimuli the way we expected, we performed several tests that caused significant errors in the propeller's response.
@@
 3609-3616.
-		doi: 10.1109/CDC.2013.6760438
 

### 2018-09-16 paper/Matlab_code/plotting_figures.m

@@ -48,8 +48,10 @@ plot(pwm_r_comparison(:,1),pwm_r_comparison(:,7))
 
 legend("Desired","Actual Thrust","Kalman Estimation")
 
-figure(4)
-title("wind");
+figure(2)
 hold on
-plot
-
+plot(wind(:,1),wind(:,8),'k')
+plot(wind(:,1),wind(:,7)+.15,'r')
+plot(wind_control(1959:end,1),wind_control(1959:end,7),'g')
+legend("Desired Thrust","No Control","Control")
+xlabel("Time (s)"); ylabel("Thrust (N)"); title("Response of Control System to Wind Disturbance");

### 2018-09-16 paper/drafts/data_for_paper/Final_test_ert_rtw/Final_test.c

@@ -7,9 +7,9 @@
  *
  * Code generation for model "Final_test".
  *
- * Model version              : 1.54
+ * Model version              : 1.55
  * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
- * C source code generated on : Sat Sep 15 17:33:20 2018
+ * C source code generated on : Sat Sep 15 19:14:33 2018
  *
  * Target selection: ert.tlc
  * Note: GRT includes extra infrastructure and instrumentation for prototyping
@@ -140,8 +140,6 @@ static codertarget_arduinobase_int_f_T *arduino_PWMOutput_arduino_PWMOu
   (codertarget_arduinobase_int_f_T *obj)
 {
   codertarget_arduinobase_int_f_T *b_obj;
-
-  /* Start for MATLABSystem: '<S2>/PWM1' */
   obj->isInitialized = 0;
   b_obj = obj;
   obj->Hw.AvailablePwmPinNames.f1 = '2';
@@ -213,15 +211,12 @@ real_T rt_powd_snf(real_T u0, real_T u1)
 static void SystemProp_matlabCodegenSetAn_f(dsp_simulink_MovingAverage_f_T *obj,
   boolean_T value)
 {
-  /* Start for MATLABSystem: '<Root>/Kalman ' */
   obj->matlabCodegenIsDeleted = value;
 }
 
 static void Final_test_SystemCore_release_f(dsp_simulink_MovingAverage_f_T *obj)
 {
   dsp_private_SlidingWindowAv_f_T *obj_0;
-
-  /* Start for MATLABSystem: '<Root>/Kalman ' */
   if ((obj->isInitialized == 1) && obj->isSetupComplete) {
     obj_0 = obj->pStatistic;
     if (obj_0->isInitialized == 1) {
@@ -230,39 +225,30 @@ static void Final_test_SystemCore_release_f(dsp_simulink_MovingAverage_f_T *obj)
 
     obj->NumChannels = -1;
   }
-
-  /* End of Start for MATLABSystem: '<Root>/Kalman ' */
 }
 
 static void Final_test_SystemCore_delete_f(dsp_simulink_MovingAverage_f_T *obj)
 {
-  /* Start for MATLABSystem: '<Root>/Kalman ' */
   Final_test_SystemCore_release_f(obj);
 }
 
[…]

### 2018-09-16 paper/drafts/data_for_paper/Final_test_ert_rtw/Final_test.h

@@ -7,9 +7,9 @@
  *
  * Code generation for model "Final_test".
  *
- * Model version              : 1.54
+ * Model version              : 1.55
  * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
- * C source code generated on : Sat Sep 15 17:33:20 2018
+ * C source code generated on : Sat Sep 15 19:14:33 2018
  *
  * Target selection: ert.tlc
  * Note: GRT includes extra infrastructure and instrumentation for prototyping
@@ -235,7 +235,7 @@ typedef struct {
     void *TimePtr;
     void *DataPtr;
     void *RSimInfoPtr;
-  } FromWs_PWORK_i;                    /* '<S5>/FromWs' */
+  } FromWs_PWORK_a;                    /* '<S8>/FromWs' */
 
   struct {
     void *LoggedData;
@@ -279,7 +279,7 @@ typedef struct {
 
   struct {
     int_T PrevIndex;
-  } FromWs_IWORK_d;                    /* '<S5>/FromWs' */
+  } FromWs_IWORK_c;                    /* '<S8>/FromWs' */
 
   int8_T Integrator_PrevResetState;    /* '<S22>/Integrator' */
   int8_T Integrator_PrevResetState_i;  /* '<S27>/Integrator' */
@@ -356,7 +356,7 @@ struct P_Final_test_T_ {
   real_T AnalogInput_SampleTime;       /* Expression: 0.01
                                         * Referenced by: '<S4>/Analog Input'
                                         */
-  real_T Constant2_Value;              /* Expression: 1
+  real_T Constant2_Value;              /* Expression: .95
                                         * Referenced by: '<Root>/Constant2'
                                         */
   real_T Memory_InitialCondition;      /* Expression: 0
@@ -413,7 +413,7 @@ struct P_Final_test_T_ {
   real_T Constant_Value_j;             /* Expression: 1
                                         * Referenced by: '<Root>/Constant'
                                         */
-  real_T ManualPWM_Gain;               /* Expression: 0
+  real_T ManualPWM_Gain;               /* Expression: 11.216335042318
                                         * Referenced by: '<Root>/Manual PWM'
                                         */
   real_T Switch2_Threshold;            /* Expression: 0
@@ -582,9 +582,9 @@ extern RT_MODEL_Final_test_T *const Final_test_M;
  * Block '<S17>/b' : Unused code path elimination
[…]

### 2018-09-16 paper/drafts/data_for_paper/Final_test_ert_rtw/Final_test_data.c

@@ -7,9 +7,9 @@
  *
  * Code generation for model "Final_test".
  *
- * Model version              : 1.54
+ * Model version              : 1.55
  * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
- * C source code generated on : Sat Sep 15 17:33:20 2018
+ * C source code generated on : Sat Sep 15 19:14:33 2018
  *
  * Target selection: ert.tlc
  * Note: GRT includes extra infrastructure and instrumentation for prototyping
@@ -73,10 +73,10 @@ P_Final_test_T Final_test_P = {
    */
   0.01,
 
-  /* Expression: 1
+  /* Expression: .95
    * Referenced by: '<Root>/Constant2'
    */
-  1.0,
+  0.95,
 
   /* Expression: 0
    * Referenced by: '<S1>/Memory'
@@ -168,10 +168,10 @@ P_Final_test_T Final_test_P = {
    */
   1.0,
 
-  /* Expression: 0
+  /* Expression: 11.216335042318
    * Referenced by: '<Root>/Manual PWM'
    */
-  0.0,
+  11.216335042318,
 
   /* Expression: 0
    * Referenced by: '<S2>/Switch2'
@@ -291,7 +291,7 @@ P_Final_test_T Final_test_P = {
   /* Computed Parameter: ManualSwitch2_CurrentSetting
    * Referenced by: '<Root>/Manual Switch2'
    */
-  1U,
+  0U,
 
   /* Computed Parameter: ManualSwitch1_CurrentSetting
    * Referenced by: '<Root>/Manual Switch1'

### 2018-09-16 paper/drafts/data_for_paper/Final_test_ert_rtw/Final_test_targ_data_map.m

@@ -566,7 +566,7 @@
 	  section.data(1).logicalSrcIdx = 15;
 	  section.data(1).dtTransOffset = 0;
 	
-	  ;% Final_test_DW.FromWs_PWORK_i.TimePtr
+	  ;% Final_test_DW.FromWs_PWORK_a.TimePtr
 	  section.data(2).logicalSrcIdx = 16;
 	  section.data(2).dtTransOffset = 1;
 	
@@ -617,7 +617,7 @@
 	  section.data(1).logicalSrcIdx = 26;
 	  section.data(1).dtTransOffset = 0;
 	
-	  ;% Final_test_DW.FromWs_IWORK_d.PrevIndex
+	  ;% Final_test_DW.FromWs_IWORK_c.PrevIndex
 	  section.data(2).logicalSrcIdx = 27;
 	  section.data(2).dtTransOffset = 1;
 	
@@ -701,8 +701,8 @@
   ;%
 
 
-  targMap.checksum0 = 3966038292;
-  targMap.checksum1 = 4260020833;
-  targMap.checksum2 = 1976021332;
-  targMap.checksum3 = 482972058;
+  targMap.checksum0 = 1871559061;
+  targMap.checksum1 = 3246618748;
+  targMap.checksum2 = 117018499;
+  targMap.checksum3 = 3821278749;
 

### 2018-09-16 paper/drafts/data_for_paper/Final_test_ert_rtw/html/define.js

@@ -12,23 +12,23 @@ this.def["Final_test_M_"] = {file: "Final_test_c.html",line:35,type:"var"};
 this.def["Final_test_M"] = {file: "Final_test_c.html",line:36,type:"var"};
 this.def["rt_ertODEUpdateContinuousStates"] = {file: "Final_test_c.html",line:62,type:"fcn"};
 this.def["arduino_PWMOutput_arduino_PWMOu"] = {file: "Final_test_c.html",line:139,type:"fcn"};
-this.def["rt_powd_snf"] = {file: "Final_test_c.html",line:167,type:"fcn"};
-this.def["SystemProp_matlabCodegenSetAn_f"] = {file: "Final_test_c.html",line:213,type:"fcn"};
-this.def["Final_test_SystemCore_release_f"] = {file: "Final_test_c.html",line:220,type:"fcn"};
-this.def["Final_test_SystemCore_delete_f"] = {file: "Final_test_c.html",line:237,type:"fcn"};
-this.def["matlabCodegenHandle_matlabCod_f"] = {file: "Final_test_c.html",line:243,type:"fcn"};
-this.def["SystemProp_matlabCodegenSetAnyP"] = {file: "Final_test_c.html",line:254,type:"fcn"};
-this.def["Final_test_SystemCore_release"] = {file: "Final_test_c.html",line:261,type:"fcn"};
-this.def["Final_test_SystemCore_delete"] = {file: "Final_test_c.html",line:278,type:"fcn"};
-this.def["matlabCodegenHandle_matlabCodeg"] = {file: "Final_test_c.html",line:284,type:"fcn"};
-this.def["SystemProp_matlabCodegenSet_fdg"] = {file: "Final_test_c.html",line:295,type:"fcn"};
-this.def["matlabCodegenHandle_matlabC_fdg"] = {file: "Final_test_c.html",line:302,type:"fcn"};
-this.def["SystemProp_matlabCodegenSetA_fd"] = {file: "Final_test_c.html",line:312,type:"fcn"};
-this.def["matlabCodegenHandle_matlabCo_fd"] = {file: "Final_test_c.html",line:319,type:"fcn"};
-this.def["Final_test_step"] = {file: "Final_test_c.html",line:330,type:"fcn"};
-this.def["Final_test_derivatives"] = {file: "Final_test_c.html",line:1073,type:"fcn"};
-this.def["Final_test_initialize"] = {file: "Final_test_c.html",line:1092,type:"fcn"};
[…]

### 2018-09-16 paper/drafts/data_for_paper/Final_test_ert_rtw/rtGetInf.c

@@ -7,9 +7,9 @@
  *
  * Code generation for model "Final_test".
  *
- * Model version              : 1.54
+ * Model version              : 1.55
  * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
- * C source code generated on : Sat Sep 15 17:33:20 2018
+ * C source code generated on : Sat Sep 15 19:14:33 2018
  *
  * Target selection: ert.tlc
  * Note: GRT includes extra infrastructure and instrumentation for prototyping

### 2018-09-16 paper/drafts/data_for_paper/Final_test_ert_rtw/rtmodel.h

@@ -7,9 +7,9 @@
  *
  * Code generation for model "Final_test".
  *
- * Model version              : 1.54
+ * Model version              : 1.55
  * Simulink Coder version : 8.14 (R2018a) 06-Feb-2018
- * C source code generated on : Sat Sep 15 17:33:20 2018
+ * C source code generated on : Sat Sep 15 19:14:33 2018
  *
  * Target selection: ert.tlc
  * Note: GRT includes extra infrastructure and instrumentation for prototyping
@@ -23,7 +23,7 @@
  * Code generation for Simulink model "Final_test".
  *
  * Simulink Coder version                : 8.14 (R2018a) 06-Feb-2018
- * C source code generated on : Sat Sep 15 17:33:20 2018
+ * C source code generated on : Sat Sep 15 19:14:33 2018
  *
  * Note that the generated code is not dependent on this header file.
  * The file is used in cojuction with the automatic build procedure.

### 2018-09-16 paper/drafts/data_for_paper/tstand_data.m

@@ -1,7 +1,7 @@
-wind= csvread("last_tests/wind.csv",1,0);
+pwm_reduc_compT= csvread("friday_night/pwm_r_comparison.csv",1,0);
 %  curr_testtorq = pt;
-[r,c] = find(wind(:,10) == 0);
-wind(r,:) = [];
+[r,c] = find(pwm_reduc_compT(:,10) == 0);
+pwm_reduc_compT(r,:) = [];
 
 % [r,c] = find(curr_testtorq(:,9) == 0);
 % 

### 2018-09-16 paper/drafts/IEEE_VERSION.tex
now you can pull
check this

@@
 
-\author{\IEEEauthorblockN{1\textsuperscript{st} Adithya Ravishankara}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address}
+\author{\IEEEauthorblockN{Adithya Ravishankara*}
+\IEEEauthorblockA{adiravishankara@gmail.com}
 \and
-\IEEEauthorblockN{2\textsuperscript{nd} Bara Emran}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address}
+\IEEEauthorblockN{Bara Emran*}
+\IEEEauthorblockA{bara.emran@gmail.com}
 \and
-\IEEEauthorblockN{3\textsuperscript{rd} Sherman}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address}
+\IEEEauthorblockN{Sherman**}
+\IEEEauthorblockA{Sherman@sherman.com}
 \and
-\IEEEauthorblockN{4\textsuperscript{th} Homayoun Najjaran}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address}
-
+\IEEEauthorblockN{Homayoun Najjaran*}
+\IEEEauthorblockA{homayoun.najjaran@ubc.ca}
+\and
+*University of British Columbia, Okanagan Campus\\
+**University of Waterloo
 }
@@
 As well their method requires a significant amount of calibration for both the propellers and rotors which makes it harder to employ in different systems.
-Streit \cite{str} developed a control system to compensate for wind disturbances using a pitot-tube sensor along with an accompanying estimation algorithm.
+Streit \cite{streit} developed a control system to compensate for wind disturbances using a pitot-tube sensor along with an accompanying estimation algorithm.
 While this seems similar to the Yeo et al paper, there are some major differences.
-Streit has only one pitot sensor onboard the UAV which is unidirectional and therefore only applies to forward motion.
+Streit \cite{streit} has only one pitot sensor onboard the UAV which is unidirectional and therefore only applies to forward motion.
 As well the pitot-tube is made of brass and therefore not feasible for all smaller UAV’s as it will be too heavy.
@@
 As well there is a very limited range of speeds that are available for measurement from the probe.
+There are some works which have used strain guages and hall effect sensors or even torque measurements to obtain the thrust
 
@@
 \subsection{Wind sensor math/theory}
-We have to start by defining the three different velocities that apply to a propeller.\\
-\begin{eqnarray}
-\label{e1}
-v_x , v_y , v_z \\
-\label{e2}
-v^s_{x} , v^s_{y} , v^s_{z} \\
-\label{e3}
-v^i_{x} , v^i_{y} , v^i_{z}
-\end{eqnarray}
-Where \ref{e1} Is the velocity of the drone, the body frame velocity, \ref{e2} is the velocity of the wind approaching the propellers, the stream velocity, and \ref{e3} is the induced velocity of the propellers.\\
-Since we are doing only the static tests in this paper, we can disregard the horizontal components of the wind as well as the body frame velocities. Then we can state 
-\begin{eqnarray}
-\nonumber
-v_s = v^s_{z}\\
-\nonumber
-v_i = v^i_{z}
-\end{eqnarray}
+We have to start by defining the three different velocities that apply to a propeller.
+$v_x , v_y , v_z$ is the velocity of the drone, the body frame velocity, $v^s_{x} , v^s_{y} , v^s_{z}$ is the velocity of the wind approaching the propellers, the stream velocity, and $ v^i_{x} , v^i_{y} , v^i_{z}$ is the induced velocity of the propellers.\\
+Since we are doing only the static tests in this paper, we can disregard the horizontal components of the wind as well as the body frame velocities.
+Then we can state $v_s = v^s_{z}$ and $ v_i = v^i_{z} $.\\
 As well, since we have stationary system, the frame velocities can be ignored as well. What the wind sensor will notice is 
@@
 \begin{eqnarray}
-WS = \frac{(V - V_{z})*0.087288}{3.038517 * T_{c} ^{0.115157}} ^ {3.009364}
+WS = \frac{(V - V_{z})x0.087288}{3.038517 x T_{c} ^{0.115157}} ^ {3.009364}
 \label{wind_speed}
@@
 \label{fvm2}
-F_p= m*(v_{tot}-v{s}) 
+F_p= mx(v_{tot}-v{s}) 
 \label{fvm3}
@@
 \begin{eqnarray}	
-v_{i}\prime = v_{i}* \gamma\\
+v_{i}\prime = v_{i}x \gamma\\
 v_{tot}\prime = v_i\prime + v_s
@@
 Accurate a priori information of the measurement and process noise statistical matrices of the state estimator is needed to avoid the divergence of the filter [3], [4].
-To resolve the problem of having imperfect a priori information, adapting R and/or Q matrices was introduced using several adaptive estimation techniques [5]–[7].
+To resolve the problem of having imperfect a priori information, adapting R and/or Q matrices was introduced using several adaptive estimation techniques \cite{sebesta},\cite{Manki},\cite{Lin}.
 Among these, the Innovative-based Adaptive Estimation (IAE) and Multiple Model Adaptive Estimation (MMAE) are commonly utilized to adapt the Kalman filter.
 Incorporating the rules of fuzzy logic to adjust the variances of these matrices has been studied in several research works.
-The Adaptive Fuzzy Kalman Filter q (AFKF) has been designed to improve the performance of the conventional filter in rejecting the measurement noise and estimating the navigational states accurately [8], [9].
+The Adaptive Fuzzy Kalman Filter (AFKF) has been designed to improve the performance of the conventional filter in rejecting the measurement noise and estimating the navigational states accurately \cite{Sharman},\cite{Emran}.
 The recurrent adjustment process of the variances of the statistical matrices Rk is designed based on an IAE approach.
-This approach is based on a covariance-matching algorithm which examines the degree of the mismatch DoM between the actual covariance $v_{K+1}$ of the residual with its theoretical value $S_{K+1}$.
+This approach is based on a covariance-matching algorithm which examines the degree of the mismatch DoM between the actual covariance $v_{k+1}$ of the residual with its theoretical value $S_{k+1}$.
 \begin{equation}
@@
 \begin{equation}
-R_{k+1} = R_k +\delta R_{K+1}
+R_{k+1} = R_k +\delta R_{k+1}
 \label{rk1}
@@
 The first of which was to determine under which orientation the sensor observed the highest range of wind speeds.
-As seen in \ref{orient_test}, the orientation of placing the wind sensor normal to the direction of wind flow allowed for the highest range of measurement.
+As seen in \ref{orientation}, the orientation of placing the wind sensor normal to the direction of wind flow allowed for the highest range of measurement.
+	\begin{figure}[htbp]
+	\includegraphics[width=7cm]{images/figure_1/orientation.jpg}
+	\caption{Block Diagram}
+	\label{orientation}
+\end{figure}
 Next we performed a test to determine the feasible range of measurement.
-This was done by exposing the wind sensor to a step-signal test and a pulse signal test ranging from the minimal PWM value to approximately $50\%$ of the motor's max value, the results of which are in \ref{min_max}.
+This was done by exposing the wind sensor to a step-signal test and a pulse signal test ranging from the minimal PWM value to approximately $25\%$ of the motor's max value, the results of which are in \ref{range}.
 The PWM values in this case are based around the Simulink-Arduino Library PWM module.
@@
 While there is possibility for the wind sensor to measure higher wind speeds, there is a significant amount of noise even with the addition of a low-pass filter, hence we decided to limit the max speed of our experiment.
-Another factor that we deem is important to characterize is the speed of response to change of wind speed.
-We measured this by running the propeller at various different speeds, while tracking the thrust output on the testbed as our base measurement of response time and then comparing the response time to see the lag in response time.
-By doing this we found that there was a negligible lag time of less than $10 ms$, which is our resolution for each measurement.
+	\begin{figure}[htbp]
+	\includegraphics[width=7cm]{images/figure_1/range.jpg}
+	\caption{range}
+	\label{range}
+\end{figure}
+
+One other factor of a sensor that is important to determine is the measurement lag.
+This is the time it takes for the sensor to notice and measure a change in the value.
+To measure this vector we introduced a large change in RPM for the propeller and then measured the average time lag between when the thrust stand noticed the change and when the wind sensor noticed the change.
+This test resulted in a near 2 second lag in extreme changes.
+While this seems like a rather long delay, for smaller changes, the sensor can react much quicker.
+The results of this test are show in fig \ref{response}.
+	\begin{figure}[htbp]
+	\includegraphics[width=7cm]{images/figure_1/response.jpg}
+	\caption{response}
+	\label{response}
+\end{figure}
 Lastly we measured the location of the wind sensor in relation to the propellers.
 To do so we measured a semi-circle area behind the propeller to deem the location of highest wind sensitivity.
-Resulting in a map as seen in figure \ref{area}.
-By characterizing the wind sensor, we can ensure that it is in the optimal configuration for us to collect data.
+Resulting in a map as seen in figure \ref{area},\ref{dist}.
+This results in a location approximately 7 cm above the axis of the propeller and 5 cm behind the propeller.
+By characterizing the wind sensor, we can ensure that it is in the optimal configuration for the collection of data.
+	\begin{figure}[htbp]
+	\includegraphics[width=7cm]{images/figure_1/area_heatmap.jpg}
+	\caption{Block Diagram}
+	\label{area}
+\end{figure}
+\begin{figure}[htbp]
+	\includegraphics[width = 7cm]{images/figure_1/dist_heatmap.jpg}
+	\caption{Block Diagram}
+	\label{dist}
+\end{figure}
 \section{Results}
-\subsection{Experimental Setup- How we set up the kalman/Algorithm}
-
+\subsection{Control Loop Setup}
+	\begin{figure}[htbp]
+	\includegraphics[width=7cm]{images/Figure_2/Block_Diagram.jpg}
+	\caption{Block Diagram}
+	\label{block_diagram}
+\end{figure}
 We developed a control architecture as pictured in fig \ref{block_diagram} where there are two sources of measurement for the thrust value.
@@
 \begin{eqnarray}
-Thrust = 1.957*10^{-5}*PWM^4 \\
-- 7.476*10^{-4}*PWM^3 \nonumber\\ 
-+ 1.272*10^{-2}*PWM^2 \nonumber\\
-+ .01092*PWM - .01842 \nonumber
+Thrust = 1.957*10^{-5}xPWM^4 \\
+- 7.476*10^{-4}xPWM^3 \nonumber\\ 
++ 1.272*10^{-2}xPWM^2 \nonumber\\
++ .01092xPWM - .01842 \nonumber
 \label{pwm_poly}
@@
 Next this value is passed to a PI controller which generates the appropriate response for the error between desired and measured.
-\subsection{The tests}
+\subsection{Testing Performance}
 Figures \ref{akf1},\ref{akf2} demonstrate the thrust estimation using the conventional and the adaptive fuzzy state estimation techniques.
@@
 The AFKF shows lower magnitudes of estimation error compared to these of the KF.
+\begin{figure}[htbp]
+	\includegraphics[width=7cm]{images/akf1.jpg}
+	\caption{response}
+	\label{akf1}
+\end{figure}
+\begin{figure}[htbp]
+	\includegraphics[width=7cm]{images/akf2.jpg}
+	\caption{response}
+	\label{akf2}
+\end{figure}
 
 To ensure the viability of our algorithm and if it would respond to external stimuli the way we expected, we performed several tests that caused significant errors in the propeller's response.
-The first test that we ran was to measure the response of the kalman filter and ensure that our thrust calculation was accurate in relation to the testbed recorded thrust.
-As seen in fig \ref{kalman} the kalman filter, while noisy due to the wind variations in the wind sensor data, follows the thrust value from the testbed closely.
-This result gives us the confidence to setup the PI based on the kalman filter's value.
-To ensure the functionality of the controller we set up several faults and disturbances to test the response of the system.
-The first step was to create an external disturbance by placing another propeller and blowing wind perpendicular to the axis of the main propeller.
-This would be akin to horizontal crosswind flow across the propeller.
+The first test that we ran was to measure the response of the kalman filter and ensure that our thrust estimation was accurate with the actual thrust measured by the thrust stand.
+We ran this as a series with no error as seen in \ref{kalman}, an internal error of a PWM drop by $20\%$ as seen in \ref{pwm_reduc}, and lastly a wind disturbance which would decrease the thrust output of the propellers, even while maintaining a particular RPM as seen in \ref{wind_d}.
+\begin{figure}[htbp]
+	\includegraphics[width=7cm]{images/Figure_2/kalman.jpg}
+	\caption{response}
+	\label{kalman}
+\end{figure}
+\begin{figure}[htbp]
+	\includegraphics[width=7cm]{images/Figure_2/pwm_reduc.jpg}
+	\caption{response}
+	\label{pwm_reduc}
+\end{figure}
+\begin{figure}[htbp]
+	\includegraphics[width=7cm]{images/Figure_2/wind_d.jpg}
+	\caption{response}
+	\label{wind_d}
+\end{figure}
 
-Based on the results of fig \ref{wind_disturb}, the control algorithm can determine the appropriate correction for such a disturbance through
+ As seen in \ref{kalman} the kalman filter, while noisy due to the wind variations in the wind sensor data, follows the thrust value from the testbed closely even while there are major errors in play.Therefore we have confidence to send this value to the PI controller to control the system.
+
+We performed the same tests, this time with the controller active, to measure the active response of the controller.
+Since the response of the wind sensor has a lot of intrinsic noise, the controller, responds with a lot of fluctuations.
+With this being the case, it is shown in \ref{wind_disturbance} and \ref{pwm_reduc_active}, that the average response of the active controller versus no control is significantly more along the desired thrust value.
+\begin{figure}[htbp]
+	\includegraphics[width=7cm]{images/Figure_2/wind_ctl.jpg}
+	\caption{response}
+	\label{wind_disturbance}
+	\end{figure}
+\begin{figure}[htbp]
+	\includegraphics[width=7cm]{images/Figure_2/pwm_control.jpg}
+	\caption{response}
+	\label{PWM_control}
+\end{figure}
 
@@
 In real situations on a quadrotor or such, the behaviour of our system might be significantly different.
-low wind speed. Have not accounted for multiple sources of wind. fixed and controlled environment. only one propeller. 
-\section{5}
-\subsection{Reiteration of results}
-In this paper we presented a closed loop control system for the purposes of controlling MAV rotor systems by the introduction of a hot wire anemometer.
-The anemometer measures the rate of wind flow from the downwash of the MAV rotor and there is a linear relationship that is developed between wind flow velocity and the thrust output of the system.
-Through this relationship we developed a PI controller that maintains a desired thrust value against internal and external disturbances.
-\subsection{Reiteration of applications}
+\section{Conclusion}
 
-\subsection{}
-	\begin{figure}[htbp]
-	\includegraphics[width=10cm]{images/block_diagram.png}
-	\caption{Block Diagram}
-	\label{block_diagram}
-	\end{figure}
-	\begin{figure}[htbp]
-	\includegraphics[width=10cm]{images/figure_1/area_heatmap.jpg}
-	\caption{Block Diagram}
-	\label{area}
-	\end{figure}
-	\begin{figure}[htbp]
-	\includegraphics[width = 7cm]{images/figure_1/dist_heatmap.jpg}
-	\caption{Block Diagram}
-	\label{dist}
-\end{figure}
-	\begin{figure}[htbp]
-	\includegraphics[width=10cm]{images/figure_1/orientation.jpg}
-	\caption{Block Diagram}
-	\label{orientation}
-\end{figure}
-	\begin{figure}[htbp]
-	\includegraphics[width=10cm]{images/figure_1/range.jpg}
-	\caption{range}
-	\label{range}
-\end{figure}
-	\begin{figure}[htbp]
-	\includegraphics[width=10cm]{images/figure_1/response.jpg}
-	\caption{response}
-	\label{response}
-\end{figure}
-%	\begin{figure}[b]
-%	\includegraphics[width=\textwidth / 2]{images/block_diagram.png}
-%	\caption{Block Diagram}
-%	\label{block_diagram}
-%\end{figure}
-%	\begin{figure}[b]
-%	\includegraphics[width=\textwidth / 2]{images/block_diagram.png}
-%	\caption{Block Diagram}
-%	\label{block_diagram}
-%\end{figure}
-%	\begin{figure}[b]
-%	\includegraphics[width=\textwidth / 2]{images/block_diagram.png}
-%	\caption{Block Diagram}
-%	\label{block_diagram}
-%\end{figure}
+In this paper, we have proposed a low-cost system for real-time estimation and regulation of aerodynamic thrust for multirotor aerial vehicles.
+The scheme mainly targets the rotor with a fixed-blade pitch which is commonly used in UAV.
+The proposed system includes the integration of an onboard wind sensor, effective adaptive Kalman filter, and a simple PI control system.
+The main features of the proposed system are the ability for a direct sensing and precise controlling of rotor thrust.
+The experimental tests showed a robust behavior towards external disturbances including wind gusts and also tolerant to efficiency loss in the rotor.
+The future work involves validating the proposed system’s features for a flying UAV.
+This includes implementing the developed system on a UAV to perform hover flight with external wind and aggressive flight maneuvers.
 
-\subsection{5.4}
 \begin{thebibliography}{00}
@@
 3609-3616.
+\bibitem{streit} B.
+Arain and F.
+Kendoul, "Real-time wind speed estimation and compensation for improved flight," in IEEE Transactions on Aerospace and Electronic Systems, vol.
+50, no.
+2, pp.
+1599-1606, April 2014.
+\bibitem{yeo}Derrick Yeo, University of Maryland, College Park; Nitin Sydney, University of Maryland, College Park; Derek A.
+Paley, University of Maryland, College Park; Donald Sofge, Naval Research Laboratory AIAA Guidance, Navigation, and Control Conference Kissimmee, Florida
+
 \end{thebibliography}

### 2018-09-16 DATA/data_for_paper/final3/sfsd.m

@@ -1,4 +1,4 @@
-wind_d= csvread("friday_night/wind_d_comparison.csv",1,0);
+wind_d= csvread("paper_data/wind_disturbance.csv",1,0);
 %  curr_testtorq = pt;
 [r,c] = find(wind_d(:,10) == 0);
 wind_d(r,:) = [];

### 2018-09-16 paper/drafts/IEEE_VERSION.tex
FINALLY DONE

@@
 \and
-\IEEEauthorblockN{Sherman**}
-\IEEEauthorblockA{Sherman@sherman.com}
+\IEEEauthorblockN{Alsharman Mohammad**}
+\IEEEauthorblockA{alsharman.mohammad@gmail.com}
 \and
@@
 \section{2}
-\subsection{Wind sensor math/theory}
+\subsection{Wind Flow Theory}
 We have to start by defining the three different velocities that apply to a propeller.
@@
 	\includegraphics[width=7cm]{images/figure_1/orientation.jpg}
-	\caption{Block Diagram}
+	\caption{Results of exposing the wind sensor in different orientations to a range of wind velocities. The orientation normal to the wind shows the highest sensitivity. }
 	\label{orientation}
@@
 	\includegraphics[width=7cm]{images/figure_1/range.jpg}
-	\caption{range}
+	\caption{Results of the test to determine the measuring range of the sensor.
+The sensor can easily measure the low end of the motor's RPM, but as the RPM surpasses $25\%$ of max RPM, there accumulates significant noise.
+}
 	\label{range}
 \end{figure}
-
 One other factor of a sensor that is important to determine is the measurement lag.
@@
 	\includegraphics[width=7cm]{images/figure_1/response.jpg}
-	\caption{response}
+	\caption{A test to measure the lag in response time between the thrust stand and the wind sensor.}
 	\label{response}
@@
 To do so we measured a semi-circle area behind the propeller to deem the location of highest wind sensitivity.
-Resulting in a map as seen in figure \ref{area},\ref{dist}.
+Resulting in a map as seen in figure \ref{area}.
 This results in a location approximately 7 cm above the axis of the propeller and 5 cm behind the propeller.
@@
 	\begin{figure}[htbp]
-	\includegraphics[width=7cm]{images/figure_1/area_heatmap.jpg}
-	\caption{Block Diagram}
+	\includegraphics[width=7cm]{images/figure_1/comb_heatmap.jpg}
+	\caption{A visual display of where the propeller's downwash is the strongest.
+a.
+shows how the wind flow is measured along a plane parallel to the propeller.
+b.
+shows how the wind flow changes in the plane perpendicular to the propeller}
 	\label{area}
 \end{figure}
-\begin{figure}[htbp]
-	\includegraphics[width = 7cm]{images/figure_1/dist_heatmap.jpg}
-	\caption{Block Diagram}
-	\label{dist}
-\end{figure}
+
 \section{Results}
@@
 	\includegraphics[width=7cm]{images/Figure_2/Block_Diagram.jpg}
-	\caption{Block Diagram}
+	\caption{Our proposed control system based around measurements from the wind sensor.}
 	\label{block_diagram}
@@
 	\includegraphics[width=7cm]{images/akf1.jpg}
-	\caption{response}
+	\caption{Thrust State Estimation}
 	\label{akf1}
@@
 	\includegraphics[width=7cm]{images/akf2.jpg}
-	\caption{response}
+	\caption{Thrust Estimation Error}
 	\label{akf2}
@@
 	\includegraphics[width=7cm]{images/Figure_2/kalman.jpg}
-	\caption{response}
+	\caption{The response of the Kalman Filter, when there is no meaningful disturbance.}
 	\label{kalman}
@@
 	\includegraphics[width=7cm]{images/Figure_2/pwm_reduc.jpg}
-	\caption{response}
+	\caption{The response of the Kalman Filter when there is an internal error to reduce the motor command by $20\%$.}
 	\label{pwm_reduc}
@@
 	\includegraphics[width=7cm]{images/Figure_2/wind_d.jpg}
-	\caption{response}
+	\caption{The response of the Kalman Filter when there is a wind disturbance reducing the thrust output of the propeller.}
 	\label{wind_d}
@@
 
-We performed the same tests, this time with the controller active, to measure the active response of the controller.
+We perform tests with similar errors to measure the active response of the controller.
 Since the response of the wind sensor has a lot of intrinsic noise, the controller, responds with a lot of fluctuations.
-With this being the case, it is shown in \ref{wind_disturbance} and \ref{pwm_reduc_active}, that the average response of the active controller versus no control is significantly more along the desired thrust value.
+With this being the case, it is shown in \ref{wind_disturbance} and \ref{PWM_control}, that the average response of the active controller versus no control is significantly more along the desired thrust value.
+Hence the controller, and the sensor work to act as a viable option to create a closed loop control system.
 \begin{figure}[htbp]
 	\includegraphics[width=7cm]{images/Figure_2/wind_ctl.jpg}
-	\caption{response}
+	\caption{The response of the active controller to a wind disturbance. Compared to no control, the system reponds with a thrust value that matches closely to the desired thrust value.}
 	\label{wind_disturbance}
@@
 	\includegraphics[width=7cm]{images/Figure_2/pwm_control.jpg}
-	\caption{response}
+	\caption{The response of the active controller to an internal error. Compared to co control, the system responds with a more accurate control to maintain the desired thrust.}
 	\label{PWM_control}
@@
 
-\subsection{Shortcomings and limitations}
+\subsection{Further Work}
 As mentioned previously, having a closed loop system allows for a more robust and agile system which allows for better flight performance.
@@
 These areas would all benefit by having a physical measurement of the thrust rather than an estimation.
+In the future we hope to apply our method towards these problems and find a solution that fits our criteria of measuring the wind to estimate thrust rather than a more complicated system.
 
@@
 In real situations on a quadrotor or such, the behaviour of our system might be significantly different.
+In the future we will move our setup onto a quadrotor where we can model how the system will behave with multiple rotors and in a more dynamic environment.
 \section{Conclusion}

### 2018-09-16 paper/drafts/IEEE_VERSION.tex
Now were actually done

@@
 As well there is a very limited range of speeds that are available for measurement from the probe.
-There are some works which have used strain guages and hall effect sensors or even torque measurements to obtain the thrust
+There are some works which have used strain guages and hall effect sensors or even torque measurements to obtain the thrust value through similar mathematical relationships.
+The last method that is availble in research is a variable pitch propeller through the research of Cutler.
+et.
+al \cite{cutler}.
+This again is mathematically sound, but in practice has far too many moving parts and is most likely to fail due to mechanical issues
 
@@
 Paley, University of Maryland, College Park; Donald Sofge, Naval Research Laboratory AIAA Guidance, Navigation, and Control Conference Kissimmee, Florida
-
+\bibitem{cutler}  M. Cutler, J. P. How, "Analysis and Control of a Variable-Pitch Quadrotor for Agile Flight," 2015
+J. Dyn. Sys., Meas., Control 137(10), 101002
 \end{thebibliography}
